### 2019-10-17 Draft.tex
update

\documentclass[12pt,a4paper,hyperref]{article}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
	\definecolor{ultramarine}{rgb}{0.07, 0.04, 0.56}
\usepackage{amsmath, natbib, latexsym, array, amssymb,longtable,float, graphicx, appendix,lscape,diagbox,textcomp,placeins}
\usepackage[colorlinks,
            linkcolor=ultramarine,
            anchorcolor=green,
            citecolor=darkblue
            ]{hyperref}
\usepackage[flushleft]{threeparttable}
\usepackage[top=2.7cm, left=3cm, right=3cm, bottom=2.7cm]{geometry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

\urlstyle{same}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{pgfplotstable}
\sisetup{
  round-mode          = places, % Rounds numbers
  round-precision     = 2, % to 2 places
}

\newenvironment{sequation}{\begin{equation}\tiny}{\end{equation}}
\DeclareMathOperator*{\plim}{plim}
\renewcommand{\floatpagefraction}{0.60}
\renewcommand{\appendixpagename}{\Large Appendix}
\setcounter{secnumdepth}{3}
\begin{document}
\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here

\center % Center everything on the page

\HRule \\[0.4cm]
{ \huge \bfseries Dynamic Heterogeneous Panels }\\[0.4cm] % Title of your document
\HRule \\[1.5cm]

\vfill % Fill the rest of the page with whitespace

\end{titlepage}

\newpage
\tableofcontents
\newpage
\section{Asymptotic bias of LS estimator}
\subsection{Brief the source of bias}
Consider the dynamic heterogeneous panels data model:
\begin{align}
y_{i,t}=\phi_{i} y_{i,t-1}+ \beta_{1i}x_{i,t}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \label{1}
\end{align}

 Form above model, the model can rewritten as
 \begin{align}
 \Delta y_{i,t}=-\left( 1-\phi_{i}\right)\left(y_{i,t}- \pi_{i}x_{i,t}  \right)+u_{i,t},
 \end{align}
where $\pi_{i}=\frac{\beta_{i}}{1-\phi_{i}}$. And we defined $\theta_{i}=\left(1-\phi_{i} \right)$.
Then we suppose
\begin{align}
\begin{split}
\theta_{i}&=\theta+\eta_{i1}, \\
\pi_{i}&=\pi+\eta_{i2}.
\end{split}
\end{align}
Therefore, we know
\begin{align}
\begin{split}
\beta_{i}=\pi_{i}\theta_{i}=\left(\pi+\eta_{i2}  \right) \left( \theta+\eta_{i1}\right)=\pi\theta+\pi\eta_{i,1}+\theta\eta_{i2}+\eta_{i1}\eta_{i2}
\end{split}
\end{align}
And we defined $\eta_{i3}=\pi\eta_{i,1}+\theta\eta_{i2}+\eta_{i1}\eta_{i2} $. Then,we know $\beta_{i}=\pi \theta+\eta_{i3}$.
Therefore, from equation $(\ref{1})$, we have
\begin{align}
\begin{split}
y_{i,t}&=\phi_{i} y_{i,t-1}+ \left(  \pi\theta+\pi\eta_{i,1}+\theta\eta_{i2}+\eta_{i1}\eta_{i2}   \right)x_{i,t}+u_{i,t} \\
&=\left(1-\theta_{i}  \right)y_{i,t-1}+\beta x_{i,t}+\eta_{i,3}x_{i,t}+u_{i,t} \\
&=(1-\theta)y_{i,t-1}-\eta_{i1}y_{i,t-1}+\beta x_{i,t}+\eta_{i3} x_{i,t}+u_{i,t} \\
&=\phi y_{i,t-1}+ \beta x_{i,t}+\left(u_{i,t}-\eta_{i1} y_{i,t-1}+\eta_{i3} x_{i,t}  \right) \\
&=\phi y_{i,t-1}+ \beta x_{i,t}+v_{i,t},
\end{split}
\end{align}
where $v_{i,t}=\left(u_{i,t}-\eta_{i1} y_{i,t-1}+\eta_{i3} x_{i,t}  \right)$.
Then,we can see that  $y_{i,t-1}$ and $x_{i,t}$ are correlated with $v_{i,t}$.

\subsection{Asymptotic bias of LS estimator}
To be continue.

\section{estimation methods }
For convenient, we assume the number of regressor is $1$ and we express the model as
\begin{align}
y_{i,t}=\phi_{i} y_{i,t-1}+ \beta_{1i}x_{i,t}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T.
\end{align}
We stack the $T$ observations for each $i$ yield
\begin{align}
\boldsymbol{y}_{i}=\phi \boldsymbol{y}_{i,-1}+ \boldsymbol{x}_{i}\beta +\boldsymbol{u}_{i},
\end{align}
where $\boldsymbol{y}_{i}=\left(y_{i,1},  \ldots, y_{i,T} \right)^{'}$, $\boldsymbol{y}_{i,-1}=\left(y_{i,0},  \ldots, y_{i,T-1} \right)^{'}$, $\boldsymbol{x}_{i}=\left(x_{i,1},  \ldots, x_{i,T} \right)^{'}$ and $\boldsymbol{u}_{i}=\left(u_{i,1}, \ldots, u_{i,T} \right)$. To be more compressive, the model can be expressed as
\begin{align}
\boldsymbol{y}_{i}=\boldsymbol{W}_{i}\boldsymbol{\varphi}+\boldsymbol{u}_{i}, \label{7}
\end{align}
 where $\boldsymbol{W}_{i}=\left(\boldsymbol{y}_{i,-1}, \boldsymbol{x}_{i} \right)$ and $\boldsymbol{\varphi}=\left( \phi, \beta \right)^{'}$

\subsection{LSMG estimator}
The LS (least square) estimator is defined as
\begin{align}
\boldsymbol{\hat{\varphi}}_{LSi}=\left(\boldsymbol{W}^{'}_{i}\boldsymbol{W}_{i}  \right)^{-1}\left(\boldsymbol{W}^{'}_{i}\boldsymbol{y}_{i}  \right)
\end{align}
Follow \citet{Pesaran:1995}, we define the LSMG (least square mean group) estimator as
\begin{align}
\boldsymbol{\hat{\varphi}}_{LSMG}=\frac{1}{N}\sum^{N}_{i=1}\boldsymbol{\hat{\varphi}}_{LSi}.
\end{align}

\subsection{IVMG estimator}
We use current and lagged values of $\boldsymbol{x}_{i}$ as instruments, as
\begin{align}
\boldsymbol{Z}_{i}=\left( \boldsymbol{x}_{i}, \boldsymbol{x}_{i,-1} \right),
\end{align}
where $\boldsymbol{x}_{i,-1} =\left(x_{i,0},  \ldots, x_{i,T-1} \right)^{'}$.

The IV (instrument variable) estimator is defined as
\begin{align}
\boldsymbol{\hat{\varphi}}_{IVi}=\left(\boldsymbol{Z}^{'}_{i}\boldsymbol{W}_{i}  \right)^{-1}\left(\boldsymbol{Z}^{'}_{i}\boldsymbol{y}_{i}  \right)
\end{align}
 We also define the IVMG (instrument variable mean group) estimator as
\begin{align}
\boldsymbol{\hat{\varphi}}_{IVMG}=\frac{1}{N}\sum^{N}_{i=1}\boldsymbol{\hat{\varphi}}_{IVi}.
\end{align}

\subsection{Norkutes' (2019) IVMG estimator}
Consider the dynamic heterogeneous panel data model with multi-factor error structure. The error term $u_{i,t}$ and $\xi_{i,t}$ can be extend as
\begin{align}
\begin{split}
u_{i,t}&=\boldsymbol{\gamma}^{0'}_{yi}\boldsymbol{f}^{0}_{yt}+\varepsilon_{yi,t}, \\
\xi_{i,t}&=\boldsymbol{\gamma}^{0'}_{xi}\boldsymbol{f}^{0}_{xt}+\varepsilon_{xi,t},
\end{split}
\end{align}
where $\boldsymbol{\gamma}^{0}_{yi}$ and $\boldsymbol{\gamma}^{0}_{xi}$ are $m_{y}\times 1$ and $m_{x}\times 1$ true
 factor loading respectively, $\boldsymbol{f}^{0}_{yt}$  and  $\boldsymbol{f}^{0}_{xt}$ are  $m_{y}\times 1$ and $m_{x}\times 1$ true vector of unobservable factors respectively. And, we set  $\varepsilon_{yi,t}\sim \mathcal{N}(0,\,\sigma_{u}^{2})\,,$ , $\varepsilon_{xi,t}\sim \mathcal{N}(0,\,\sigma_{\xi}^{2})\,.$
 In the first step, we asymptotically eliminate the common factor in $\boldsymbol{x}_{i}$ by projecting matrix, $\boldsymbol{M}_{F^{0}_{x}}$.
 \begin{align}
 \boldsymbol{M}_{F^{0}_{x}}=\boldsymbol{I}_{T}-\boldsymbol{F}^{0}_{x}\left(\boldsymbol{F}^{0'}_{x}\boldsymbol{F}^{0}_{x}  \right)^{-1}\boldsymbol{F}^{0'}_{x} ; \boldsymbol{M}_{F^{0}_{x,-1}}=\boldsymbol{I}_{T}-\boldsymbol{F}^{0}_{x,-1}\left(\boldsymbol{F}^{0'}_{x,-1}\boldsymbol{F}^{0}_{x,-1}  \right)^{-1}\boldsymbol{F}^{0'}_{x,-1}
 \end{align}
And using the defactored covariates as instruments, as
\begin{align}
\boldsymbol{Z}_{IVi}=\left(\boldsymbol{M}_{F^{0}_{x}}\boldsymbol{x}_{i}, \boldsymbol{M}_{F^{0}_{x,-1}}\boldsymbol{x}_{i,-1}  \right)
\end{align}
We use $\boldsymbol{Z}_{IVi}$ as instruments to obtain first step estimator. Then, we can use CCE (common correlated effects) method or PC (principal component) methods to estimate $\boldsymbol{F}^{0}_{y}$ from the residuals in first step IV regression. In second step, we asymptotically eliminate the common factor, $\boldsymbol{F}^{0}_{y}$ by projecting matrix, $\boldsymbol{M}_{F^{0}_{y}}$.
Therefore, we premultiply $\boldsymbol{M}_{F^{0}_{y}}$ in both side of equation $(\ref{7})$ as
\begin{align}
\boldsymbol{M}_{F^{0}_{y}}\boldsymbol{y}_{i}=\boldsymbol{M}_{F^{0}_{y}} \boldsymbol{W}_{i}\boldsymbol{\varphi}+\boldsymbol{M}_{F^{0}_{y}}\boldsymbol{\varepsilon}_{i},
\end{align}
 where $\boldsymbol{\varepsilon}_{i}=\left(\varepsilon_{i,1}, \ldots, \varepsilon_{i,T} \right)$.
The second step IV estimator can be expressed as
\begin{align}
\begin{split}
\boldsymbol{\hat{\hat{\varphi}}}_{IV}&=\left(    \left(\boldsymbol{W}^{'}_{i}\boldsymbol{M}_{F^{0}_{y}}\boldsymbol{Z}_{IVi} \right) \left( \boldsymbol{Z}^{'}_{IVi} \boldsymbol{M}_{F^{0}_{y}}\boldsymbol{Z}_{IVi}  \right)^{-1}    \left(  \boldsymbol{Z}^{'}_{IVi}  \boldsymbol{M}_{F^{0}_{y}} \boldsymbol{W} \right)\right)^{-1} \times \\
& \left(\boldsymbol{W}^{'}_{i}\boldsymbol{M}_{F^{0}_{y}}\boldsymbol{Z}_{IVi} \right) \left( \boldsymbol{Z}^{'}_{IVi} \boldsymbol{M}_{F^{0}_{y}}\boldsymbol{Z}_{IVi}  \right)^{-1}  \left(  \boldsymbol{Z}^{'}_{IVi}  \boldsymbol{M}_{F^{0}_{y}} \boldsymbol{y}_{i} \right)
\end{split}
\end{align}

\section{MC setting}
\subsection{Dynamic heterogeneous panels data model without multi-factor error structure }
Consider the dynamic heterogeneous panels data model:
\begin{align}
\begin{split}
y_{i,t}&=\phi_{i} y_{i,t-1}+ \beta_{1i}x_{i,t}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \\ \label{M1}
x_{i,t}&=\rho x_{i,t-1}+\xi_{i,t},
\end{split}
\end{align}
where $u_{i,t}\sim \mathcal{N}(0,\,\sigma_{u}^{2})\,,$ and $\xi_{i,t}\sim \mathcal{N}(0,\,\sigma_{\xi}^{2})\,.$

\subsection{Dynamic heterogeneous panels data model with multi-factor error structure }
In dynamic panel data 
The generating process of $y$ and $x$ follow $(\ref{M1})$, but we assume
\begin{align}
\begin{split}
u_{i,t}&=\boldsymbol{\gamma}^{'}_{yi}\boldsymbol{f}_{yt}+\varepsilon_{yi,t}, \\
\xi_{i,t}&=\boldsymbol{\gamma}^{'}_{xi}\boldsymbol{f}_{xt}+\varepsilon_{xi,t},
\end{split}
\end{align}
where $\boldsymbol{\gamma}_{yi}$ and $\boldsymbol{\gamma}_{xi}$ are $m_{y}\times 1$ and $m_{x}\times 1$
 factor loading respectively, $\boldsymbol{f}_{yt}$  and  $\boldsymbol{f}_{xt}$ are  $m_{y}\times 1$ and $m_{x}\times 1$ unobservable factors respectively. And, we set  $\varepsilon_{yi,t}\sim \mathcal{N}(0,\,\sigma_{u}^{2})\,,$ , $\varepsilon_{xi,t}\sim \mathcal{N}(0,\,\sigma_{\xi}^{2})\,.$

\begin{align}
\begin{split}
\phi_{i}&= \phi+\eta_{1i}    \\
\beta_{1i}&= \beta_{1}+\eta_{2i},
\end{split}
\end{align}
where $\eta_{1i}\sim \mathcal{IID}\,\mathcal{U}(0.5,\, 1)\,,$ and $\eta_{2i}\sim \mathcal{IID}\,\mathcal{U}(0,\, 0.8)\,$
We also try $\phi_{i}$ is fixed across group, which means $\phi_{i}= \phi$.

We chose $\phi=\{0.25 \}$ and $\beta_{1}=1-\phi$ and $\rho=\{0, 0.5 \}$. Also, we selected $\sigma_{u}^{2}=1$ and $\sigma_{\xi}^{2}=1$. The replication is 1000.
We define LSMG (lest square mean group) estimator and instrument variable mean group (IVMG) estimator.

In the simulation results, we provide the bias and RMSE (root mean square errors) for LSMG estimator and IVMG estimator.

\section{MC results}
Report in excel file. \\
In Excel file:\\
\subsection{Model  without factor structure }
Sheet 1: ARDL(1,0); $\phi_{i}$ ; $\beta_{i}$ .\\
Sheet 2: ARDL(1,0); $\phi$ ; $\beta_{i}$ .\\
Sheet 3: ARDL(1,1); $\phi_{i}$ ; $\beta_{i}$ .\\
Sheet 4: ARDL(1,1); $\phi$ ; $\beta_{i}$  . \\

\subsection{Model have factor structure 1}
We estimate the number of factor is $0$, so we use traditional OLS estimation method and IV estimation method.  \\
Sheet 1: ARDL(1,0); $\phi_{i}$ ; $\beta_{i}$. \\
Sheet 2: ARDL(1,0); $\phi$ ; $\beta_{i}$ \\
Sheet 3: ARDL(1,1); $\phi_{i}$ ; $\beta_{i}$. \\
Sheet 4: ARDL(1,1); $\phi$ ; $\beta_{i}$  . \\

\subsection{Model have factor structure 2}
 We provide MC simulation results for IV estimator that is been provided by \citet{Norkute:2019}. \\
 Sheet 1: ARDL(1,0); $\phi_{i}$ ; $\beta_{i}$. \\
Sheet 2: ARDL(1,0); $\phi$ ; $\beta_{i}$ .\\
Sheet 3: ARDL(1,1); $\phi_{i}$ ; $\beta_{i}$ .\\
Sheet 4: ARDL(1,1); $\phi$ ; $\beta_{i}$.   \\

\newpage

\addcontentsline{toc}{section}{Reference}
\renewcommand\refname{References}
\bibliographystyle{chicago}
\bibliography{1}

\end{document}  \href{*}{*}

### 2019-10-17 MC_code/IV_Norkute.m
up

@@ -8,7 +8,10 @@ b=[b1,b2];
 rho=[0];
 pi_u=0.75;
 SNR=4;
-rho_gamma_1s=0;
+Mu1=1;
+Mu2=-0.5;
+A=0.5;
+rho_gamma_1s=0.5;
 k=2;   % number of regressors
 m_x=2; % number of factors of regressor
 my=1;
@@ -42,6 +45,12 @@ N = list_N(idx_N);
 Dis_T=50;  % discard first 50 time series
 TT= (T0+1)+Dis_T;    
 IVs_MG=zeros(1+k,rep);   % 1+k by rep 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+randn('state', 12345678) ;
+rand('state', 1234567) ;
+   RandStream.setGlobalStream (RandStream('mcg16807','seed',34));
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 sml=1;         
 while sml<=rep
 %parfor sml=1:rep
@@ -77,7 +86,7 @@ end
 
 
 
-beta_i=b'*ones(1,N)+(sqrt(0.4^(2)/12)*rho_b*Xi_b+sqrt(1-rho_b^(2))*ones(k,1)*eta_rho_i); % k by N
+beta_i=b'*ones(1,N)+(sqrt(0.4^(2)/12)*rho_b*Xi_b+sqrt(1-rho_b^(2))*ones(k,1)*eta_rho_bi); % k by N
 
 theta_i=[phi_i;beta_i];   % 1+k by N  
 
@@ -86,15 +95,16 @@ theta_i=[phi_i;beta_i];   % 1+k by N
 
 a_i=zeros(N,1);
 for a=1:N
-a_i(a,:)=normrnd(0,(1-phi_i(:,a))^(2)); % interactive effect for y; N by 1
+a_i(a,:)=A+normrnd(0,(1-phi_i(:,a))^(2)); % interactive effect for y; N by 1
 end
 
-mu_i=zeros(N,1);
+mu1_i=zeros(N,1);
+mu2_i=zeros(N,1);
 for mu=1:N
[…]

### 2019-10-17 MC_code/LS.m
up

@@ -1,19 +1,28 @@
-rep = 1000;  
+rep = 2000;  
 list_T = [25 50 100 200]; 
 list_N = [25 50 100 200];  
-list_phi= [0.25]; 
+list_phi= [0.5]; 
 rho=[0.5];
-k=1;   % number of regressors
+b1=3;
+b2=1;
+rho_b=0.4;
+b=[b1,b2];
+k=2;   % number of regressors
 bias_mean_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
-bias_mean_beta=zeros(size(list_T,2), size(list_N,2)); 
+bias_mean_beta1=zeros(size(list_T,2), size(list_N,2)); 
+bias_mean_beta2=zeros(size(list_T,2), size(list_N,2)); 
 std_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-std_beta=zeros(size(list_T,2), size(list_N,2));  
+std_beta1=zeros(size(list_T,2), size(list_N,2));  
+std_beta2=zeros(size(list_T,2), size(list_N,2));  
 rmse_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-rmse_beta=zeros(size(list_T,2), size(list_N,2));
+rmse_beta1=zeros(size(list_T,2), size(list_N,2));
+rmse_beta2=zeros(size(list_T,2), size(list_N,2));
+
 
 for idx_phi=1:size(list_phi,2)     
 phi= list_phi(idx_phi);  
-  b=1-phi; 
+  b1=3;
+  b2=1;
 for idx_T=1:size(list_T,2)    
 T0 = list_T(idx_T);             
  
@@ -23,68 +32,93 @@ Dis_T=50;
 
 TT= (T0+1)+Dis_T;    
 
-
 LS_MG=zeros(1+k,rep);   % 1+k by rep
 sml=1;         
-%while sml<=rep
-parfor sml=1:rep
+while sml<=rep
+%parfor sml=1:rep
 y=zeros(N,TT);
-x=zeros(N,TT);
[…]

### 2019-10-17 MC_code/IV_MG.m
Update IV_MG.m

@@ -1,19 +1,28 @@
-rep = 1000;  
+rep = 2000;  
 list_T = [25 50 100 200]; 
 list_N = [25 50 100 200];  
-list_phi= [0.25]; 
-rho=[0];
-k=1;
+list_phi= [0.5]; 
+rho=0.5;
+b1=3;
+b2=1;
+rho_b=0.4;
+b=[b1,b2];
+k=2;   % number of regressors
 bias_mean_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
-bias_mean_beta=zeros(size(list_T,2), size(list_N,2)); 
+bias_mean_beta1=zeros(size(list_T,2), size(list_N,2)); 
+bias_mean_beta2=zeros(size(list_T,2), size(list_N,2)); 
 std_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-std_beta=zeros(size(list_T,2), size(list_N,2));  
+std_beta1=zeros(size(list_T,2), size(list_N,2));  
+std_beta2=zeros(size(list_T,2), size(list_N,2));  
 rmse_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-rmse_beta=zeros(size(list_T,2), size(list_N,2));
+rmse_beta1=zeros(size(list_T,2), size(list_N,2));
+rmse_beta2=zeros(size(list_T,2), size(list_N,2));
+
 
 for idx_phi=1:size(list_phi,2)     
 phi= list_phi(idx_phi);  
-  b=1-phi; 
+  b1=3;
+  b2=1;
 for idx_T=1:size(list_T,2)    
 T0 = list_T(idx_T);             
  
@@ -23,80 +32,108 @@ Dis_T=50;
 
 TT= (T0+1)+Dis_T;    
 
-IVs_MG=zeros(1+k,rep);   % 1+k by rep
+IVMG=zeros(1+k,rep);   % 1+k by rep
+
 sml=1;         
-%while sml<=rep
-parfor sml=1:rep
-    
[…]

### 2019-10-18 MC_code/IV_MG.m
update

@@ -8,8 +8,7 @@ b2=1;
 rho_b=0.4;
 b=[b1,b2];
 k=2;   % number of regressors
-bias_mean_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
-bias_mean_beta1=zeros(size(list_T,2), size(list_N,2)); 
+bias_mean_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); bias_mean_beta1=zeros(size(list_T,2), size(list_N,2)); 
 bias_mean_beta2=zeros(size(list_T,2), size(list_N,2)); 
 std_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
 std_beta1=zeros(size(list_T,2), size(list_N,2));  
@@ -104,7 +103,7 @@ Z=zeros(T0,2*k,N);
 for iii=1:N
 W(:,:,iii)=[W_it(iii,:,1)', W_it(iii,:,2)',W_it(iii,:,3)']; % T0 by 1+k
 Z(:,:,iii)=[Z_it(iii,:,1)', Z_it(iii,:,2)', Z_it(iii,:,3)',Z_it(iii,:,4)'];  %  T0 by 2k
-theta_IV(:,iii)=(((Z(:,:,iii)'*MF_x2*W(:,:,iii))' /T0)*((Z(:,:,iii)'*MF_x2*Z(:,:,iii))/T0)^(-1)*((Z(:,:,iii)'*MF_x2*W(:,:,iii)) /T0))^(-1)*(((Z(:,:,iii)'*MF_x2*W(:,:,iii))' /T0)*((Z(:,:,iii)'*MF_x2*Z(:,:,iii))/T0)^(-1)*((Z(:,:,iii)'*MF_x2*y_NT2(iii,:)')/T0));
+theta_IV(:,iii)=(((Z(:,:,iii)'*W(:,:,iii))' /T0)*((Z(:,:,iii)'*Z(:,:,iii))/T0)^(-1)*((Z(:,:,iii)'*W(:,:,iii)) /T0))^(-1)*(((Z(:,:,iii)'*W(:,:,iii))' /T0)*((Z(:,:,iii)'*Z(:,:,iii))/T0)^(-1)*((Z(:,:,iii)'*y_NT2(iii,:)')/T0));
 
 end
 
@@ -118,8 +117,8 @@ mean_beta1= nanmean(IVMG(2,:));
[…]

### 2019-10-18 MC_code/IV_MG_factor.m
up

@@ -1,118 +1,0 @@
-rep = 1000;  
-list_T = [25 50 100 200]; 
-list_N = [25 50 100 200];  
-list_phi= [0.25]; 
-rho=[0];
-k=1;   % number of regressors
-m_x=2; % number of factors of regressor
-m_y=2; % number of factors of y
-
-bias_mean_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
-bias_mean_beta=zeros(size(list_T,2), size(list_N,2)); 
-std_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-std_beta=zeros(size(list_T,2), size(list_N,2));  
-rmse_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-rmse_beta=zeros(size(list_T,2), size(list_N,2));
-
-for idx_phi=1:size(list_phi,2)     
-phi= list_phi(idx_phi);  
-  b=1-phi; 
-for idx_T=1:size(list_T,2)    
-T0 = list_T(idx_T);             
- 
-for idx_N=1:size(list_N,2)   
-N = list_N(idx_N);
-Dis_T=50;
-
-TT= (T0+1)+Dis_T;    
-
-IVs_MG=zeros(1+k,rep);   % 1+k by rep
-sml=1;         
-%while sml<=rep
-parfor sml=1:rep
-    
-y=zeros(N,TT);
-x=zeros(N,TT);
-phi_i= phi+  (0.8)*rand([1,N]); 
-%phi_i= phi*ones(1,N);
-%beta_i=b*ones(1,N);
-beta_i=b+0.5+(0.5)*rand([1,N]); 
-theta_i=[phi_i;beta_i];   % 1+k by N
-eta_y=normrnd(0,1/m_y,[m_y,N]);  % factor loading; N by m
-fy=zeros(m_y,TT);  % creat a space for saving data factor
-fy(:,1)=zeros(m_y,1);   % setting the initial factor
-for t=2:TT
[…]

### 2019-10-18 MC_code/IV_defactor.m

@@ -1,128 +1,0 @@
-rep = 500;  
-list_T = [25 50 100]; 
-list_N = [25 50 100];  
-list_phi= [0.8]; 
-rho=[0];
-k=1;   % number of regressors
-m_x=2; % number of factors of regressor
-m_y=2; % number of factors of y
-
-bias_mean_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
-bias_mean_beta=zeros(size(list_T,2), size(list_N,2)); 
-std_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-std_beta=zeros(size(list_T,2), size(list_N,2));  
-rmse_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-rmse_beta=zeros(size(list_T,2), size(list_N,2));
-
-for idx_phi=1:size(list_phi,2)     
-phi= list_phi(idx_phi);  
-  %b=1-phi; % beta
-  b=3;
-for idx_T=1:size(list_T,2)    
-T0 = list_T(idx_T);             
- 
-for idx_N=1:size(list_N,2)   
-N = list_N(idx_N);
-Dis_T=50;  % discard first 50 time series
-TT= (T0+1)+Dis_T;    
-IVs_MG=zeros(1+k,rep);   % 1+k by rep 
-sml=1;         
-while sml<=rep
-%parfor sml=1:rep
-
-y=zeros(N,TT);
-x=zeros(N,TT);
-phi_i= phi+  (0.5)*rand([1,N]);  % phi heterogeneous
-%phi_i= phi*ones(1,N);  % phi homogenous 
-%beta_i=b*ones(1,N);   % beta homogenous 
-beta_i=b+0.5+(0.5)*rand([1,N]); % beta heterogeneous
-theta_i=[phi_i;beta_i];   % 1+k by N  
-eta_y=normrnd(0,1/m_y,[N, m_y]);  % factor loading; N by m
-fy=zeros(m_y,TT);  % creat a space for saving data factor
[…]

### 2019-10-18 MC_code/LS.m

@@ -101,7 +101,7 @@ end
 
 mean_phi= nanmean(LS_MG(1,:));
 mean_beta1= nanmean(LS_MG(2,:));
-mean_beta2= nanmean(LS_MG(2,:));
+mean_beta2= nanmean(LS_MG(3,:));
 bias_mean_phi(idx_T, idx_N, idx_phi) = mean_phi - phi;
 bias_mean_beta1(idx_T, idx_N )=mean_beta1 - b1;
 bias_mean_beta2(idx_T, idx_N )=mean_beta2 - b2;

### 2019-10-18 MC_code/LS_factor.m

@@ -1,105 +1,0 @@
-rep = 1000;  
-list_T = [25 50 100 200]; 
-list_N = [25 50 100 200];  
-list_phi= [0.25]; 
-rho=[0];
-k=1;   % number of regressors
-m_x=2; % number of factors of regressor
-m_y=2; % number of factors of y
-bias_mean_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
-bias_mean_beta=zeros(size(list_T,2), size(list_N,2)); 
-std_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-std_beta=zeros(size(list_T,2), size(list_N,2));  
-rmse_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-rmse_beta=zeros(size(list_T,2), size(list_N,2));
-
-for idx_phi=1:size(list_phi,2)     
-phi= list_phi(idx_phi);  
-  b=1-phi; 
-for idx_T=1:size(list_T,2)    
-T0 = list_T(idx_T);             
- 
-for idx_N=1:size(list_N,2)   
-N = list_N(idx_N);
-Dis_T=50;
-
-TT= (T0+1)+Dis_T;    
-
-
-LS_MG=zeros(1+k,rep);   % 1+k by rep
-sml=1;         
-%while sml<=rep
-parfor sml=1:rep
-y=zeros(N,TT);
-x=zeros(N,TT);
-%phi_i= phi+  (0.8)*rand([1,N]);
-phi_i= phi*ones(1,N);
-beta_i=b+0.5+(0.5)*rand([1,N]); 
-theta_i=[phi_i;beta_i];   % 1+k by N
-eta_y=normrnd(0,1/m_y,[m_y,N]);  % factor loading; N by m
-fy=zeros(m_y,TT);  % creat a space for saving data factor
-fy(:,1)=zeros(m_y,1);   % setting the initial factor
-for t=2:TT
-   fy(:,t)= 0.5*fy(:,t-1)+sqrt(1-0.5^2)*normrnd(0,1,[m_y,1]); % m by TT
-end 
-
-eta_x=normrnd(0,1/m_x,[m_x,N]);  % factor loading; N by m
[…]

### 2019-10-18 MC_code/LS.m
up

@@ -33,6 +33,11 @@ Dis_T=50;
 TT= (T0+1)+Dis_T;    
 
 LS_MG=zeros(1+k,rep);   % 1+k by rep
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+randn('state', 12345678) ;
+rand('state', 1234567) ;
+   RandStream.setGlobalStream (RandStream('mcg16807','seed',34));
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 sml=1;         
 while sml<=rep
 %parfor sml=1:rep

### 2019-10-18 MC_code/LS.m
up

@@ -119,7 +119,7 @@ std_beta2(idx_T, idx_N) = nanstd(LS_MG(3,:));
 
 rmse_phi(idx_T, idx_N,idx_phi) = sqrt( nanmean( (LS_MG(1,:)-phi).^2) ); 
 rmse_beta1(idx_T, idx_N) = sqrt( nanmean( (LS_MG(2,:)-b1).^2) ); 
-rmse_beta2(idx_T, idx_N) = sqrt( nanmean( (LS_MG(3,:)-b1).^2) ); 
+rmse_beta2(idx_T, idx_N) = sqrt( nanmean( (LS_MG(3,:)-b2).^2) ); 
 
 end
 end

### 2019-10-18 MC_code/IV_MG.m
up

@@ -2,7 +2,7 @@ rep = 2000;
 list_T = [25 50 100 200]; 
 list_N = [25 50 100 200];  
 list_phi= [0.5]; 
-rho=0.5;
+rho=0;
 b1=3;
 b2=1;
 rho_b=0.4;

### 2019-10-18 MC_code/LS.m

@@ -2,7 +2,7 @@ rep = 2000;
 list_T = [25 50 100 200]; 
 list_N = [25 50 100 200];  
 list_phi= [0.5]; 
-rho=[0.5];
+rho=[0];
 b1=3;
 b2=1;
 rho_b=0.4;

### 2019-12-16 Draft_V5.tex
up

\documentclass[12pt,a4paper,hyperref]{article}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
	\definecolor{ultramarine}{rgb}{0.07, 0.04, 0.56}
\usepackage{amsmath, natbib, latexsym, array, amssymb,longtable,float, graphicx, appendix,lscape,diagbox,textcomp,placeins}
\usepackage[colorlinks,
            linkcolor=ultramarine,
            anchorcolor=green,
            citecolor=darkblue
            ]{hyperref}
\usepackage[flushleft]{threeparttable}
\usepackage[top=2.7cm, left=3cm, right=3cm, bottom=2.7cm]{geometry}
\usepackage{hyperref}
\newtheorem{myDef}{Definition}
\newtheorem{myTheo}{Theorem}
\newtheorem{myProp}{proposition}
\newtheorem{myRem}{Remark}
\newtheorem{myAssu}{Assumption}
\newtheorem{myCor}{Corollary}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

\urlstyle{same}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{pgfplotstable}
\sisetup{
  round-mode          = places, % Rounds numbers
  round-precision     = 2, % to 2 places
}

\newenvironment{sequation}{\begin{equation}\tiny}{\end{equation}}
\DeclareMathOperator*{\plim}{plim}
\renewcommand{\floatpagefraction}{0.60}
\renewcommand{\appendixpagename}{\Large Appendix}
\setcounter{secnumdepth}{3}
\begin{document}
\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here

\center % Center everything on the page

\HRule \\[0.4cm]
{ \huge \bfseries Dynamic Heterogeneous Panels }\\[0.4cm] % Title of your document
\HRule \\[1.5cm]

\vfill % Fill the rest of the page with whitespace

\end{titlepage}

\newpage
\tableofcontents
\newpage
\section{Model, asymptotic property of LS and IV estimator}
\subsection{The models and Assumptions}
\subsubsection{Fixed effects model}
Consider the dynamic heterogeneous panels data model with fixed effects:
\begin{align}
\begin{split}
y_{i,t}&=\alpha_{i}+\phi_{i} y_{i,t-1}+ \boldsymbol{x}^{'}_{i,t}\boldsymbol{\beta}_{i}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \\
&= \boldsymbol{w}^{'}_{i,t}\boldsymbol{\theta}+ \alpha_{i}+u_{i,t}, \label{1}
\end{split}
\end{align}
where $\boldsymbol{x}_{i,t}$ and $\boldsymbol{\beta}_{i}$ are $k \times 1$ vectors and $\boldsymbol{w}_{i,t}=\left(\phi_{i}, \boldsymbol{\beta}^{'}_{i} \right)^{'}$ is a $\left(1+k\right) \times 1$ vector.
Stacking the $T$ observations for each $i$, we have
\begin{align}
\boldsymbol{y}_{i}=\boldsymbol{W}_{i}\boldsymbol{\theta}_{i}+ \alpha_{i}\boldsymbol{\iota}_{T}+ \boldsymbol{u}_{i}, \label{2}
\end{align}
where $\boldsymbol{y}_{i}=\left(y_{i,1},\ldots, y_{i,T} \right)^{'}$, $\boldsymbol{W}_{i}=\left(\boldsymbol{w}_{i,1},\ldots, \boldsymbol{w}_{i,T} \right)^{'}$, $\iota_{T}=\left(1,\ldots,1 \right)^{'}$ and $\boldsymbol{u}_{i}=\left(u_{i,1}, \ldots, u_{i,T} \right)^{'}$.

Due to the incidental parameters problem arise, we use forward filter to the model by \citet{Moon:2000}, \citet{Hayakawa:2009} and \citet{Hayakawa:2019}. We define the $\left(T-1 \right) \times 1$ forward demeaning matrix as

\begin{align}
\boldsymbol{F}=diag(c_{1}, c_{2}, \ldots c_{T-1})
\begin{bmatrix}
1 & \frac{-1}{T-1} & \cdots & \cdots & \frac{-1}{T-1}\\
\vdots & 1 & \frac{-1}{T-2} & \cdots & \frac{-1}{T-2}\\
\vdots & \vdots & \vdots & \ddots & \vdots \\
0 & 0 & 0 & \cdots & -1 
\end{bmatrix},
\end{align}    
where $c_{t}=\sqrt{\left( T-t\right)\left( T-t+1\right) }$.
Multiply $\boldsymbol{F}$ to model $(\ref{2})$, the model can expressed as  
\begin{align}
\tilde{\boldsymbol{y}}_{i}= \tilde{\boldsymbol{W}}_{i}\boldsymbol{\theta}+\tilde{\boldsymbol{u}}_{i},
\end{align}
where $\tilde{\boldsymbol{y}}_{i}=\boldsymbol{F}\boldsymbol{y}_{i}= \left(\tilde{\boldsymbol{y}}_{i,1}, \ldots, \tilde{\boldsymbol{y}}_{i,T-1} \right)^{'}$,  $\tilde{\boldsymbol{W}}_{i}=\boldsymbol{F}\boldsymbol{W}_{i}= \left(\tilde{\boldsymbol{w}}_{i,1}, \ldots, \tilde{\boldsymbol{w}}_{i,T-1} \right)^{'}$ and $\tilde{\boldsymbol{u}}_{i}=\boldsymbol{F}\boldsymbol{u}_{i}= \left(\tilde{\boldsymbol{u}}_{i,1}, \ldots, \tilde{\boldsymbol{u}}_{i,T-1} \right)^{'}$ with $\tilde{\boldsymbol{y}}_{i,t}=c_{t}\left[y_{i,t}-\left(y_{i,t+1}+\cdots+y_{i,T} \right)/\left(T-t \right) \right]$ for $t=1, \ldots, T-1.$

\subsubsection{Trend model}
Consider the dynamic heterogeneous panels data model with fixed effects and heterogeneous time trends:
\begin{align}
\begin{split}
y_{i,t}&=\alpha_{i}+\eta_{i}t +\phi_{i} y_{i,t-1}+ \boldsymbol{x}^{'}_{i,t}\boldsymbol{\beta}_{i}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \\
&= \boldsymbol{w}^{'}_{i,t}\boldsymbol{\theta}+ \alpha_{i}+\eta_{i}t+u_{i,t}, 
\end{split}
\end{align}
where $\boldsymbol{x}_{i,t}$ and $\boldsymbol{\beta}_{i}$ are $k \times 1$ vectors and $\boldsymbol{w}_{i,t}=\left(\phi_{i}, \boldsymbol{\beta}^{'}_{i} \right)^{'}$ is a $\left(1+k\right) \times 1$ vector.
Stacking the $T$ observations for each $i$, we have
\begin{align}
\boldsymbol{y}_{i}=\boldsymbol{W}_{i}\boldsymbol{\theta}_{i}+ \alpha_{i}\boldsymbol{\iota}_{T}+\eta_{i}\boldsymbol{\tau}_{T} + \boldsymbol{u}_{i}, \label{6}
\end{align}
where $\boldsymbol{\tau}_{T}=\left(1, 2, \ldots, T \right)^{'}$. Again, we define the forward demeaning matrix as

\begin{align}
\boldsymbol{F}^{\tau}=diag(c^{\tau}_{1}, c^{\tau}_{2}, \ldots c^{\tau}_{T-2})
\begin{bmatrix}
1 & \frac{2(-2(T-2))}{(T-1)(T-2)} & \frac{2(-2(T-2)+3)}{(T-1)(T-2)} & \cdots & \frac{2(-2(T-2)+3(T-2))}{(T-1)(T-2)} \\
0 & 1 & \frac{2(-2(T-3))}{(T-2)(T-3)} & \cdots & \frac{2(-2(T-3)+3(T-3))}{(T-3)(T-4)} \\
\vdots &\vdots & \vdots & \ddots  &\vdots \\
0 & \cdots & \cdots & \cdots & \frac{2(-2+3)}{2 \cdot 1}
\end{bmatrix}, \label {7}
\end{align}   
where $c^{\tau}_{t}=\sqrt((T-t)(T-t-1)/(T-t-1)(T-t+2)).$

Multiply $\boldsymbol{F}$ to model $(\ref{6})$, the model can expressed as  
\begin{align}
\tilde{\boldsymbol{y}}^{\tau}_{i}= \tilde{\boldsymbol{W}}^{\tau}_{i}\boldsymbol{\theta}+\tilde{\boldsymbol{u}}^{\tau}_{i},
\end{align}
where $\tilde{\boldsymbol{y}}^{\tau}_{i}=\boldsymbol{F}^{\tau}\boldsymbol{y}_{i}= \left(\tilde{\boldsymbol{y}}^{\tau}_{i,1}, \ldots, \tilde{\boldsymbol{y}}^{\tau}_{i,T-2} \right)^{'}$,  $\tilde{\boldsymbol{W}}^{\tau}_{i}=\boldsymbol{F}^{\tau}\boldsymbol{W}_{i}$ and $\tilde{\boldsymbol{u}}^{\tau}_{i}=\boldsymbol{F}^{\tau}\boldsymbol{u}_{i}.$

\begin{myAssu}
$x_{i,t}$ and $u_{i,t}$ are independently distributed for all $t$ and $s$ .
\end{myAssu}

\subsection{IV estimator}
We use current and lagged values of $\boldsymbol{x}_{i}$ as instruments, as
\begin{align}
\boldsymbol{Z}^{(j)}_{i}=\left( \boldsymbol{x}_{i,\cdot}, \boldsymbol{x}_{i,-1},\ldots, \boldsymbol{x}_{i,-j} \right)^{'},
\end{align}
where $\boldsymbol{Z}^{(j)}_{i}$ is $T \times  (j+1)k$ matrix with $j \geq 1$. \\

Then, we can define IV estimator in fixed effect model of $\boldsymbol{\theta}^{b}_{i}$ as
\begin{align}
\hat{\boldsymbol{\theta}}^{b}_{IV,i}= \left( \tilde{\boldsymbol{W}}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \tilde{\boldsymbol{W}}_{i} \right)^{-1} \tilde{\boldsymbol{W}}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \tilde{\boldsymbol{y}}_{i},
\end{align}
where $\boldsymbol{P}^{(j)}_{i}=\boldsymbol{Z}^{(j)}_{i} \left(\boldsymbol{Z}^{(j)'}_{i}\boldsymbol{Z}^{(j)}_{i} \right)^{-1}\boldsymbol{Z}^{(j)'}_{i}$ and $b=1$ corresponds to the fixed effects model while $b=2$ corresponds to the trend models.

The

\subsection{Asymptotic property of LS estimator}

Based on heterogenous dynamic panel data model $(\ref{1})$, we can obtain fixed effect estimator as
\begin{align}
\hat{\boldsymbol{\theta}}_{LS,i}=
\begin{pmatrix}
\hat{\phi}_{i} \\
\hat{\beta}_{i}
\end{pmatrix}=
\begin{pmatrix}
\frac{\sum^{T}_{t=1}\tilde{y}^{2}_{i,t-1}}{T} & \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{x}_{i,t}}{T} \\
\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t-1}}{T} &  \frac{\sum^{T}_{t=1}\tilde{x}_{i,t}^{2}}{T}
\end{pmatrix}^{-1}
\begin{pmatrix}
\frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{y}_{i,t}}{T} \\
\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t}}{T}
\end{pmatrix},
\end{align}

where $\tilde{y}_{i,t}=y_{i,t}-\bar{y}_{i}$, $\tilde{y}_{i,t-1}=y_{i,t-1}-\bar{y}_{i,-1}\iota_{T}$ and $\tilde{x}_{i,t}=x_{i,t}-\bar{x}_{i}$ with $\bar{y}_{i}=\frac{1}{T}\sum^{T}_{t=1}y_{i,t}$, $\bar{y}_{i,-1}=\frac{1}{T}\sum^{T}_{t=1}y_{i,t-1}$,  $\bar{x}_{i}=\frac{1}{T}\sum^{T}_{t=1}x_{i,t}$.  Under equation $(\ref{1})$, we have
\begin{align}
\begin{pmatrix}
\hat{\phi}_{i}-\phi_{i} \\
\hat{\beta}_{i}-\beta_{i}
\end{pmatrix}=
\begin{pmatrix}
\frac{\sum^{T}_{t=1}\tilde{y}^{2}_{i,t-1}}{T} & \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{x}_{i,t}}{T} \\
\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t-1}}{T} &  \frac{\sum^{T}_{t=1}\tilde{x}_{i,t}^{2}}{T}
\end{pmatrix}^{-1}
\begin{pmatrix}
\frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{u}_{i,t}}{T} \\
\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{u}_{i,t}}{T}
\end{pmatrix},
\end{align}
where $\tilde{u}_{i,t}$ is $u_{i,t}-\bar{u}_{i}$ with $\bar{u}_{i}=\frac{1}{T}\sum^{T}_{t=1}u_{i,t}.$

Now, we can investigate asymptotic bias by taking the probability limit as
\begin{align}
A^{(1)}_{\phi i}=\plim_{T  \rightarrow \infty}\left( \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{u}_{i,t}}{T} \right). \label{11}
\end{align}
Then $A^{(1)}_{i}$ can be taken expectations as
\begin{align}
\begin{split}
A^{(1)}_{\phi i}&=E\left(y_{i,t-1}-\bar{y}_{i,-1} \right) \left(u_{i,t}-\bar{u}_{i} \right) \\
&= E\left( y_{i,t-1}u_{i,t}\right) - E\left( y_{i,t-1} \bar{u}_{i}  \right)-E\left(\bar{y}_{i,-1}   u_{i,t}\right)+E\left(\bar{y}_{i,-1}  \bar{u}_{i}\right),
\end{split}
\end{align}
where $E\left( y_{i,t-1}u_{i,t}\right)=0$.

And we assume $y_{i,t}$ has started from a long time period in the past, so we have
\begin{align}
y_{i,t}=\frac{\alpha_{i}}{\left(1-\phi_{i} \right)}+\sum^{\infty}_{s=0}\beta_{i}\phi^{s}_{i}x_{i,t -s}+\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s},
\end{align}

Then, we have
\begin{align}
\begin{split}
A^{(1)}_{\phi i}&=-E\left( \left(\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right) \left(\frac{1}{T}\sum^{T}_{t=1}u_{i,t} \right)  \right)-E\left(\frac{u_{i,t}}{T}\sum^{T}_{t=1}\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right)+ \\
&\left(\frac{1}{T}\sum^{T}_{t=1}\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right)\left( \frac{1}{T}\sum^{T}_{t=1}u_{i,t} \right). \label{12}
\end{split}
\end{align}
 Hence, from above equation, we have
 \begin{equation}
\begin{split}
A^{(1)}_{\phi i}=&-\dfrac{1}{T} E\left\{  \left( u_{i,t-1}+u_{i,t-2}\phi_{i}^{1}+u_{i,t-3}\phi_{i}^{2}+\ldots\right)\left(u_{i,1}+\ldots+u_{i,t-1}+u_{i,t}+\ldots+u_{i,T}\right) \right\} -\\
 &\dfrac{1}{T} E \left\{  u_{i,t}\sum^{T}_{s=1}\left( u_{i,s-1}\phi_{i}^{0}+u_{i,s-2}\phi_{i}^{1}+\ldots+u_{i,s-t-1}\phi_{i}^{t}+\ldots+u_{i,s-T-1}\phi_{i}^{T}+\ldots \right)  \right\}  + \\
 +& \dfrac{1}{T} E\{ \left( \sum^{T}_{s=1}u_{i,s-1}\phi_{i}^{0}+\sum^{T}_{s=1}u_{i,s-2}\phi_{i}^{1}+\ldots+\sum^{T}_{s=1}u_{i,s-t-1}\phi_{i}^{t}+\ldots
+\sum^{T}_{s=1}u_{is-T-1}\phi_{i}^{T}+\ldots \right)\\
 &\left(\dfrac{1}{T}\sum^{T}_{s=1}u_{i,s}\right) \} \\
 =&-\dfrac{\sigma_{u}^{2}}{T}\dfrac{(1-\phi_{i}^{t-1})}{1-\phi_{i}}-\dfrac{\sigma^{2}_{u}}{T}\dfrac{(1-\phi_{i}^{T-t})}{(1-\phi_{i})}+\dfrac{\sigma^{2}_{u}}{T} \left( \dfrac{1}{1-\phi_{i}}-\dfrac{1}{T}\dfrac{(1-\phi_{i}^{T})}{(1-\phi_{i})^{2}}\right) \\
 =&-\dfrac{\sigma_{u}^{2}}{T(1-\phi_{i})}\left( 1-\phi_{i}^{t-1}-\phi_{i}^{T-t}+\dfrac{1}{T}\dfrac{(1-\phi_{i}^{T})}{(1-\phi_{i})}  \right).
 \end{split}
\end{equation}

Therefore, we can see the bias of $\hat{\phi}_{i}$ is $O\left(T^{-1}\right)$.

To be more compact ,we can rewrite the model as,
\begin{align}
\tilde{\boldsymbol{y}}_{i}=\tilde{\boldsymbol{W}}_{i}\boldsymbol{\theta}_{i}+\tilde{\boldsymbol{u}}_{i},
\end{align}
where $\tilde{\boldsymbol{y}}_{i}=\left(\tilde{\boldsymbol{y}}_{i,1},\ldots, \tilde{\boldsymbol{y}}_{i,T}  \right)^{'}$ is $T \times 1$ vector,  $\tilde{\boldsymbol{W}}_{i}=\left( \tilde{\boldsymbol{w}}_{i,1},\ldots, \tilde{\boldsymbol{w}}_{i,T} \right)^{'}$ is $T \times 2$ matrix and $\tilde{\boldsymbol{u}}_{i}=\left(\tilde{\boldsymbol{u}}_{i,1}, \ldots, \tilde{\boldsymbol{u}}_{i,T} \right)$ is $T \times 1$ vector with $\tilde{\boldsymbol{w}}_{i,t}=\left(y_{i,t-1}-\bar{y}_{i,-1}, x_{i,t}-\bar{x}_{i}  \right)^{'}$, for $t=1,\ldots, T$ and $i=1,\ldots, N.$

Also, we define our interested parameter as
\begin{align}
\left(\phi_{i},\beta_{i}  \right)^{'}=\boldsymbol{\theta}_{i}=\boldsymbol{\theta}+\boldsymbol{\lambda}_{i},
\end{align}
where $\boldsymbol{\lambda}_{i}\overset{i.i.d.}{\sim} \left(\boldsymbol{0}, \boldsymbol{\Sigma}_{\lambda} \right).$
The lest square estimator, $\hat{\boldsymbol{\theta}}_{LS,i}$, can be expressed as
\begin{align}
\hat{\boldsymbol{\theta}}_{LS,i}=\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{y}}_{i}}{T}. \label{13}
\end{align}

From above discussion and assumptions, we have following theorem \\
\begin{myTheo}
\begin{align}
\sqrt{T}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}\right) \overset{d}{\to} N \left(\boldsymbol{0}, \boldsymbol{Q}_{i}^{-1}\boldsymbol{\Sigma}_{LS,i}\boldsymbol{Q}_{i}^{-1}  \right),
\end{align}
where $\boldsymbol{\Sigma}_{LS,i}=\plim_{T \to \infty} T^{-1}\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{u}}_{i} \tilde{\boldsymbol{u}}^{'}_{i}  \tilde{\boldsymbol{W}}_{i} $ and $\boldsymbol{Q}_{i}=\plim_{T \to \infty} T^{-1}\tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{W}}_{i}$
\end{myTheo}

\subsubsection{Mean group LS estimator }
Now, we define the mean group estimator of $\boldsymbol{\theta}$:
\begin{align}
\hat{\boldsymbol{\theta}}_{LSMG}=\frac{1}{N}\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSi}.
\end{align}
And we can show that the asymptotic property of $\hat{\boldsymbol{\theta}}_{LSMG}$, as
\begin{align}
\begin{split}
\hat{\boldsymbol{\theta}}_{LSMG}&=N^{-1}\sum^{N}_{i=1}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{y}}_{i}}{T} \\
&=\bar{\boldsymbol{\theta}}+N^{-1}\sum^{N}_{i=1}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T},
\end{split}
\end{align}
where $\bar{\boldsymbol{\theta}}=N^{-1}\sum^{N}_{i=1}\boldsymbol{\theta}_{i}.$
For fixed $N$ and large $T$, we have
\begin{align}
\plim_{T \to \infty}\hat{\boldsymbol{\theta}}_{LSMG} =  \bar{\boldsymbol{\theta}}+ N^{-1}\sum^{N}_{i=1}\plim_{T \to \infty}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1}\plim_{T \to \infty}\left( \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T}\right)
\end{align}
 Then, from section $1.1$, we know that $\plim_{T \to \infty}\left( \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T}\right)=O_{p}(1)$. Thus,  we can obtain
\begin{align}
\plim_{T \to \infty}\hat{\boldsymbol{\theta}}_{LSMG} =  \bar{\boldsymbol{\theta}}.
\end{align}
When $N \to \infty$ and $T \to \infty$ and by the law of large numbers, we can see that
\begin{align}
\plim_{T \to \infty, N \to \infty}\hat{\boldsymbol{\theta}}_{LSMG}=\boldsymbol{\theta}.
\end{align}

And the variance estimator of $\hat{\boldsymbol{\theta}}_{LSMG}$ is given by
\begin{align}
\hat{\boldsymbol{\Sigma}}_{LS,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}.
\end{align}

We show that $\hat{\boldsymbol{\Sigma}}_{LS,\lambda}$ is consistent when $N \to \infty$ and $T \to \infty.$
\begin{align}
\begin{split}
&\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}=\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right) \right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'}\\
&+\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right) \left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'}\\
&-\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right) \left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'} \\
&-\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right) \left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'}. \label{20}
\end{split}
\end{align}

Taking expectation on equation $(\ref{20})$, we have
\begin{align}
\begin{split}
&E\left( \sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'} \right)=
 \sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)+
\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG}+  \\
&\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right) E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}-
\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LS,i}+
\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)\hat{\boldsymbol{\theta}}^{'}_{LS,i}-
\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSMG}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}- \\
&\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LSMG}+
\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LS,i}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}-
\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right) E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'} = \\
&\sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)-N E \left(\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG} \right)+\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right) E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}
\end{split}
\end{align}
and
\begin{align}
E \left(\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG} \right)=\frac{1}{N^{2}} \sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right).
\end{align}

And, we also have
\begin{align}
E \left(\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG} \right)=\frac{1}{N^{2}}\left( \sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)+ \sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right) \right).
\end{align}
Then,
\begin{align}
\begin{split}
&E\left( \sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'} \right)= \\
&\left(1-\frac{1}{N} \right)\sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)+ \sum^{N}_{i=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right)- \frac{1}{N}\sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right). \label{24}
\end{split}
\end{align}
From above equation $(\ref{24})$, we can observe the bias term as,
\begin{align}
\aleph=\sum^{N}_{i=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right)- \frac{1}{N}\sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right). \label{25}
\end{align}

 Taking expectation on equation $(26)$, we have
\begin{align}
E\left( \hat{\boldsymbol{\theta}}_{LS,i} \right)=\boldsymbol{\theta}+E \left(b_{i} \right),
\end{align}
From equation $(\ref{25})$, we know that
 \begin{align}
\aleph=\sum^{N}_{i=1}E \left(b_{i}\right) E\left(b^{'}_{i} \right)- \frac{1}{N}\sum^{N}_{i=1}\sum^{N}_{j=1}E \left(b_{i}\right) E\left(b^{'}_{j} \right).
 \end{align}
When $T \to \infty$, $\aleph=0$.
Therefore, we have following theorem \\

\begin{myTheo}
When $(T,N) \overset{j}{\to} \infty$ such that $N/T \to c$ with $0<c< \infty$,
\begin{enumerate}
\item \begin{align}
\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{LSMG}-\boldsymbol{\theta}  \right)\overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{LS,\lambda} \right).
\end{align}
\item \begin{align}
\hat{\boldsymbol{\Sigma}}_{LS,\lambda} \overset{p}{\to}  \boldsymbol{\Sigma}_{LS,\lambda}
\end{align}
where
\begin{align}
 \hat{\boldsymbol{\Sigma}}_{LS,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}.
\end{align}
\end{enumerate}
\end{myTheo}

\subsection{Asymptotic property of IV estimator}
We use current and lagged values of $\boldsymbol{x}_{i}$ as instruments, as
\begin{align}
\tilde{\boldsymbol{Z}}_{i,t}=\left( \tilde{\boldsymbol{x}}_{i}, \tilde{\boldsymbol{x}}_{i,-1} \right)^{'},
\end{align}
where $\tilde{\boldsymbol{Z}}_{i}$ is $T \times  2$ vector. \\

\begin{myAssu}
$\boldsymbol{A}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{A}}_{i,T}$ has full column rank, $\boldsymbol{B}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{B}}_{i,T}$ and $\boldsymbol{\Sigma}_{i}=\plim_{T \to \infty} T^{-1}\boldsymbol{Z}^{'}_{i}\boldsymbol{u}_{i} \boldsymbol{u}_{i}^{'}\boldsymbol{Z}$ has positive definite, uniformly, where $\tilde{\boldsymbol{A}}_{i,T}= \frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{W}}_{i}$ and $\tilde{\boldsymbol{B}}_{i,T}= \frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{Z}}_{i}$ \\
\end{myAssu}

Then, the IV estimator can be expressed as
\begin{align}
\boldsymbol{\hat{\theta}}_{IV,i}=\left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{g}}_{i,T},
\end{align}
where
\begin{align}
\tilde{\boldsymbol{g}}_{i,T}=\frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{y}}_{i},
\end{align}
 and $\tilde{\boldsymbol{W}}_{i}=\left( \tilde{w}^{'}_{i,1},\ldots, \tilde{w}^{'}_{i,T} \right)^{'}$ is $T \times 2$ matrix

From above equation, we have
\begin{align}
\sqrt{T}\left(\boldsymbol{\hat{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)=\left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\left(T^{-1/2}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \right)
\end{align}
Then, the property of $T^{-1/2}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} $ is given by following proposition.\\
\begin{myProp}
Under above assumptions, as $\left(N, T \right)\overset{j}{\to} \infty$ such that $N/T \to c$ with $0 < c<\infty $, for each $i$, we have
\begin{align}
\begin{split}
&N^{-1} \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}\overset{p}{\to} \boldsymbol{0},  \\
&\,\,\,\,and\,\,\,\,\, \\
&T^{-1/2}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{i} \right).
\end{split}
\end{align}
\end{myProp}

Thus, IV  estimator, $\boldsymbol{\theta}_{IV, i}$ is $\sqrt{T}$ consistent to $\boldsymbol{\theta}_{i}$ and this estimator does not have Nickell's bias. Then, we have following theorem\\
$\mathbf{Theorem \,\,1}$ \\
As $\left(N,T \right)\to \infty $ such that $N/T \to c$ with $0< c< \infty$. for each $i$,
\begin{align}
\sqrt{T}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right)\overset{d}{\to} N \left(\boldsymbol{0},\,\left(\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}\boldsymbol{A}_{i} \right)^{-1}\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}   \boldsymbol{\Sigma}_{i}\boldsymbol{B}_{i}^{-1} \boldsymbol{A}_{i}\left(\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}\boldsymbol{A}_{i} \right)\right).
\end{align}

\subsubsection{Mean group IV estimator }
Now, we define the mean group estimator of $\boldsymbol{\theta}$:
\begin{align}
\hat{\boldsymbol{\theta}}_{IVMG}=\frac{1}{N}\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{IVi}.
\end{align}
And we can show that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG}$, as
\begin{align}
\hat{\boldsymbol{\theta}}_{IVMG}-\boldsymbol{\theta}=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}\right)=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}_{i}\right)+\frac{1}{N}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i},
\end{align}
where
\begin{align}
\begin{split}
\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}_{i}\right)&=\frac{1}{N}\sum^{N}_{i=1} \left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)^{-1}\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\left(T^{-1}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \right) \\
&= O_{p}\left(\delta^{-2}_{NT} \right),
\end{split}
\end{align}
where $\delta_{NT}=\min \{\sqrt{N},\,\sqrt{T} \}$.
We note that $\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}=O_{p}\left(N^{-1/2} \right)$, if $\delta_{NT}^{-(2+\varsigma)}\to 0$ for any $\varsigma >0$, we have
\begin{align}
\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{IVMG}-\boldsymbol{\theta}  \right)=\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}+o_{p} \left(1 \right).
\end{align}

And the variance estimator of $\hat{\boldsymbol{\theta}}_{IVMG}$ is given by
\begin{align}
\hat{\boldsymbol{\Sigma}}_{IV,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{IV,i}- \hat{\boldsymbol{\theta}}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}_{IV,i}- \hat{\boldsymbol{\theta}}_{IVMG}\right)^{'}. \label{44}
\end{align}
Follow \citet{Norkute:2019}, we can show that $\hat{\boldsymbol{\Sigma}}_{IV,\lambda}$ is consistent and it does not have small $T$ bias.
Firstly, we decompose $(\ref{44})$ as
\begin{align}
\begin{split}
&\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}_{IVMG}\right)^{'}= \\
& \sum^{N}_{i=1} \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)^{'}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) -\\
&N\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right). \label{45}
\end{split}
\end{align}
Then we can show consistent of $\hat{\boldsymbol{\Sigma}}_{IV,\lambda}$ as
\begin{align}
\begin{split}
&\hat{\boldsymbol{\Sigma}}_{IV,\lambda}-\boldsymbol{\Sigma}_{IV,\lambda}=
 \frac{1}{N-1}\sum^{N}_{i=1}\left( \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}-\boldsymbol{\Sigma}_{IV,\lambda}\right) +\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)^{'} \\
&+\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\frac{1}{N-1}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) -\\
&\frac{N}{N-1}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right)  =o_{p}(1).
\end{split}
\end{align}

Then, we can see that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG} $ as,
\begin{align}
\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{IVMG}-\boldsymbol{\theta}  \right)\overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{IV,\lambda} \right).
\end{align}

\section{Choosing the number of instruments}
When $\{ x_{i,t} \}^{T}_{t=1-j}$ for $j \geq 1$ are available $\left( j+1 \right)$ instruments can be used. And we also know that using more instruments, estimator are more efficient but more biased.

\section{Estimation method on dynamic heterogeneous panel data model with  multifactor error structure}
For convenient, we assume the number of regressor is $1$ and we express the model as
\begin{align}
y_{i,t}=\phi_{i} y_{i,t-1}+ \sum^{k}_{\ell=1}\beta_{\ell i}x_{\ell i,t}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T, \, \ell=1,\ldots, k. \label{46}
\end{align}
Consider the model $(\ref{45})$, we drawn $x_{\ell i,t}$ as
\begin{align}
x_{\ell i,t}=\boldsymbol{\gamma}^{0'}_{xi}\boldsymbol{f}^{0}_{xt}+\varepsilon_{xi,t}
\end{align}
and the idiosyncratic errors of the process for $y_{i,t}$ as
\begin{align}
u_{i,t}=\boldsymbol{\gamma}^{0'}_{yi}\boldsymbol{f}^{0}_{yt}+\varepsilon_{yi,t},
\end{align}
where $\boldsymbol{\gamma}^{0}_{yi}$ and $\boldsymbol{\gamma}^{0}_{xi}$ are $m_{y}\times 1$ and $m_{x}\times 1$ true
 factor loading respectively, $\boldsymbol{f}^{0}_{yt}$  and  $\boldsymbol{f}^{0}_{xt}$ are  $m_{y}\times 1$ and $m_{x}\times 1$ true vector of unobservable factors respectively.
\subsection{Norkutes' (2019) IVMG estimator}
 We asymptotically eliminate the common factor in $\boldsymbol{x}_{i}$ by projecting matrix, $\boldsymbol{M}_{F^{0}_{x}}$.
 \begin{align}
 \boldsymbol{M}_{F^{0}_{x}}=\boldsymbol{I}_{T}-\boldsymbol{F}^{0}_{x}\left(\boldsymbol{F}^{0'}_{x}\boldsymbol{F}^{0}_{x}  \right)^{-1}\boldsymbol{F}^{0'}_{x} ; \boldsymbol{M}_{F^{0}_{x,-1}}=\boldsymbol{I}_{T}-\boldsymbol{F}^{0}_{x,-1}\left(\boldsymbol{F}^{0'}_{x,-1}\boldsymbol{F}^{0}_{x,-1}  \right)^{-1}\boldsymbol{F}^{0'}_{x,-1}
 \end{align}
And using the defactored covariates as instruments, as
\begin{align}
\boldsymbol{Z}_{IVi}=\left(\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{x}_{i}, \boldsymbol{M}_{F^{0}_{x,-1}}\boldsymbol{X}_{i,-1}  \right)
\end{align}

The first step IV estimator can be expressed as
\begin{align}
\begin{split}
\boldsymbol{\hat{\varphi}}_{IVi}&=\left(\left(\frac{\boldsymbol{Z}^{'}_{i}\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{W}_{i}}{T } \right)^{'} \left(\frac{\boldsymbol{Z}^{'}_{i}\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{Z}_{i}}{T}  \right)^{-1}  \left(\frac{\boldsymbol{Z}^{'}_{i}\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{W}_{i}}{T}  \right)\right)^{-1} \\
&\left(\left( \frac{\boldsymbol{Z}^{'}_{i}\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{W}_{i}}{T}  \right)^{'} \left(\frac{\boldsymbol{Z}^{'}_{i}\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{Z}_{i}}{T}  \right)^{-1}  \left(\frac{\boldsymbol{Z}^{'}_{i}\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{y}_{i}}{T}  \right)\right).
\end{split}
\end{align}

\section{Monte Carlo simulation design}
\subsection{dynamic heterogeneous panels data model without error factor structure}
The data generating process:
\begin{align}
\begin{split}
y_{i,t}&= \phi_{i} y_{i,t-1}+ \sum^{k}_{\ell=1}\beta_{\ell i}x_{\ell i,t}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=-49,\ldots,T\, , \\ \label{M1}
x_{\ell i,t}&=\sum^{k}_{\ell=1}\phi_{\ell i}x_{\ell i,t-1}+v_{\ell i,t},
\end{split}
\end{align}
where $u_{i,t}\overset{i.i.d.}{\sim} \mathcal{N}(0,\,1)\,,$ and $v_{\ell i,t}=\rho_{v, \ell}v_{\ell i,t-1}+\left( 1-\rho^{2}_{v, \ell} \right)^{\frac{1}{2}}\varpi_{\ell i,t}, \varpi_{\ell i,t} \overset{i.i.d.}{\sim} U(0.5, 1.5) \, ,\rho_{v, \ell}=0.5.$

The slope coefficients are generated as
\begin{align}
\phi_{i}=\phi+\eta_{\phi i},\,\, \beta_{1,i}=\beta_{1}+\eta_{\beta_{1} i}\, and\, \beta_{2,i}=\beta_{2}+\eta_{\beta_{2}i}.
\end{align}
Here we consider $\phi \in \left\{0.5 \right\}$, $\beta_{1}=3$ and $\beta_{2}=1$. For the design of heterogenous slopes, $\eta_{\phi i} \overset{i.i.d.}{\sim} U\left( -c, c\right)$, and
\begin{align}
\eta_{\beta_{\ell}i}= \left(1-\rho^{2}_{\beta}  \right)^{1/2}\eta_{\phi i}.
\end{align}
Here, we set $c=0.2,\, \rho_{\beta}=0.4$ for $\ell=1,2.$

\subsection{Dynamic heterogeneous panels data model with multi-factor error structure}
This Monte Carlo simulation design same as \citet{Norkute:2019}.
For convenience, we rewrite the data generating process as bellow
\begin{align}
y_{i,t}=\alpha_{i}+\phi_{i} y_{i,t-1}+ \sum^{k}_{\ell=1}\beta_{\ell i}x_{\ell i,t}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=-49,\ldots,T\, . \\ \label{M1}
\end{align}
We allow error factor structure in the model as
\begin{align}
u_{i,t}=    \sum^{m_{y}}_{s=1}\gamma^{0}_{si}f^{0}_{s,t} +\varepsilon_{i,t},
\end{align}
where
\begin{align}
f^{0}_{s,t}=\rho^{0}_{s,t} f^{0}_{s,t-1}+\left( 1-\rho^{2}_{fs} \right)^{1/2}\zeta_{s,t},
\end{align}
with $\zeta_{s,t} \overset{i.i.d.}{\sim} N(0,1)$ for $s=1,\ldots m_{y}$. We assume $k=2$ and $m_{y}=1+k=3$ and set $\rho^{0}_{s,t}=0.5$ for all $s$. The error term, $\varepsilon_{i,t}$, setting as
\begin{align}
\varepsilon_{i,t}=\varsigma_{\varepsilon}\sigma_{it}\left(\epsilon_{it}-1 \right)/\sqrt{2},
\end{align}
where $ \epsilon_{it}\overset{i.i.d.}{\sim} \chi^{2}_{1},\, \sigma^{2}_{it}=\eta_{i}\varphi_{t}, \,\eta_{i}\overset{i.i.d.}{\sim}\chi^{2}_{2}/2,$  and  $\varphi_{t}=t/T\, for \,\, t=0,\ldots, T.$ And we set
\begin{align}
\varsigma_{\varepsilon}=\frac{\pi_{\mu}}{1-\pi_{\mu}}m_{y}.
\end{align}
we set $\pi_{\mu} \in \left\{ 3/4\right\}.$

The process of regressors is
\begin{align}
x_{\ell it}=\mu_{\ell i}++\sum^{k}_{\ell=1}\phi_{\ell i}x_{\ell i,t-1}+\sum^{m_{x}}_{s=1}\gamma^{0}_{\ell si}f^{0}_{s,t}+v_{\ell it}, \,\, for\,\,i=1,\ldots N;\,t=-49,\ldots,T\,; \, \ell=1,2.
\end{align}
We set number of factor, $m_{x}$, is $2$. Therefore, $\boldsymbol{f}^{0}_{y,t}=\left(f^{0}_{1t}, f^{0}_{2t},f^{0}_{3t}  \right)^{'}$ and $\boldsymbol{f}^{0}_{x,t}=\left(f^{0}_{1t}, f^{0}_{2t}  \right)^{'}.$
We set
\begin{align}
v_{\ell i,t}=\rho_{v, \ell}v_{\ell i,t-1}+\left( 1-\rho^{2}_{v, \ell} \right)^{\frac{1}{2}}\varpi_{\ell i,t},  for \, \ell=1,2,
\end{align}
  where $\rho_{v, \ell}=0.5$ for all $\ell$.
The individual effect is
\begin{align}
 \alpha^{\ast}_{i}\overset{i.i.d.}{\sim} N\left(0, (1-\rho_{i})^{2} \right), \,\, \mu^{\ast}_{\ell i}=\rho_{\mu,\ell}\alpha^{\ast}_{i}+\left( 1-\rho^{2}_{\mu,\ell} \right)^{1/2}\omega_{\ell i},
\end{align}
where $\omega \overset{i.i.d.}{\sim}N\left(0, (1-\rho_{i})^{2} \right)$ and $\rho_{\mu,\ell}=0.5$.

Now, we define the factor loading in $u_{i,t}$ are generated as $\gamma^{0\ast}_{si}\overset{i.i.d.}{\sim}N\left(0, 1 \right)$, for $s=1,\ldots, m_{y}=3$, and the factor loading in $x_{1it}$ and $x_{2it}$ are drawn as
\begin{align}
\begin{split}
\gamma^{0\ast}_{1si}&=\rho_{\gamma,1s} \gamma^{0\ast}_{3i}+\left(1-\rho^{2}_{\gamma,1s}  \right)^{1/2}\xi_{1si};\,\xi_{1si}\overset{i.i.d.}{\sim}N\left(0, 1 \right); \\
\gamma^{0\ast}_{2si}&=\rho_{\gamma,2s} \gamma^{0\ast}_{si}+\left(1-\rho^{2}_{\gamma,2s}  \right)^{1/2}\xi_{2si};\,\xi_{2si}\overset{i.i.d.}{\sim}N\left(0, 1 \right);
\end{split}
\end{align}
for $s=1,\ldots, m_{x}=2$. We set $\rho_{\gamma, 11}=\rho_{\gamma, 12} \in \left\{ 0.5 \right\}$ and $\rho_{\gamma, 21}=\rho_{\gamma, 22}=0.5.$
The factor loading are generated as
\begin{align}
\boldsymbol{\Gamma}=\boldsymbol{\Gamma}^{0}+\boldsymbol{\Gamma}^{0\ast}_{i}
\end{align}
where
\begin{align}
\boldsymbol{\Gamma}^{0}_{i}=
\begin{bmatrix}
\gamma^{0}_{1i} & \gamma^{0}_{11i} & \gamma^{0}_{21i} \\
\gamma^{0}_{2i} & \gamma^{0}_{12i} & \gamma^{0}_{22i} \\
\gamma^{0}_{3i} &  0               &     0
\end{bmatrix}
\end{align}
and
\begin{align}
\boldsymbol{\Gamma}^{0\ast}_{i}=
\begin{bmatrix}
\gamma^{0\ast}_{1i} & \gamma^{0\ast}_{11i} & \gamma^{0\ast}_{21i} \\
\gamma^{0\ast}_{2i} & \gamma^{0\ast}_{12i} & \gamma^{0\ast}_{22i} \\
\gamma^{0\ast}_{3i} &  0               &     0
\end{bmatrix}.
\end{align}
We set
\begin{align}
\boldsymbol{\Gamma}^{0}=
\begin{bmatrix}
1/4 & 1/4 & -1 \\
1/2 & -1  & 1/4 \\
1/2 & 0   & 0
\end{bmatrix} .
\end{align}
And
\begin{align}
\alpha_{i}=\alpha+ \alpha^{\ast}_{i}, \, \mu_{\ell i}= \mu_{\ell}+\mu^{\ast}_{\ell i},
\end{align}
where $\alpha=1/2$, $\mu_{1}=1$, $\mu_{2}=-1/2$.

The slope coefficients are generated as
\begin{align}
\phi_{i}=\phi+\eta_{\phi i},\,\, \beta_{1,i}=\beta_{1}+\eta_{\beta_{1} i}\, and\, \beta_{2,i}=\beta_{2}+\eta_{\beta_{2}i}.
\end{align}
Here we consider $\phi \in \left\{0.5\right\}$, $\beta_{1}=3$ and $\beta_{2}=1$. For the design of heterogenous slopes, $\eta_{\phi i} \overset{i.i.d.}{\sim} U\left( -c, c\right)$, and
\begin{align}
\eta_{\beta_{\ell}i}=\left[(2c)^{2}/12 \right]\rho_{\beta}\xi_{\beta \ell i}+ \left(1-\rho^{2}_{\beta}  \right)^{1/2}\eta_{\phi i},
\end{align}
where
\begin{align}
\xi_{\beta \ell i}=\frac{\bar{v^{2}_{\ell i}}- \bar{v^{2}_{\ell}}}{\left[ N^{-1}\sum^{N}_{i=1} \left( \bar{v^{2}_{\ell i}}- \bar{v^{2}_{\ell }}\right)^{2} \right]^{1/2} },
\end{align}
with $\bar{v^{2}_{ell i}}=T^{-1}\sum^{T}_{t=1}v^{2}_{\ell i t}$, $\bar{v^{2}_{\ell}}=N^{-1} \sum^{N}_{i=1} \bar{v^{2}_{\ell i}}$, for $\ell=1,2.$
Here, we set $c=0.2,\, \rho_{\beta}=0.4$ for $\ell=1,2.$ And
\begin{align}
\varsigma^{2}_{v}=\varsigma^{2}_{\varepsilon}\left[SNR-\frac{\rho^{2}_{v}}{1-\rho^{2}_{v}}   \right]\left(\frac{\beta^{2}_{1}+\beta^{2}_{2}}{1-\rho^{2}_{v}}  \right)^{-1},
\end{align}

where $SNR=4$. For the $(T,N)$, we consider $T \in \left\{25, 50, 100, 200  \right\}$ and  $N \in \left\{25, 50, 100, 200  \right\}.$

\section{Monte Carlo simulation results}
\subsection{Dynamic Heterogeneous Panels without multifactor error structure }
We consider ARDL(1,0) model. \\
$\phi \in \left\{0.5 \right\}.$ \\
 $\beta_{1}=3.$ \\
  $\beta_{2}=1.$ \\
$u_{i,t}\overset{i.i.d.}{\sim} \mathcal{N}(0,\,1).$ \\
$\varpi_{\ell i,t} \overset{i.i.d.}{\sim} U(0.5, 1.5).$ \\
$\rho_{v, \ell}=0.5.$ \\
  $c=0.2.$ \\
  $ \rho_{\beta}=0.4.$ \\
 $T \in \left\{25, 50, 100, 200  \right\}.$ \\
 $N \in \left\{25, 50, 100, 200  \right\}.$ \\

LSMG estimator is provided in sheet 1 of MC.xlsx file. \\
IVMG estimator is provided in sheet 2 of MC.xlsx file. \\

\subsection{Dynamic Heterogeneous Panels with multifactor error structure }
We consider ARDL(1,0) model. \\
$\phi \in \left\{0.5 \right\}.$ \\
 $\beta_{1}=3.$ \\
  $\beta_{2}=1.$ \\
  $k=2.$ \\
  $m_{y}=1+k=3.$\\
  $m_{x}=k=2.$\\
$\zeta_{s,t} \overset{i.i.d.}{\sim} N(0,1)$ \\
$\pi_{\mu} \in \left\{ 3/4\right\}.$ \\
$\rho^{0}_{s,t}=0.5.$ \\
$\rho_{v, \ell}=0.5.$\\
 $\rho_{\mu,\ell}=0.5.$ \\
  $\gamma^{0\ast}_{si}\overset{i.i.d.}{\sim}N\left(0, 1 \right).$ \\
 $\xi_{1si}\overset{i.i.d.}{\sim}N\left(0, 1 \right).$ \\
$\xi_{2si}\overset{i.i.d.}{\sim}N\left(0, 1 \right).$ \\
$\rho_{\gamma, 11}=\rho_{\gamma, 12} \in \left\{ 0.5 \right\}.$ \\
$\rho_{\gamma, 21}=\rho_{\gamma, 22}=0.5.$ \\
$
\boldsymbol{\Gamma}^{0}=
\begin{bmatrix}
1/4 & 1/4 & -1 \\
1/2 & -1  & 1/4 \\
1/2 & 0   & 0
\end{bmatrix} .
$ \\
$\alpha=1/2.$ \\
 $\mu_{1}=1.$\\
  $\mu_{2}=-1/2.$ \\
$c=0.2.$ \\
$\rho_{\beta}=0.4.$ \\
$SNR=4.$ \\
$T \in \left\{25, 50, 100, 200  \right\}.$ \\
 $N \in \left\{25, 50, 100, 200  \right\}.$ \\

IVMG estimator is provided in sheet 3 of MC.xlsx file. \\

\section{Short summary}
\subsection{Dynamic Heterogeneous Panels without multifactor error structure}
1. The performance of IVMG estimator is better than LSMG estimator in bias and RMSE.

\subsection{Dynamic Heterogeneous Panels with multifactor error structure}
1. When $N$ and $T$ increase, the performance of IVMG estimator is good in bias and RMSE. \\
Related literature to dynamic Heterogeneous Panels with multifactor error structure: \citet{Chudik:2015} and \citet{Norkute:2019}.\\
Related literature to choosing number of instruments: \citet{Stephen:2001}, \citet{Swanson:2005}, \citet{Marine:2012}, \citet{Bai:2010} and \citet{Kang:2019}.

\newpage

\addcontentsline{toc}{section}{Reference}
\renewcommand\refname{References}
\bibliographystyle{chicago}
\bibliography{1}

\end{document}  \href{*}{*}

### 2019-12-17 Draft_V5.tex
up

@@
 \end{align}
-where $\tilde{\boldsymbol{y}}_{i}=\boldsymbol{F}\boldsymbol{y}_{i}= \left(\tilde{\boldsymbol{y}}_{i,1}, \ldots, \tilde{\boldsymbol{y}}_{i,T-1} \right)^{'}$,  $\tilde{\boldsymbol{W}}_{i}=\boldsymbol{F}\boldsymbol{W}_{i}= \left(\tilde{\boldsymbol{w}}_{i,1}, \ldots, \tilde{\boldsymbol{w}}_{i,T-1} \right)^{'}$ and $\tilde{\boldsymbol{u}}_{i}=\boldsymbol{F}\boldsymbol{u}_{i}= \left(\tilde{\boldsymbol{u}}_{i,1}, \ldots, \tilde{\boldsymbol{u}}_{i,T-1} \right)^{'}$ with $\tilde{\boldsymbol{y}}_{i,t}=c_{t}\left[y_{i,t}-\left(y_{i,t+1}+\cdots+y_{i,T} \right)/\left(T-t \right) \right]$ for $t=1, \ldots, T-1.$
+where $\tilde{\boldsymbol{y}}_{i}=\boldsymbol{F}\boldsymbol{y}_{i}= \left(\tilde{\boldsymbol{y}}_{i,1}, \ldots, \tilde{\boldsymbol{y}}_{i,T-1} \right)^{'}$,  $\tilde{\boldsymbol{W}}_{i}=\boldsymbol{F}\boldsymbol{W}_{i}= \left(\tilde{\boldsymbol{w}}_{i,1}, \ldots, \tilde{\boldsymbol{w}}_{i,T-1} \right)^{'}$ and $\tilde{\boldsymbol{u}}_{i}=\boldsymbol{F}\boldsymbol{u}_{i}= \left(\tilde{\boldsymbol{u}}_{i,1}, \ldots, \tilde{\boldsymbol{u}}_{i,T-1} \right)^{'}$ with $\tilde{\boldsymbol{y}}_{i,t}=c_{t}\left[y_{i,t}-\left(y_{i,t+1}+\cdots+y_{i,T} \right)/\left(T-t \right) \right]$, for $t=1, \ldots, T-1.$
 
@@
 
-Then, we can define IV estimator in fixed effect model of $\boldsymbol{\theta}^{b}_{i}$ as
+Then, we can define IV estimator, $\boldsymbol{\theta}^{b}_{i}$, as
 \begin{align}
@@
 
-The
+If we can observe long lagged length from data, we have many instruments that can be used.
+In empirical study, researchers do not use all past variables as instruments because there are trade off between efficiency and bias.
+But we have not clearly know that the effect of using long lagged length  IV estimator in heterogeneous dynamic panel data model. And how to select the instruments to balance the bias and efficiency.
+
+\citet{Kuersteiner:2010} provided model averaging two stage least squares estimator to balance the bias and efficiency.
+We try to follow this method to construct the optimal instruments.
+We define a weighting vector $\boldsymbol{W}=\left(w_{1}, \ldots, w_{j} \right)^{'}$.
+Then, we can weight $\boldsymbol{P}^{(j)}_{i}$ as
+\begin{align}
+\boldsymbol{P}\left(\boldsymbol{W} \right)= \sum^{J}_{j=1}w_{j} \boldsymbol{P}^{(j)}_{i},
+\end{align}
+where $J$ is maximum number of lagged variables that we can observed. 
+Our goal is choosing $\boldsymbol{W}$ to minimize the approximate mean square error.
 
@@
 
-\section{Choosing the number of instruments}
-When $\{ x_{i,t} \}^{T}_{t=1-j}$ for $j \geq 1$ are available $\left( j+1 \right)$ instruments can be used. And we also know that using more instruments, estimator are more efficient but more biased.
-
 \section{Estimation method on dynamic heterogeneous panel data model with  multifactor error structure}

### 2019-12-18 Draft_V5.tex
up

@@
 \newpage
-\section{Model, asymptotic property of LS and IV estimator}
+\section{Model, asymptotic property of IV estimator}
 \subsection{The models and Assumptions}
@@
 y_{i,t}&=\alpha_{i}+\phi_{i} y_{i,t-1}+ \boldsymbol{x}^{'}_{i,t}\boldsymbol{\beta}_{i}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \\
-&= \boldsymbol{w}^{'}_{i,t}\boldsymbol{\theta}+ \alpha_{i}+u_{i,t}, \label{1}
+&= \boldsymbol{w}^{'}_{i,t}\boldsymbol{\theta}_{i}+ \alpha_{i}+u_{i,t}, \label{1}
 \end{split}
 \end{align}
-where $\boldsymbol{x}_{i,t}$ and $\boldsymbol{\beta}_{i}$ are $k \times 1$ vectors and $\boldsymbol{w}_{i,t}=\left(\phi_{i}, \boldsymbol{\beta}^{'}_{i} \right)^{'}$ is a $\left(1+k\right) \times 1$ vector.
+where $\boldsymbol{x}_{i,t}$ and $\boldsymbol{\beta}_{i}$ are $k \times 1$ vectors, $\boldsymbol{\theta}_{i}=\left(\phi_{i}, \boldsymbol{\beta}^{'}_{i} \right)^{'}$ and $\boldsymbol{w}_{i,t}=\left(y_{i,t-1}, \boldsymbol{x}^{'}_{i,t} \right)^{'}$ is a $\left(1+k\right) \times 1$ vector.
 Stacking the $T$ observations for each $i$, we have
@@
 
-\subsection{IV estimator}
-We use current and lagged values of $\boldsymbol{x}_{i}$ as instruments, as
+\subsection{IV estimation method and asymptotic property}
+\citet{Norkute:2019} propose an IV estimator in dynamic heterogeneous panel data model. 
+They use current and lagged values of $\boldsymbol{x}_{i}$ as instruments, as
+\begin{align}
+\boldsymbol{Z}_{i,t}=\left( \boldsymbol{x}_{i}, \boldsymbol{x}_{i,-1} \right)^{'},
+\end{align}
+where $\boldsymbol{Z}_{i}$ is $T \times  2k$ vector. \\
+
+\begin{myAssu}
+$\boldsymbol{A}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{A}}_{i,T}$ has full column rank, $\boldsymbol{B}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{B}}_{i,T}$ and $\boldsymbol{\Sigma}_{i}=\plim_{T \to \infty} T^{-1}\boldsymbol{Z}^{'}_{i}\boldsymbol{u}_{i} \boldsymbol{u}_{i}^{'}\boldsymbol{Z}$ has positive definite, uniformly, where $\tilde{\boldsymbol{A}}_{i,T}= \frac{1}{T}\boldsymbol{Z}^{'}_{i}\tilde{\boldsymbol{W}}^{b}_{i}$ and $\tilde{\boldsymbol{B}}_{i,T}= \frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\boldsymbol{Z}_{i}$, \\
+where $b = 1$ corresponds to the fixed effects model while $b = 2$ corresponds to the trend models.
+\end{myAssu}
+
+Then, the IV estimator can be expressed as
+\begin{align}
+\boldsymbol{\hat{\theta}}^{b}_{IV,i}=\left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{g}}_{i,T},
+\end{align}
+where
+\begin{align}
+\tilde{\boldsymbol{g}}_{i,T}=\frac{1}{T}\boldsymbol{Z}^{'}_{i}\tilde{\boldsymbol{y}}^{b}_{i},
+\end{align}
+ and $\tilde{\boldsymbol{W}}^{b}_{i}=\left( \tilde{w}^{b}_{i,1},\ldots, \tilde{w}^{b}_{i,T} \right)^{'}$ is $T \times 2k$ matrix
+
+From above equation, we have
+\begin{align}
+\sqrt{T}\left(\boldsymbol{\hat{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i} \right)=\left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\left(T^{-1/2}  \boldsymbol{Z}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \right)
+\end{align}
+Then, the property of $T^{-1/2}  \boldsymbol{Z}^{'}_{i}\tilde{\boldsymbol{u}}_{i} $ is given by following proposition.\\
+\begin{myProp}
+Under above assumptions, as $\left(N, T \right)\overset{j}{\to} \infty$ such that $N/T \to c$ with $0 < c<\infty $, for each $i$, we have
+\begin{align}
+\begin{split}
+&N^{-1} \boldsymbol{Z}^{'}_{i}\tilde{\boldsymbol{u}}_{i}\overset{p}{\to} \boldsymbol{0},  \\
+&\,\,\,\,and\,\,\,\,\, \\
+&T^{-1/2}  \boldsymbol{Z}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{i} \right).
+\end{split}
+\end{align}
+\end{myProp}
+
+Thus, IV  estimator, $\boldsymbol{\theta}^{b}_{IV, i}$ is $\sqrt{T}$ consistent to $\boldsymbol{\theta}_{i}$ and this estimator does not have Nickell's bias. Then, we have following theorem\\
+$\mathbf{Theorem \,\,1}$ \\
+As $\left(N,T \right)\to \infty $ such that $N/T \to c$ with $0< c< \infty$. for each $i$,
+\begin{align}
+\sqrt{T}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i}  \right)\overset{d}{\to} N \left(\boldsymbol{0},\,\left(\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}\boldsymbol{A}_{i} \right)^{-1}\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}   \boldsymbol{\Sigma}_{i}\boldsymbol{B}_{i}^{-1} \boldsymbol{A}_{i}\left(\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}\boldsymbol{A}_{i} \right)\right).
+\end{align}
+
+\subsubsection{Mean group IV estimator }
+Now, we define the mean group estimator of $\boldsymbol{\theta}$:
+\begin{align}
+\hat{\boldsymbol{\theta}}^{b}_{IVMG}=\frac{1}{N}\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}^{b}_{IVi}.
+\end{align}
+And we can show that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG}$, as
+\begin{align}
+\hat{\boldsymbol{\theta}}^{b}_{IVMG}-\boldsymbol{\theta}=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}- \boldsymbol{\theta}\right)=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}- \boldsymbol{\theta}_{i}\right)+\frac{1}{N}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i},
+\end{align}
+where
+\begin{align}
+\begin{split}
+\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}- \boldsymbol{\theta}_{i}\right)&=\frac{1}{N}\sum^{N}_{i=1} \left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)^{-1}\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\left(T^{-1}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \right) \\
+&= O_{p}\left(\delta^{-2}_{NT} \right),
+\end{split}
+\end{align}
+where $\delta_{NT}=\min \{\sqrt{N},\,\sqrt{T} \}$.
+We note that $\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}=O_{p}\left(N^{-1/2} \right)$, if $\delta_{NT}^{-(2+\varsigma)}\to 0$ for any $\varsigma >0$, we have
+\begin{align}
+\sqrt{N}\left(\hat{\boldsymbol{\theta}}^{b}_{IVMG}-\boldsymbol{\theta}  \right)=\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}+o_{p} \left(1 \right).
+\end{align}
+
+And the variance estimator of $\hat{\boldsymbol{\theta}}_{IVMG}$ is given by
+\begin{align}
+\hat{\boldsymbol{\Sigma}}_{IV,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}^{b}_{IV,i}- \hat{\boldsymbol{\theta}}^{b}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}^{b}_{IV,i}- \hat{\boldsymbol{\theta}}^{b}_{IVMG}\right)^{'}.
+\label{44}
+\end{align}
+Follow \citet{Norkute:2019}, we can show that $\hat{\boldsymbol{\Sigma}}_{IV,\lambda}$ is consistent and it does not have small $T$ bias.
+Firstly, we decompose $(\ref{44})$ as
+\begin{align}
+\begin{split}
+&\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}^{b}_{IV,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}^{b}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}^{b}_{IV,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}^{b}_{IVMG}\right)^{'}= \\
+& \sum^{N}_{i=1} \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i} \right)^{'}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i}  \right) -\\
+&N\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}^{b}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}^{b}_{IVMG} \right). \label{45}
+\end{split}
+\end{align}
+Then we can show consistent of $\hat{\boldsymbol{\Sigma}}^{b}_{IV,\lambda}$ as
+\begin{align}
+\begin{split}
+&\hat{\boldsymbol{\Sigma}}^{b}_{IV,\lambda}-\boldsymbol{\Sigma}_{IV,\lambda}=
+ \frac{1}{N-1}\sum^{N}_{i=1}\left( \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}-\boldsymbol{\Sigma}_{IV,\lambda}\right) +\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i} \right)^{'} \\
+&+\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\frac{1}{N-1}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i}  \right) -\\
+&\frac{N}{N-1}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}^{b}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}^{b}_{IVMG} \right)  =o_{p}(1).
+\end{split}
+\end{align}
+
+Then, we can see that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG} $ as,
+\begin{align}
+\sqrt{N}\left(\hat{\boldsymbol{\theta}}^{b}_{IVMG}-\boldsymbol{\theta}  \right)\overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{IV,\lambda} \right).
+\end{align}
+
+\section{Construction optimal instruments}
+How to select optimal instruments is important issue in empirical studies.
+\citet{Stephen:2001}, \citet{Kuersteiner:2010}, \citet{Ryo:2011}, \citet{Kang:2019} and \citet{Seojeong:2019} propose different methods to construct optimal instruments.
+Here, we try to apply model average approach by \citet{Kuersteiner:2010} in here.
+
+If we can observed long past periods variables, we have many instruments. In this case we define our instruments, as
 \begin{align}
@@
 We try to follow this method to construct the optimal instruments.
-We define a weighting vector $\boldsymbol{W}=\left(w_{1}, \ldots, w_{j} \right)^{'}$.
+We define a weighting vector $\boldsymbol{H}=\left(h_{1}, \ldots, h_{j} \right)^{'}$.
 Then, we can weight $\boldsymbol{P}^{(j)}_{i}$ as
 \begin{align}
-\boldsymbol{P}\left(\boldsymbol{W} \right)= \sum^{J}_{j=1}w_{j} \boldsymbol{P}^{(j)}_{i},
+\boldsymbol{P}\left(\boldsymbol{H} \right)= \sum^{J}_{j=1}h_{j} \boldsymbol{P}^{(j)}_{i},
 \end{align}
 where $J$ is maximum number of lagged variables that we can observed. 
-Our goal is choosing $\boldsymbol{W}$ to minimize the approximate mean square error.
-
-\subsection{Asymptotic property of LS estimator}
-
-Based on heterogenous dynamic panel data model $(\ref{1})$, we can obtain fixed effect estimator as
-\begin{align}
-\hat{\boldsymbol{\theta}}_{LS,i}=
-\begin{pmatrix}
-\hat{\phi}_{i} \\
-\hat{\beta}_{i}
-\end{pmatrix}=
-\begin{pmatrix}
-\frac{\sum^{T}_{t=1}\tilde{y}^{2}_{i,t-1}}{T} & \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{x}_{i,t}}{T} \\
-\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t-1}}{T} &  \frac{\sum^{T}_{t=1}\tilde{x}_{i,t}^{2}}{T}
-\end{pmatrix}^{-1}
-\begin{pmatrix}
-\frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{y}_{i,t}}{T} \\
-\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t}}{T}
-\end{pmatrix},
-\end{align}
-
-where $\tilde{y}_{i,t}=y_{i,t}-\bar{y}_{i}$, $\tilde{y}_{i,t-1}=y_{i,t-1}-\bar{y}_{i,-1}\iota_{T}$ and $\tilde{x}_{i,t}=x_{i,t}-\bar{x}_{i}$ with $\bar{y}_{i}=\frac{1}{T}\sum^{T}_{t=1}y_{i,t}$, $\bar{y}_{i,-1}=\frac{1}{T}\sum^{T}_{t=1}y_{i,t-1}$,  $\bar{x}_{i}=\frac{1}{T}\sum^{T}_{t=1}x_{i,t}$.
-Under equation $(\ref{1})$, we have
-\begin{align}
-\begin{pmatrix}
-\hat{\phi}_{i}-\phi_{i} \\
-\hat{\beta}_{i}-\beta_{i}
-\end{pmatrix}=
-\begin{pmatrix}
-\frac{\sum^{T}_{t=1}\tilde{y}^{2}_{i,t-1}}{T} & \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{x}_{i,t}}{T} \\
-\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t-1}}{T} &  \frac{\sum^{T}_{t=1}\tilde{x}_{i,t}^{2}}{T}
-\end{pmatrix}^{-1}
-\begin{pmatrix}
-\frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{u}_{i,t}}{T} \\
-\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{u}_{i,t}}{T}
-\end{pmatrix},
-\end{align}
-where $\tilde{u}_{i,t}$ is $u_{i,t}-\bar{u}_{i}$ with $\bar{u}_{i}=\frac{1}{T}\sum^{T}_{t=1}u_{i,t}.$
-
-Now, we can investigate asymptotic bias by taking the probability limit as
-\begin{align}
-A^{(1)}_{\phi i}=\plim_{T  \rightarrow \infty}\left( \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{u}_{i,t}}{T} \right). \label{11}
-\end{align}
-Then $A^{(1)}_{i}$ can be taken expectations as
-\begin{align}
-\begin{split}
-A^{(1)}_{\phi i}&=E\left(y_{i,t-1}-\bar{y}_{i,-1} \right) \left(u_{i,t}-\bar{u}_{i} \right) \\
-&= E\left( y_{i,t-1}u_{i,t}\right) - E\left( y_{i,t-1} \bar{u}_{i}  \right)-E\left(\bar{y}_{i,-1}   u_{i,t}\right)+E\left(\bar{y}_{i,-1}  \bar{u}_{i}\right),
-\end{split}
-\end{align}
-where $E\left( y_{i,t-1}u_{i,t}\right)=0$.
-
-And we assume $y_{i,t}$ has started from a long time period in the past, so we have
-\begin{align}
-y_{i,t}=\frac{\alpha_{i}}{\left(1-\phi_{i} \right)}+\sum^{\infty}_{s=0}\beta_{i}\phi^{s}_{i}x_{i,t -s}+\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s},
-\end{align}
-
-Then, we have
-\begin{align}
-\begin{split}
-A^{(1)}_{\phi i}&=-E\left( \left(\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right) \left(\frac{1}{T}\sum^{T}_{t=1}u_{i,t} \right)  \right)-E\left(\frac{u_{i,t}}{T}\sum^{T}_{t=1}\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right)+ \\
-&\left(\frac{1}{T}\sum^{T}_{t=1}\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right)\left( \frac{1}{T}\sum^{T}_{t=1}u_{i,t} \right). \label{12}
-\end{split}
-\end{align}
- Hence, from above equation, we have
- \begin{equation}
-\begin{split}
-A^{(1)}_{\phi i}=&-\dfrac{1}{T} E\left\{  \left( u_{i,t-1}+u_{i,t-2}\phi_{i}^{1}+u_{i,t-3}\phi_{i}^{2}+\ldots\right)\left(u_{i,1}+\ldots+u_{i,t-1}+u_{i,t}+\ldots+u_{i,T}\right) \right\} -\\
- &\dfrac{1}{T} E \left\{  u_{i,t}\sum^{T}_{s=1}\left( u_{i,s-1}\phi_{i}^{0}+u_{i,s-2}\phi_{i}^{1}+\ldots+u_{i,s-t-1}\phi_{i}^{t}+\ldots+u_{i,s-T-1}\phi_{i}^{T}+\ldots \right)  \right\}  + \\
- +& \dfrac{1}{T} E\{ \left( \sum^{T}_{s=1}u_{i,s-1}\phi_{i}^{0}+\sum^{T}_{s=1}u_{i,s-2}\phi_{i}^{1}+\ldots+\sum^{T}_{s=1}u_{i,s-t-1}\phi_{i}^{t}+\ldots
-+\sum^{T}_{s=1}u_{is-T-1}\phi_{i}^{T}+\ldots \right)\\
- &\left(\dfrac{1}{T}\sum^{T}_{s=1}u_{i,s}\right) \} \\
- =&-\dfrac{\sigma_{u}^{2}}{T}\dfrac{(1-\phi_{i}^{t-1})}{1-\phi_{i}}-\dfrac{\sigma^{2}_{u}}{T}\dfrac{(1-\phi_{i}^{T-t})}{(1-\phi_{i})}+\dfrac{\sigma^{2}_{u}}{T} \left( \dfrac{1}{1-\phi_{i}}-\dfrac{1}{T}\dfrac{(1-\phi_{i}^{T})}{(1-\phi_{i})^{2}}\right) \\
- =&-\dfrac{\sigma_{u}^{2}}{T(1-\phi_{i})}\left( 1-\phi_{i}^{t-1}-\phi_{i}^{T-t}+\dfrac{1}{T}\dfrac{(1-\phi_{i}^{T})}{(1-\phi_{i})}  \right).
- \end{split}
-\end{equation}
-
-Therefore, we can see the bias of $\hat{\phi}_{i}$ is $O\left(T^{-1}\right)$.
-
-To be more compact ,we can rewrite the model as,
-\begin{align}
-\tilde{\boldsymbol{y}}_{i}=\tilde{\boldsymbol{W}}_{i}\boldsymbol{\theta}_{i}+\tilde{\boldsymbol{u}}_{i},
-\end{align}
-where $\tilde{\boldsymbol{y}}_{i}=\left(\tilde{\boldsymbol{y}}_{i,1},\ldots, \tilde{\boldsymbol{y}}_{i,T}  \right)^{'}$ is $T \times 1$ vector,  $\tilde{\boldsymbol{W}}_{i}=\left( \tilde{\boldsymbol{w}}_{i,1},\ldots, \tilde{\boldsymbol{w}}_{i,T} \right)^{'}$ is $T \times 2$ matrix and $\tilde{\boldsymbol{u}}_{i}=\left(\tilde{\boldsymbol{u}}_{i,1}, \ldots, \tilde{\boldsymbol{u}}_{i,T} \right)$ is $T \times 1$ vector with $\tilde{\boldsymbol{w}}_{i,t}=\left(y_{i,t-1}-\bar{y}_{i,-1}, x_{i,t}-\bar{x}_{i}  \right)^{'}$, for $t=1,\ldots, T$ and $i=1,\ldots, N.$
-
-Also, we define our interested parameter as
-\begin{align}
-\left(\phi_{i},\beta_{i}  \right)^{'}=\boldsymbol{\theta}_{i}=\boldsymbol{\theta}+\boldsymbol{\lambda}_{i},
-\end{align}
-where $\boldsymbol{\lambda}_{i}\overset{i.i.d.}{\sim} \left(\boldsymbol{0}, \boldsymbol{\Sigma}_{\lambda} \right).$
-The lest square estimator, $\hat{\boldsymbol{\theta}}_{LS,i}$, can be expressed as
-\begin{align}
-\hat{\boldsymbol{\theta}}_{LS,i}=\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{y}}_{i}}{T}. \label{13}
-\end{align}
-
-From above discussion and assumptions, we have following theorem \\
-\begin{myTheo}
-\begin{align}
-\sqrt{T}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}\right) \overset{d}{\to} N \left(\boldsymbol{0}, \boldsymbol{Q}_{i}^{-1}\boldsymbol{\Sigma}_{LS,i}\boldsymbol{Q}_{i}^{-1}  \right),
-\end{align}
-where $\boldsymbol{\Sigma}_{LS,i}=\plim_{T \to \infty} T^{-1}\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{u}}_{i} \tilde{\boldsymbol{u}}^{'}_{i}  \tilde{\boldsymbol{W}}_{i} $ and $\boldsymbol{Q}_{i}=\plim_{T \to \infty} T^{-1}\tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{W}}_{i}$
-\end{myTheo}
-
-\subsubsection{Mean group LS estimator }
-Now, we define the mean group estimator of $\boldsymbol{\theta}$:
-\begin{align}
-\hat{\boldsymbol{\theta}}_{LSMG}=\frac{1}{N}\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSi}.
-\end{align}
-And we can show that the asymptotic property of $\hat{\boldsymbol{\theta}}_{LSMG}$, as
-\begin{align}
-\begin{split}
-\hat{\boldsymbol{\theta}}_{LSMG}&=N^{-1}\sum^{N}_{i=1}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{y}}_{i}}{T} \\
-&=\bar{\boldsymbol{\theta}}+N^{-1}\sum^{N}_{i=1}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T},
-\end{split}
-\end{align}
-where $\bar{\boldsymbol{\theta}}=N^{-1}\sum^{N}_{i=1}\boldsymbol{\theta}_{i}.$
-For fixed $N$ and large $T$, we have
-\begin{align}
-\plim_{T \to \infty}\hat{\boldsymbol{\theta}}_{LSMG} =  \bar{\boldsymbol{\theta}}+ N^{-1}\sum^{N}_{i=1}\plim_{T \to \infty}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1}\plim_{T \to \infty}\left( \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T}\right)
-\end{align}
- Then, from section $1.1$, we know that $\plim_{T \to \infty}\left( \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T}\right)=O_{p}(1)$. Thus,  we can obtain
-\begin{align}
-\plim_{T \to \infty}\hat{\boldsymbol{\theta}}_{LSMG} =  \bar{\boldsymbol{\theta}}.
-\end{align}
-When $N \to \infty$ and $T \to \infty$ and by the law of large numbers, we can see that
-\begin{align}
-\plim_{T \to \infty, N \to \infty}\hat{\boldsymbol{\theta}}_{LSMG}=\boldsymbol{\theta}.
-\end{align}
-
-And the variance estimator of $\hat{\boldsymbol{\theta}}_{LSMG}$ is given by
-\begin{align}
-\hat{\boldsymbol{\Sigma}}_{LS,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}.
-\end{align}
-
-We show that $\hat{\boldsymbol{\Sigma}}_{LS,\lambda}$ is consistent when $N \to \infty$ and $T \to \infty.$
-\begin{align}
-\begin{split}
-&\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}=\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right) \right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'}\\
-&+\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right) \left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'}\\
-&-\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right) \left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'} \\
-&-\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right) \left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'}.
-\label{20}
-\end{split}
-\end{align}
-
-Taking expectation on equation $(\ref{20})$, we have
-\begin{align}
-\begin{split}
-&E\left( \sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'} \right)=
- \sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)+
-\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG}+  \\
-&\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right) E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}-
-\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LS,i}+
-\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)\hat{\boldsymbol{\theta}}^{'}_{LS,i}-
-\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSMG}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}- \\
-&\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LSMG}+
-\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LS,i}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}-
-\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right) E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'} = \\
-&\sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)-N E \left(\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG} \right)+\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right) E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}
-\end{split}
-\end{align}
-and
-\begin{align}
-E \left(\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG} \right)=\frac{1}{N^{2}} \sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right).
-\end{align}
-
-And, we also have
-\begin{align}
-E \left(\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG} \right)=\frac{1}{N^{2}}\left( \sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)+ \sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right) \right).
-\end{align}
-Then,
-\begin{align}
-\begin{split}
-&E\left( \sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'} \right)= \\
-&\left(1-\frac{1}{N} \right)\sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)+ \sum^{N}_{i=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right)- \frac{1}{N}\sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right).
-\label{24}
-\end{split}
-\end{align}
-From above equation $(\ref{24})$, we can observe the bias term as,
-\begin{align}
-\aleph=\sum^{N}_{i=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right)- \frac{1}{N}\sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right).
-\label{25}
-\end{align}
-
- Taking expectation on equation $(26)$, we have
-\begin{align}
-E\left( \hat{\boldsymbol{\theta}}_{LS,i} \right)=\boldsymbol{\theta}+E \left(b_{i} \right),
-\end{align}
-From equation $(\ref{25})$, we know that
- \begin{align}
-\aleph=\sum^{N}_{i=1}E \left(b_{i}\right) E\left(b^{'}_{i} \right)- \frac{1}{N}\sum^{N}_{i=1}\sum^{N}_{j=1}E \left(b_{i}\right) E\left(b^{'}_{j} \right).
- \end{align}
-When $T \to \infty$, $\aleph=0$.
-Therefore, we have following theorem \\
-
-\begin{myTheo}
-When $(T,N) \overset{j}{\to} \infty$ such that $N/T \to c$ with $0<c< \infty$,
-\begin{enumerate}
-\item \begin{align}
-\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{LSMG}-\boldsymbol{\theta}  \right)\overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{LS,\lambda} \right).
-\end{align}
-\item \begin{align}
-\hat{\boldsymbol{\Sigma}}_{LS,\lambda} \overset{p}{\to}  \boldsymbol{\Sigma}_{LS,\lambda}
-\end{align}
-where
-\begin{align}
- \hat{\boldsymbol{\Sigma}}_{LS,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}.
-\end{align}
-\end{enumerate}
-\end{myTheo}
-
-\subsection{Asymptotic property of IV estimator}
-We use current and lagged values of $\boldsymbol{x}_{i}$ as instruments, as
-\begin{align}
-\tilde{\boldsymbol{Z}}_{i,t}=\left( \tilde{\boldsymbol{x}}_{i}, \tilde{\boldsymbol{x}}_{i,-1} \right)^{'},
-\end{align}
-where $\tilde{\boldsymbol{Z}}_{i}$ is $T \times  2$ vector. \\
-
-\begin{myAssu}
-$\boldsymbol{A}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{A}}_{i,T}$ has full column rank, $\boldsymbol{B}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{B}}_{i,T}$ and $\boldsymbol{\Sigma}_{i}=\plim_{T \to \infty} T^{-1}\boldsymbol{Z}^{'}_{i}\boldsymbol{u}_{i} \boldsymbol{u}_{i}^{'}\boldsymbol{Z}$ has positive definite, uniformly, where $\tilde{\boldsymbol{A}}_{i,T}= \frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{W}}_{i}$ and $\tilde{\boldsymbol{B}}_{i,T}= \frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{Z}}_{i}$ \\
-\end{myAssu}
-
-Then, the IV estimator can be expressed as
-\begin{align}
-\boldsymbol{\hat{\theta}}_{IV,i}=\left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{g}}_{i,T},
-\end{align}
-where
-\begin{align}
-\tilde{\boldsymbol{g}}_{i,T}=\frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{y}}_{i},
-\end{align}
- and $\tilde{\boldsymbol{W}}_{i}=\left( \tilde{w}^{'}_{i,1},\ldots, \tilde{w}^{'}_{i,T} \right)^{'}$ is $T \times 2$ matrix
-
-From above equation, we have
-\begin{align}
-\sqrt{T}\left(\boldsymbol{\hat{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)=\left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\left(T^{-1/2}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \right)
-\end{align}
-Then, the property of $T^{-1/2}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} $ is given by following proposition.\\
-\begin{myProp}
-Under above assumptions, as $\left(N, T \right)\overset{j}{\to} \infty$ such that $N/T \to c$ with $0 < c<\infty $, for each $i$, we have
-\begin{align}
-\begin{split}
-&N^{-1} \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}\overset{p}{\to} \boldsymbol{0},  \\
-&\,\,\,\,and\,\,\,\,\, \\
-&T^{-1/2}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{i} \right).
-\end{split}
-\end{align}
-\end{myProp}
-
-Thus, IV  estimator, $\boldsymbol{\theta}_{IV, i}$ is $\sqrt{T}$ consistent to $\boldsymbol{\theta}_{i}$ and this estimator does not have Nickell's bias. Then, we have following theorem\\
-$\mathbf{Theorem \,\,1}$ \\
-As $\left(N,T \right)\to \infty $ such that $N/T \to c$ with $0< c< \infty$. for each $i$,
-\begin{align}
-\sqrt{T}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right)\overset{d}{\to} N \left(\boldsymbol{0},\,\left(\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}\boldsymbol{A}_{i} \right)^{-1}\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}   \boldsymbol{\Sigma}_{i}\boldsymbol{B}_{i}^{-1} \boldsymbol{A}_{i}\left(\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}\boldsymbol{A}_{i} \right)\right).
-\end{align}
-
-\subsubsection{Mean group IV estimator }
-Now, we define the mean group estimator of $\boldsymbol{\theta}$:
-\begin{align}
-\hat{\boldsymbol{\theta}}_{IVMG}=\frac{1}{N}\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{IVi}.
-\end{align}
-And we can show that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG}$, as
-\begin{align}
-\hat{\boldsymbol{\theta}}_{IVMG}-\boldsymbol{\theta}=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}\right)=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}_{i}\right)+\frac{1}{N}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i},
-\end{align}
-where
-\begin{align}
-\begin{split}
-\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}_{i}\right)&=\frac{1}{N}\sum^{N}_{i=1} \left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)^{-1}\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\left(T^{-1}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \right) \\
-&= O_{p}\left(\delta^{-2}_{NT} \right),
-\end{split}
-\end{align}
-where $\delta_{NT}=\min \{\sqrt{N},\,\sqrt{T} \}$.
-We note that $\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}=O_{p}\left(N^{-1/2} \right)$, if $\delta_{NT}^{-(2+\varsigma)}\to 0$ for any $\varsigma >0$, we have
-\begin{align}
-\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{IVMG}-\boldsymbol{\theta}  \right)=\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}+o_{p} \left(1 \right).
-\end{align}
-
-And the variance estimator of $\hat{\boldsymbol{\theta}}_{IVMG}$ is given by
-\begin{align}
-\hat{\boldsymbol{\Sigma}}_{IV,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{IV,i}- \hat{\boldsymbol{\theta}}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}_{IV,i}- \hat{\boldsymbol{\theta}}_{IVMG}\right)^{'}.
-\label{44}
-\end{align}
-Follow \citet{Norkute:2019}, we can show that $\hat{\boldsymbol{\Sigma}}_{IV,\lambda}$ is consistent and it does not have small $T$ bias.
-Firstly, we decompose $(\ref{44})$ as
-\begin{align}
-\begin{split}
-&\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}_{IVMG}\right)^{'}= \\
-& \sum^{N}_{i=1} \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)^{'}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) -\\
-&N\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right). \label{45}
-\end{split}
-\end{align}
-Then we can show consistent of $\hat{\boldsymbol{\Sigma}}_{IV,\lambda}$ as
-\begin{align}
-\begin{split}
-&\hat{\boldsymbol{\Sigma}}_{IV,\lambda}-\boldsymbol{\Sigma}_{IV,\lambda}=
- \frac{1}{N-1}\sum^{N}_{i=1}\left( \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}-\boldsymbol{\Sigma}_{IV,\lambda}\right) +\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)^{'} \\
-&+\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\frac{1}{N-1}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) -\\
-&\frac{N}{N-1}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right)  =o_{p}(1).
-\end{split}
-\end{align}
-
-Then, we can see that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG} $ as,
-\begin{align}
-\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{IVMG}-\boldsymbol{\theta}  \right)\overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{IV,\lambda} \right).
-\end{align}
+Our goal is estimating $\boldsymbol{H}$ to minimize the approximate mean square error.
 
@@
 \newpage
+\appendix
+\appendixpage
+\section{Asymptotic property of LS estimator}
+
+Based on heterogenous dynamic panel data model $(\ref{1})$, we can obtain fixed effect estimator as
+\begin{align}
+\hat{\boldsymbol{\theta}}_{LS,i}=
+\begin{pmatrix}
+\hat{\phi}_{i} \\
+\hat{\beta}_{i}
+\end{pmatrix}=
+\begin{pmatrix}
+\frac{\sum^{T}_{t=1}\tilde{y}^{2}_{i,t-1}}{T} & \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{x}_{i,t}}{T} \\
+\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t-1}}{T} &  \frac{\sum^{T}_{t=1}\tilde{x}_{i,t}^{2}}{T}
+\end{pmatrix}^{-1}
+\begin{pmatrix}
+\frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{y}_{i,t}}{T} \\
+\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t}}{T}
+\end{pmatrix},
+\end{align}
+
+where $\tilde{y}_{i,t}=y_{i,t}-\bar{y}_{i}$, $\tilde{y}_{i,t-1}=y_{i,t-1}-\bar{y}_{i,-1}\iota_{T}$ and $\tilde{x}_{i,t}=x_{i,t}-\bar{x}_{i}$ with $\bar{y}_{i}=\frac{1}{T}\sum^{T}_{t=1}y_{i,t}$, $\bar{y}_{i,-1}=\frac{1}{T}\sum^{T}_{t=1}y_{i,t-1}$,  $\bar{x}_{i}=\frac{1}{T}\sum^{T}_{t=1}x_{i,t}$.
+Under equation $(\ref{1})$, we have
+\begin{align}
+\begin{pmatrix}
+\hat{\phi}_{i}-\phi_{i} \\
+\hat{\beta}_{i}-\beta_{i}
+\end{pmatrix}=
+\begin{pmatrix}
+\frac{\sum^{T}_{t=1}\tilde{y}^{2}_{i,t-1}}{T} & \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{x}_{i,t}}{T} \\
+\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t-1}}{T} &  \frac{\sum^{T}_{t=1}\tilde{x}_{i,t}^{2}}{T}
+\end{pmatrix}^{-1}
+\begin{pmatrix}
+\frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{u}_{i,t}}{T} \\
+\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{u}_{i,t}}{T}
+\end{pmatrix},
+\end{align}
+where $\tilde{u}_{i,t}$ is $u_{i,t}-\bar{u}_{i}$ with $\bar{u}_{i}=\frac{1}{T}\sum^{T}_{t=1}u_{i,t}.$
+
+Now, we can investigate asymptotic bias by taking the probability limit as
+\begin{align}
+A^{(1)}_{\phi i}=\plim_{T  \rightarrow \infty}\left( \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{u}_{i,t}}{T} \right). \label{11}
+\end{align}
+Then $A^{(1)}_{i}$ can be taken expectations as
+\begin{align}
+\begin{split}
+A^{(1)}_{\phi i}&=E\left(y_{i,t-1}-\bar{y}_{i,-1} \right) \left(u_{i,t}-\bar{u}_{i} \right) \\
+&= E\left( y_{i,t-1}u_{i,t}\right) - E\left( y_{i,t-1} \bar{u}_{i}  \right)-E\left(\bar{y}_{i,-1}   u_{i,t}\right)+E\left(\bar{y}_{i,-1}  \bar{u}_{i}\right),
+\end{split}
+\end{align}
+where $E\left( y_{i,t-1}u_{i,t}\right)=0$.
+
+And we assume $y_{i,t}$ has started from a long time period in the past, so we have
+\begin{align}
+y_{i,t}=\frac{\alpha_{i}}{\left(1-\phi_{i} \right)}+\sum^{\infty}_{s=0}\beta_{i}\phi^{s}_{i}x_{i,t -s}+\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s},
+\end{align}
+
+Then, we have
+\begin{align}
+\begin{split}
+A^{(1)}_{\phi i}&=-E\left( \left(\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right) \left(\frac{1}{T}\sum^{T}_{t=1}u_{i,t} \right)  \right)-E\left(\frac{u_{i,t}}{T}\sum^{T}_{t=1}\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right)+ \\
+&\left(\frac{1}{T}\sum^{T}_{t=1}\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right)\left( \frac{1}{T}\sum^{T}_{t=1}u_{i,t} \right). \label{12}
+\end{split}
+\end{align}
+ Hence, from above equation, we have
+ \begin{equation}
+\begin{split}
+A^{(1)}_{\phi i}=&-\dfrac{1}{T} E\left\{  \left( u_{i,t-1}+u_{i,t-2}\phi_{i}^{1}+u_{i,t-3}\phi_{i}^{2}+\ldots\right)\left(u_{i,1}+\ldots+u_{i,t-1}+u_{i,t}+\ldots+u_{i,T}\right) \right\} -\\
+ &\dfrac{1}{T} E \left\{  u_{i,t}\sum^{T}_{s=1}\left( u_{i,s-1}\phi_{i}^{0}+u_{i,s-2}\phi_{i}^{1}+\ldots+u_{i,s-t-1}\phi_{i}^{t}+\ldots+u_{i,s-T-1}\phi_{i}^{T}+\ldots \right)  \right\}  + \\
+ +& \dfrac{1}{T} E\{ \left( \sum^{T}_{s=1}u_{i,s-1}\phi_{i}^{0}+\sum^{T}_{s=1}u_{i,s-2}\phi_{i}^{1}+\ldots+\sum^{T}_{s=1}u_{i,s-t-1}\phi_{i}^{t}+\ldots
++\sum^{T}_{s=1}u_{is-T-1}\phi_{i}^{T}+\ldots \right)\\
+ &\left(\dfrac{1}{T}\sum^{T}_{s=1}u_{i,s}\right) \} \\
+ =&-\dfrac{\sigma_{u}^{2}}{T}\dfrac{(1-\phi_{i}^{t-1})}{1-\phi_{i}}-\dfrac{\sigma^{2}_{u}}{T}\dfrac{(1-\phi_{i}^{T-t})}{(1-\phi_{i})}+\dfrac{\sigma^{2}_{u}}{T} \left( \dfrac{1}{1-\phi_{i}}-\dfrac{1}{T}\dfrac{(1-\phi_{i}^{T})}{(1-\phi_{i})^{2}}\right) \\
+ =&-\dfrac{\sigma_{u}^{2}}{T(1-\phi_{i})}\left( 1-\phi_{i}^{t-1}-\phi_{i}^{T-t}+\dfrac{1}{T}\dfrac{(1-\phi_{i}^{T})}{(1-\phi_{i})}  \right).
+ \end{split}
+\end{equation}
+
+Therefore, we can see the bias of $\hat{\phi}_{i}$ is $O\left(T^{-1}\right)$.
+
+To be more compact ,we can rewrite the model as,
+\begin{align}
+\tilde{\boldsymbol{y}}_{i}=\tilde{\boldsymbol{W}}_{i}\boldsymbol{\theta}_{i}+\tilde{\boldsymbol{u}}_{i},
+\end{align}
+where $\tilde{\boldsymbol{y}}_{i}=\left(\tilde{\boldsymbol{y}}_{i,1},\ldots, \tilde{\boldsymbol{y}}_{i,T}  \right)^{'}$ is $T \times 1$ vector,  $\tilde{\boldsymbol{W}}_{i}=\left( \tilde{\boldsymbol{w}}_{i,1},\ldots, \tilde{\boldsymbol{w}}_{i,T} \right)^{'}$ is $T \times 2$ matrix and $\tilde{\boldsymbol{u}}_{i}=\left(\tilde{\boldsymbol{u}}_{i,1}, \ldots, \tilde{\boldsymbol{u}}_{i,T} \right)$ is $T \times 1$ vector with $\tilde{\boldsymbol{w}}_{i,t}=\left(y_{i,t-1}-\bar{y}_{i,-1}, x_{i,t}-\bar{x}_{i}  \right)^{'}$, for $t=1,\ldots, T$ and $i=1,\ldots, N.$
+
+Also, we define our interested parameter as
+\begin{align}
+\left(\phi_{i},\beta_{i}  \right)^{'}=\boldsymbol{\theta}_{i}=\boldsymbol{\theta}+\boldsymbol{\lambda}_{i},
+\end{align}
+where $\boldsymbol{\lambda}_{i}\overset{i.i.d.}{\sim} \left(\boldsymbol{0}, \boldsymbol{\Sigma}_{\lambda} \right).$
+The lest square estimator, $\hat{\boldsymbol{\theta}}_{LS,i}$, can be expressed as
+\begin{align}
+\hat{\boldsymbol{\theta}}_{LS,i}=\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{y}}_{i}}{T}. \label{13}
+\end{align}
+
+From above discussion and assumptions, we have following theorem \\
+\begin{myTheo}
+\begin{align}
+\sqrt{T}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}\right) \overset{d}{\to} N \left(\boldsymbol{0}, \boldsymbol{Q}_{i}^{-1}\boldsymbol{\Sigma}_{LS,i}\boldsymbol{Q}_{i}^{-1}  \right),
+\end{align}
+where $\boldsymbol{\Sigma}_{LS,i}=\plim_{T \to \infty} T^{-1}\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{u}}_{i} \tilde{\boldsymbol{u}}^{'}_{i}  \tilde{\boldsymbol{W}}_{i} $ and $\boldsymbol{Q}_{i}=\plim_{T \to \infty} T^{-1}\tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{W}}_{i}$
+\end{myTheo}
+
+\subsubsection{Mean group LS estimator }
+Now, we define the mean group estimator of $\boldsymbol{\theta}$:
+\begin{align}
+\hat{\boldsymbol{\theta}}_{LSMG}=\frac{1}{N}\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSi}.
+\end{align}
+And we can show that the asymptotic property of $\hat{\boldsymbol{\theta}}_{LSMG}$, as
+\begin{align}
+\begin{split}
+\hat{\boldsymbol{\theta}}_{LSMG}&=N^{-1}\sum^{N}_{i=1}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{y}}_{i}}{T} \\
+&=\bar{\boldsymbol{\theta}}+N^{-1}\sum^{N}_{i=1}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T},
+\end{split}
+\end{align}
+where $\bar{\boldsymbol{\theta}}=N^{-1}\sum^{N}_{i=1}\boldsymbol{\theta}_{i}.$
+For fixed $N$ and large $T$, we have
+\begin{align}
+\plim_{T \to \infty}\hat{\boldsymbol{\theta}}_{LSMG} =  \bar{\boldsymbol{\theta}}+ N^{-1}\sum^{N}_{i=1}\plim_{T \to \infty}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1}\plim_{T \to \infty}\left( \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T}\right)
+\end{align}
+ Then, from section $1.1$, we know that $\plim_{T \to \infty}\left( \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T}\right)=O_{p}(1)$. Thus,  we can obtain
+\begin{align}
+\plim_{T \to \infty}\hat{\boldsymbol{\theta}}_{LSMG} =  \bar{\boldsymbol{\theta}}.
+\end{align}
+When $N \to \infty$ and $T \to \infty$ and by the law of large numbers, we can see that
+\begin{align}
+\plim_{T \to \infty, N \to \infty}\hat{\boldsymbol{\theta}}_{LSMG}=\boldsymbol{\theta}.
+\end{align}
+
+And the variance estimator of $\hat{\boldsymbol{\theta}}_{LSMG}$ is given by
+\begin{align}
+\hat{\boldsymbol{\Sigma}}_{LS,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}.
+\end{align}
+
+We show that $\hat{\boldsymbol{\Sigma}}_{LS,\lambda}$ is consistent when $N \to \infty$ and $T \to \infty.$
+\begin{align}
+\begin{split}
+&\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}=\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right) \right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'}\\
+&+\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right) \left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'}\\
+&-\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right) \left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'} \\
+&-\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right) \left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'}.
+\label{20}
+\end{split}
+\end{align}
+
+Taking expectation on equation $(\ref{20})$, we have
+\begin{align}
+\begin{split}
+&E\left( \sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'} \right)=
+ \sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)+
+\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG}+  \\
+&\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right) E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}-
+\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LS,i}+
+\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)\hat{\boldsymbol{\theta}}^{'}_{LS,i}-
+\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSMG}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}- \\
+&\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LSMG}+
+\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LS,i}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}-
+\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right) E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'} = \\
+&\sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)-N E \left(\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG} \right)+\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right) E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}
+\end{split}
+\end{align}
+and
+\begin{align}
+E \left(\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG} \right)=\frac{1}{N^{2}} \sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right).
+\end{align}
+
+And, we also have
+\begin{align}
+E \left(\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG} \right)=\frac{1}{N^{2}}\left( \sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)+ \sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right) \right).
+\end{align}
+Then,
+\begin{align}
+\begin{split}
+&E\left( \sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'} \right)= \\
+&\left(1-\frac{1}{N} \right)\sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)+ \sum^{N}_{i=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right)- \frac{1}{N}\sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right).
+\label{24}
+\end{split}
+\end{align}
+From above equation $(\ref{24})$, we can observe the bias term as,
+\begin{align}
+\aleph=\sum^{N}_{i=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right)- \frac{1}{N}\sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right).
+\label{25}
+\end{align}
+
+ Taking expectation on equation $(26)$, we have
+\begin{align}
+E\left( \hat{\boldsymbol{\theta}}_{LS,i} \right)=\boldsymbol{\theta}+E \left(b_{i} \right),
+\end{align}
+From equation $(\ref{25})$, we know that
+ \begin{align}
+\aleph=\sum^{N}_{i=1}E \left(b_{i}\right) E\left(b^{'}_{i} \right)- \frac{1}{N}\sum^{N}_{i=1}\sum^{N}_{j=1}E \left(b_{i}\right) E\left(b^{'}_{j} \right).
+ \end{align}
+When $T \to \infty$, $\aleph=0$.
+Therefore, we have following theorem \\
+
+\begin{myTheo}
+When $(T,N) \overset{j}{\to} \infty$ such that $N/T \to c$ with $0<c< \infty$,
+\begin{enumerate}
+\item \begin{align}
+\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{LSMG}-\boldsymbol{\theta}  \right)\overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{LS,\lambda} \right).
+\end{align}
+\item \begin{align}
+\hat{\boldsymbol{\Sigma}}_{LS,\lambda} \overset{p}{\to}  \boldsymbol{\Sigma}_{LS,\lambda}
+\end{align}
+where
+\begin{align}
+ \hat{\boldsymbol{\Sigma}}_{LS,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}.
+\end{align}
+\end{enumerate}
+\end{myTheo}
 

### 2019-12-19 Draft_V5.tex
Update Draft_V5.tex
up

@@
+<<<<<<< HEAD
+\documentclass[12pt,a4paper,hyperref]{article}
+\usepackage[usenames,dvipsnames]{xcolor}
+\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
+	\definecolor{ultramarine}{rgb}{0.07, 0.04, 0.56}
+\usepackage{amsmath, natbib, latexsym, array, amssymb,longtable,float, graphicx, appendix,lscape,diagbox,textcomp,placeins}
+\usepackage[colorlinks,
+            linkcolor=ultramarine,
+            anchorcolor=green,
+            citecolor=darkblue
+            ]{hyperref}
+\usepackage[flushleft]{threeparttable}
+\usepackage[top=2.7cm, left=3cm, right=3cm, bottom=2.7cm]{geometry}
+\usepackage{hyperref}
+\newtheorem{myDef}{Definition}
+\newtheorem{myTheo}{Theorem}
+\newtheorem{myProp}{proposition}
+\newtheorem{myRem}{Remark}
+\newtheorem{myAssu}{Assumption}
+\newtheorem{myCor}{Corollary}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=magenta,
+    urlcolor=cyan,
+}
+
+\urlstyle{same}
+\usepackage{booktabs}
+\usepackage{siunitx}
+\usepackage{pgfplotstable}
+\sisetup{
+  round-mode          = places, % Rounds numbers
+  round-precision     = 2, % to 2 places
+}
+
+\newenvironment{sequation}{\begin{equation}\tiny}{\end{equation}}
+\DeclareMathOperator*{\plim}{plim}
+\renewcommand{\floatpagefraction}{0.60}
+\renewcommand{\appendixpagename}{\Large Appendix}
+\setcounter{secnumdepth}{3}
+\begin{document}
+\begin{titlepage}
+
+\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here
+
+\center % Center everything on the page
+
+\HRule \\[0.4cm]
+{ \huge \bfseries Dynamic Heterogeneous Panels }\\[0.4cm] % Title of your document
+\HRule \\[1.5cm]
+
+\vfill % Fill the rest of the page with whitespace
+
+\end{titlepage}
+
+\newpage
+\tableofcontents
+\newpage
+\section{Model, asymptotic property of LS and IV estimator}
+\subsection{The models and Assumptions}
+\subsubsection{Fixed effects model}
+Consider the dynamic heterogeneous panels data model with fixed effects:
+\begin{align}
+\begin{split}
+y_{i,t}&=\alpha_{i}+\phi_{i} y_{i,t-1}+ \boldsymbol{x}^{'}_{i,t}\boldsymbol{\beta}_{i}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \\
+&= \boldsymbol{w}^{'}_{i,t}\boldsymbol{\theta}+ \alpha_{i}+u_{i,t}, \label{1}
+\end{split}
+\end{align}
+where $\boldsymbol{x}_{i,t}$ and $\boldsymbol{\beta}_{i}$ are $k \times 1$ vectors and $\boldsymbol{w}_{i,t}=\left(\phi_{i}, \boldsymbol{\beta}^{'}_{i} \right)^{'}$ is a $\left(1+k\right) \times 1$ vector.
+Stacking the $T$ observations for each $i$, we have
+\begin{align}
+\boldsymbol{y}_{i}=\boldsymbol{W}_{i}\boldsymbol{\theta}_{i}+ \alpha_{i}\boldsymbol{\iota}_{T}+ \boldsymbol{u}_{i}, \label{2}
+\end{align}
+where $\boldsymbol{y}_{i}=\left(y_{i,1},\ldots, y_{i,T} \right)^{'}$, $\boldsymbol{W}_{i}=\left(\boldsymbol{w}_{i,1},\ldots, \boldsymbol{w}_{i,T} \right)^{'}$, $\iota_{T}=\left(1,\ldots,1 \right)^{'}$ and $\boldsymbol{u}_{i}=\left(u_{i,1}, \ldots, u_{i,T} \right)^{'}$.
+
+Due to the incidental parameters problem arise, we use forward filter to the model by \citet{Moon:2000}, \citet{Hayakawa:2009} and \citet{Hayakawa:2019}.
+We define the $\left(T-1 \right) \times 1$ forward demeaning matrix as
+
+\begin{align}
+\boldsymbol{F}=diag(c_{1}, c_{2}, \ldots c_{T-1})
+\begin{bmatrix}
+1 & \frac{-1}{T-1} & \cdots & \cdots & \frac{-1}{T-1}\\
+\vdots & 1 & \frac{-1}{T-2} & \cdots & \frac{-1}{T-2}\\
+\vdots & \vdots & \vdots & \ddots & \vdots \\
+0 & 0 & 0 & \cdots & -1 
+\end{bmatrix},
+\end{align}    
+where $c_{t}=\sqrt{\left( T-t\right)\left( T-t+1\right) }$.
+Multiply $\boldsymbol{F}$ to model $(\ref{2})$, the model can expressed as  
+\begin{align}
+\tilde{\boldsymbol{y}}_{i}= \tilde{\boldsymbol{W}}_{i}\boldsymbol{\theta}+\tilde{\boldsymbol{u}}_{i},
+\end{align}
+where $\tilde{\boldsymbol{y}}_{i}=\boldsymbol{F}\boldsymbol{y}_{i}= \left(\tilde{\boldsymbol{y}}_{i,1}, \ldots, \tilde{\boldsymbol{y}}_{i,T-1} \right)^{'}$,  $\tilde{\boldsymbol{W}}_{i}=\boldsymbol{F}\boldsymbol{W}_{i}= \left(\tilde{\boldsymbol{w}}_{i,1}, \ldots, \tilde{\boldsymbol{w}}_{i,T-1} \right)^{'}$ and $\tilde{\boldsymbol{u}}_{i}=\boldsymbol{F}\boldsymbol{u}_{i}= \left(\tilde{\boldsymbol{u}}_{i,1}, \ldots, \tilde{\boldsymbol{u}}_{i,T-1} \right)^{'}$ with $\tilde{\boldsymbol{y}}_{i,t}=c_{t}\left[y_{i,t}-\left(y_{i,t+1}+\cdots+y_{i,T} \right)/\left(T-t \right) \right]$, for $t=1, \ldots, T-1.$
+
+\subsubsection{Trend model}
+Consider the dynamic heterogeneous panels data model with fixed effects and heterogeneous time trends:
+\begin{align}
+\begin{split}
+y_{i,t}&=\alpha_{i}+\eta_{i}t +\phi_{i} y_{i,t-1}+ \boldsymbol{x}^{'}_{i,t}\boldsymbol{\beta}_{i}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \\
+&= \boldsymbol{w}^{'}_{i,t}\boldsymbol{\theta}+ \alpha_{i}+\eta_{i}t+u_{i,t}, 
+\end{split}
+\end{align}
+where $\boldsymbol{x}_{i,t}$ and $\boldsymbol{\beta}_{i}$ are $k \times 1$ vectors and $\boldsymbol{w}_{i,t}=\left(\phi_{i}, \boldsymbol{\beta}^{'}_{i} \right)^{'}$ is a $\left(1+k\right) \times 1$ vector.
+Stacking the $T$ observations for each $i$, we have
+\begin{align}
+\boldsymbol{y}_{i}=\boldsymbol{W}_{i}\boldsymbol{\theta}_{i}+ \alpha_{i}\boldsymbol{\iota}_{T}+\eta_{i}\boldsymbol{\tau}_{T} + \boldsymbol{u}_{i}, \label{6}
+\end{align}
+where $\boldsymbol{\tau}_{T}=\left(1, 2, \ldots, T \right)^{'}$. Again, we define the forward demeaning matrix as
+
+\begin{align}
+\boldsymbol{F}^{\tau}=diag(c^{\tau}_{1}, c^{\tau}_{2}, \ldots c^{\tau}_{T-2})
+\begin{bmatrix}
+1 & \frac{2(-2(T-2))}{(T-1)(T-2)} & \frac{2(-2(T-2)+3)}{(T-1)(T-2)} & \cdots & \frac{2(-2(T-2)+3(T-2))}{(T-1)(T-2)} \\
+0 & 1 & \frac{2(-2(T-3))}{(T-2)(T-3)} & \cdots & \frac{2(-2(T-3)+3(T-3))}{(T-3)(T-4)} \\
+\vdots &\vdots & \vdots & \ddots  &\vdots \\
+0 & \cdots & \cdots & \cdots & \frac{2(-2+3)}{2 \cdot 1}
+\end{bmatrix}, \label {7}
+\end{align}   
+where $c^{\tau}_{t}=\sqrt((T-t)(T-t-1)/(T-t-1)(T-t+2)).$
+
+Multiply $\boldsymbol{F}$ to model $(\ref{6})$, the model can expressed as  
+\begin{align}
+\tilde{\boldsymbol{y}}^{\tau}_{i}= \tilde{\boldsymbol{W}}^{\tau}_{i}\boldsymbol{\theta}+\tilde{\boldsymbol{u}}^{\tau}_{i},
+\end{align}
+where $\tilde{\boldsymbol{y}}^{\tau}_{i}=\boldsymbol{F}^{\tau}\boldsymbol{y}_{i}= \left(\tilde{\boldsymbol{y}}^{\tau}_{i,1}, \ldots, \tilde{\boldsymbol{y}}^{\tau}_{i,T-2} \right)^{'}$,  $\tilde{\boldsymbol{W}}^{\tau}_{i}=\boldsymbol{F}^{\tau}\boldsymbol{W}_{i}$ and $\tilde{\boldsymbol{u}}^{\tau}_{i}=\boldsymbol{F}^{\tau}\boldsymbol{u}_{i}.$
+
+\begin{myAssu}
+$x_{i,t}$ and $u_{i,t}$ are independently distributed for all $t$ and $s$ .
+\end{myAssu}
+
+\subsection{IV estimator}
+We use current and lagged values of $\boldsymbol{x}_{i}$ as instruments, as
+\begin{align}
+\boldsymbol{Z}^{(j)}_{i}=\left( \boldsymbol{x}_{i,\cdot}, \boldsymbol{x}_{i,-1},\ldots, \boldsymbol{x}_{i,-j} \right)^{'},
+\end{align}
+where $\boldsymbol{Z}^{(j)}_{i}$ is $T \times  (j+1)k$ matrix with $j \geq 1$. \\
+
+Then, we can define IV estimator, $\boldsymbol{\theta}^{b}_{i}$, as
+\begin{align}
+\hat{\boldsymbol{\theta}}^{b}_{IV,i}= \left( \tilde{\boldsymbol{W}}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \tilde{\boldsymbol{W}}_{i} \right)^{-1} \tilde{\boldsymbol{W}}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \tilde{\boldsymbol{y}}_{i},
+\end{align}
+where $\boldsymbol{P}^{(j)}_{i}=\boldsymbol{Z}^{(j)}_{i} \left(\boldsymbol{Z}^{(j)'}_{i}\boldsymbol{Z}^{(j)}_{i} \right)^{-1}\boldsymbol{Z}^{(j)'}_{i}$ and $b=1$ corresponds to the fixed effects model while $b=2$ corresponds to the trend models.
+
+If we can observe long lagged length from data, we have many instruments that can be used.
+In empirical study, researchers do not use all past variables as instruments because there are trade off between efficiency and bias.
+But we have not clearly know that the effect of using long lagged length  IV estimator in heterogeneous dynamic panel data model. And how to select the instruments to balance the bias and efficiency.
+
+\citet{Kuersteiner:2010} provided model averaging two stage least squares estimator to balance the bias and efficiency.
+We try to follow this method to construct the optimal instruments.
+We define a weighting vector $\boldsymbol{W}=\left(w_{1}, \ldots, w_{j} \right)^{'}$.
+Then, we can weight $\boldsymbol{P}^{(j)}_{i}$ as
+\begin{align}
+\boldsymbol{P}\left(\boldsymbol{W} \right)= \sum^{J}_{j=1}w_{j} \boldsymbol{P}^{(j)}_{i},
+\end{align}
+where $J$ is maximum number of lagged variables that we can observed. 
+Our goal is choosing $\boldsymbol{W}$ to minimize the approximate mean square error.
+
+\subsection{Asymptotic property of LS estimator}
+
+Based on heterogenous dynamic panel data model $(\ref{1})$, we can obtain fixed effect estimator as
+\begin{align}
+\hat{\boldsymbol{\theta}}_{LS,i}=
+\begin{pmatrix}
+\hat{\phi}_{i} \\
+\hat{\beta}_{i}
+\end{pmatrix}=
+\begin{pmatrix}
+\frac{\sum^{T}_{t=1}\tilde{y}^{2}_{i,t-1}}{T} & \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{x}_{i,t}}{T} \\
+\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t-1}}{T} &  \frac{\sum^{T}_{t=1}\tilde{x}_{i,t}^{2}}{T}
+\end{pmatrix}^{-1}
+\begin{pmatrix}
+\frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{y}_{i,t}}{T} \\
+\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t}}{T}
+\end{pmatrix},
+\end{align}
+
+where $\tilde{y}_{i,t}=y_{i,t}-\bar{y}_{i}$, $\tilde{y}_{i,t-1}=y_{i,t-1}-\bar{y}_{i,-1}\iota_{T}$ and $\tilde{x}_{i,t}=x_{i,t}-\bar{x}_{i}$ with $\bar{y}_{i}=\frac{1}{T}\sum^{T}_{t=1}y_{i,t}$, $\bar{y}_{i,-1}=\frac{1}{T}\sum^{T}_{t=1}y_{i,t-1}$,  $\bar{x}_{i}=\frac{1}{T}\sum^{T}_{t=1}x_{i,t}$.
+Under equation $(\ref{1})$, we have
+\begin{align}
+\begin{pmatrix}
+\hat{\phi}_{i}-\phi_{i} \\
+\hat{\beta}_{i}-\beta_{i}
+\end{pmatrix}=
+\begin{pmatrix}
+\frac{\sum^{T}_{t=1}\tilde{y}^{2}_{i,t-1}}{T} & \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{x}_{i,t}}{T} \\
+\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t-1}}{T} &  \frac{\sum^{T}_{t=1}\tilde{x}_{i,t}^{2}}{T}
+\end{pmatrix}^{-1}
+\begin{pmatrix}
+\frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{u}_{i,t}}{T} \\
+\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{u}_{i,t}}{T}
+\end{pmatrix},
+\end{align}
+where $\tilde{u}_{i,t}$ is $u_{i,t}-\bar{u}_{i}$ with $\bar{u}_{i}=\frac{1}{T}\sum^{T}_{t=1}u_{i,t}.$
+
+Now, we can investigate asymptotic bias by taking the probability limit as
+\begin{align}
+A^{(1)}_{\phi i}=\plim_{T  \rightarrow \infty}\left( \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{u}_{i,t}}{T} \right). \label{11}
+\end{align}
+Then $A^{(1)}_{i}$ can be taken expectations as
+\begin{align}
+\begin{split}
+A^{(1)}_{\phi i}&=E\left(y_{i,t-1}-\bar{y}_{i,-1} \right) \left(u_{i,t}-\bar{u}_{i} \right) \\
+&= E\left( y_{i,t-1}u_{i,t}\right) - E\left( y_{i,t-1} \bar{u}_{i}  \right)-E\left(\bar{y}_{i,-1}   u_{i,t}\right)+E\left(\bar{y}_{i,-1}  \bar{u}_{i}\right),
+\end{split}
+\end{align}
+where $E\left( y_{i,t-1}u_{i,t}\right)=0$.
+
+And we assume $y_{i,t}$ has started from a long time period in the past, so we have
+\begin{align}
+y_{i,t}=\frac{\alpha_{i}}{\left(1-\phi_{i} \right)}+\sum^{\infty}_{s=0}\beta_{i}\phi^{s}_{i}x_{i,t -s}+\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s},
+\end{align}
+
+Then, we have
+\begin{align}
+\begin{split}
+A^{(1)}_{\phi i}&=-E\left( \left(\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right) \left(\frac{1}{T}\sum^{T}_{t=1}u_{i,t} \right)  \right)-E\left(\frac{u_{i,t}}{T}\sum^{T}_{t=1}\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right)+ \\
+&\left(\frac{1}{T}\sum^{T}_{t=1}\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right)\left( \frac{1}{T}\sum^{T}_{t=1}u_{i,t} \right). \label{12}
+\end{split}
+\end{align}
+ Hence, from above equation, we have
+ \begin{equation}
+\begin{split}
+A^{(1)}_{\phi i}=&-\dfrac{1}{T} E\left\{  \left( u_{i,t-1}+u_{i,t-2}\phi_{i}^{1}+u_{i,t-3}\phi_{i}^{2}+\ldots\right)\left(u_{i,1}+\ldots+u_{i,t-1}+u_{i,t}+\ldots+u_{i,T}\right) \right\} -\\
+ &\dfrac{1}{T} E \left\{  u_{i,t}\sum^{T}_{s=1}\left( u_{i,s-1}\phi_{i}^{0}+u_{i,s-2}\phi_{i}^{1}+\ldots+u_{i,s-t-1}\phi_{i}^{t}+\ldots+u_{i,s-T-1}\phi_{i}^{T}+\ldots \right)  \right\}  + \\
+ +& \dfrac{1}{T} E\{ \left( \sum^{T}_{s=1}u_{i,s-1}\phi_{i}^{0}+\sum^{T}_{s=1}u_{i,s-2}\phi_{i}^{1}+\ldots+\sum^{T}_{s=1}u_{i,s-t-1}\phi_{i}^{t}+\ldots
++\sum^{T}_{s=1}u_{is-T-1}\phi_{i}^{T}+\ldots \right)\\
+ &\left(\dfrac{1}{T}\sum^{T}_{s=1}u_{i,s}\right) \} \\
+ =&-\dfrac{\sigma_{u}^{2}}{T}\dfrac{(1-\phi_{i}^{t-1})}{1-\phi_{i}}-\dfrac{\sigma^{2}_{u}}{T}\dfrac{(1-\phi_{i}^{T-t})}{(1-\phi_{i})}+\dfrac{\sigma^{2}_{u}}{T} \left( \dfrac{1}{1-\phi_{i}}-\dfrac{1}{T}\dfrac{(1-\phi_{i}^{T})}{(1-\phi_{i})^{2}}\right) \\
+ =&-\dfrac{\sigma_{u}^{2}}{T(1-\phi_{i})}\left( 1-\phi_{i}^{t-1}-\phi_{i}^{T-t}+\dfrac{1}{T}\dfrac{(1-\phi_{i}^{T})}{(1-\phi_{i})}  \right).
+ \end{split}
+\end{equation}
+
+Therefore, we can see the bias of $\hat{\phi}_{i}$ is $O\left(T^{-1}\right)$.
+
+To be more compact ,we can rewrite the model as,
+\begin{align}
+\tilde{\boldsymbol{y}}_{i}=\tilde{\boldsymbol{W}}_{i}\boldsymbol{\theta}_{i}+\tilde{\boldsymbol{u}}_{i},
+\end{align}
+where $\tilde{\boldsymbol{y}}_{i}=\left(\tilde{\boldsymbol{y}}_{i,1},\ldots, \tilde{\boldsymbol{y}}_{i,T}  \right)^{'}$ is $T \times 1$ vector,  $\tilde{\boldsymbol{W}}_{i}=\left( \tilde{\boldsymbol{w}}_{i,1},\ldots, \tilde{\boldsymbol{w}}_{i,T} \right)^{'}$ is $T \times 2$ matrix and $\tilde{\boldsymbol{u}}_{i}=\left(\tilde{\boldsymbol{u}}_{i,1}, \ldots, \tilde{\boldsymbol{u}}_{i,T} \right)$ is $T \times 1$ vector with $\tilde{\boldsymbol{w}}_{i,t}=\left(y_{i,t-1}-\bar{y}_{i,-1}, x_{i,t}-\bar{x}_{i}  \right)^{'}$, for $t=1,\ldots, T$ and $i=1,\ldots, N.$
+
+Also, we define our interested parameter as
+\begin{align}
+\left(\phi_{i},\beta_{i}  \right)^{'}=\boldsymbol{\theta}_{i}=\boldsymbol{\theta}+\boldsymbol{\lambda}_{i},
+\end{align}
+where $\boldsymbol{\lambda}_{i}\overset{i.i.d.}{\sim} \left(\boldsymbol{0}, \boldsymbol{\Sigma}_{\lambda} \right).$
+The lest square estimator, $\hat{\boldsymbol{\theta}}_{LS,i}$, can be expressed as
+\begin{align}
+\hat{\boldsymbol{\theta}}_{LS,i}=\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{y}}_{i}}{T}. \label{13}
+\end{align}
+
+From above discussion and assumptions, we have following theorem \\
+\begin{myTheo}
+\begin{align}
+\sqrt{T}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}\right) \overset{d}{\to} N \left(\boldsymbol{0}, \boldsymbol{Q}_{i}^{-1}\boldsymbol{\Sigma}_{LS,i}\boldsymbol{Q}_{i}^{-1}  \right),
+\end{align}
+where $\boldsymbol{\Sigma}_{LS,i}=\plim_{T \to \infty} T^{-1}\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{u}}_{i} \tilde{\boldsymbol{u}}^{'}_{i}  \tilde{\boldsymbol{W}}_{i} $ and $\boldsymbol{Q}_{i}=\plim_{T \to \infty} T^{-1}\tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{W}}_{i}$
+\end{myTheo}
+
+\subsubsection{Mean group LS estimator }
+Now, we define the mean group estimator of $\boldsymbol{\theta}$:
+\begin{align}
+\hat{\boldsymbol{\theta}}_{LSMG}=\frac{1}{N}\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSi}.
+\end{align}
+And we can show that the asymptotic property of $\hat{\boldsymbol{\theta}}_{LSMG}$, as
+\begin{align}
+\begin{split}
+\hat{\boldsymbol{\theta}}_{LSMG}&=N^{-1}\sum^{N}_{i=1}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{y}}_{i}}{T} \\
+&=\bar{\boldsymbol{\theta}}+N^{-1}\sum^{N}_{i=1}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T},
+\end{split}
+\end{align}
+where $\bar{\boldsymbol{\theta}}=N^{-1}\sum^{N}_{i=1}\boldsymbol{\theta}_{i}.$
+For fixed $N$ and large $T$, we have
+\begin{align}
+\plim_{T \to \infty}\hat{\boldsymbol{\theta}}_{LSMG} =  \bar{\boldsymbol{\theta}}+ N^{-1}\sum^{N}_{i=1}\plim_{T \to \infty}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1}\plim_{T \to \infty}\left( \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T}\right)
+\end{align}
+ Then, from section $1.1$, we know that $\plim_{T \to \infty}\left( \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T}\right)=O_{p}(1)$. Thus,  we can obtain
+\begin{align}
+\plim_{T \to \infty}\hat{\boldsymbol{\theta}}_{LSMG} =  \bar{\boldsymbol{\theta}}.
+\end{align}
+When $N \to \infty$ and $T \to \infty$ and by the law of large numbers, we can see that
+\begin{align}
+\plim_{T \to \infty, N \to \infty}\hat{\boldsymbol{\theta}}_{LSMG}=\boldsymbol{\theta}.
+\end{align}
+
+And the variance estimator of $\hat{\boldsymbol{\theta}}_{LSMG}$ is given by
+\begin{align}
+\hat{\boldsymbol{\Sigma}}_{LS,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}.
+\end{align}
+
+We show that $\hat{\boldsymbol{\Sigma}}_{LS,\lambda}$ is consistent when $N \to \infty$ and $T \to \infty.$
+\begin{align}
+\begin{split}
+&\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}=\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right) \right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'}\\
+&+\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right) \left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'}\\
+&-\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right) \left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'} \\
+&-\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right) \left( \hat{\boldsymbol{\theta}}_{LSMG}- E\left(\hat{\boldsymbol{\theta}}_{LS, i}\right)\right)^{'}.
+\label{20}
+\end{split}
+\end{align}
+
+Taking expectation on equation $(\ref{20})$, we have
+\begin{align}
+\begin{split}
+&E\left( \sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'} \right)=
+ \sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)+
+\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG}+  \\
+&\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right) E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}-
+\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LS,i}+
+\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)\hat{\boldsymbol{\theta}}^{'}_{LS,i}-
+\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSMG}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}- \\
+&\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LSMG}+
+\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LS,i}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}-
+\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right) E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'} = \\
+&\sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)-N E \left(\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG} \right)+\sum^{N}_{i=1}E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right) E\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)^{'}
+\end{split}
+\end{align}
+and
+\begin{align}
+E \left(\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG} \right)=\frac{1}{N^{2}} \sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right).
+\end{align}
+
+And, we also have
+\begin{align}
+E \left(\hat{\boldsymbol{\theta}}_{LSMG}\hat{\boldsymbol{\theta}}^{'}_{LSMG} \right)=\frac{1}{N^{2}}\left( \sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)+ \sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right) \right).
+\end{align}
+Then,
+\begin{align}
+\begin{split}
+&E\left( \sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'} \right)= \\
+&\left(1-\frac{1}{N} \right)\sum^{N}_{i=1}Var\left(\hat{\boldsymbol{\theta}}_{LS,i}\right)+ \sum^{N}_{i=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right)- \frac{1}{N}\sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right).
+\label{24}
+\end{split}
+\end{align}
+From above equation $(\ref{24})$, we can observe the bias term as,
+\begin{align}
+\aleph=\sum^{N}_{i=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right)- \frac{1}{N}\sum^{N}_{i=1}\sum^{N}_{j=1}E \left(\hat{\boldsymbol{\theta}}_{LS,i}\hat{\boldsymbol{\theta}}^{'}_{LS,i} \right).
+\label{25}
+\end{align}
+
+ Taking expectation on equation $(26)$, we have
+\begin{align}
+E\left( \hat{\boldsymbol{\theta}}_{LS,i} \right)=\boldsymbol{\theta}+E \left(b_{i} \right),
+\end{align}
+From equation $(\ref{25})$, we know that
+ \begin{align}
+\aleph=\sum^{N}_{i=1}E \left(b_{i}\right) E\left(b^{'}_{i} \right)- \frac{1}{N}\sum^{N}_{i=1}\sum^{N}_{j=1}E \left(b_{i}\right) E\left(b^{'}_{j} \right).
+ \end{align}
+When $T \to \infty$, $\aleph=0$.
+Therefore, we have following theorem \\
+
+\begin{myTheo}
+When $(T,N) \overset{j}{\to} \infty$ such that $N/T \to c$ with $0<c< \infty$,
+\begin{enumerate}
+\item \begin{align}
+\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{LSMG}-\boldsymbol{\theta}  \right)\overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{LS,\lambda} \right).
+\end{align}
+\item \begin{align}
+\hat{\boldsymbol{\Sigma}}_{LS,\lambda} \overset{p}{\to}  \boldsymbol{\Sigma}_{LS,\lambda}
+\end{align}
+where
+\begin{align}
+ \hat{\boldsymbol{\Sigma}}_{LS,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}.
+\end{align}
+\end{enumerate}
+\end{myTheo}
+
+\subsection{Asymptotic property of IV estimator}
+We use current and lagged values of $\boldsymbol{x}_{i}$ as instruments, as
+\begin{align}
+\tilde{\boldsymbol{Z}}_{i,t}=\left( \tilde{\boldsymbol{x}}_{i}, \tilde{\boldsymbol{x}}_{i,-1} \right)^{'},
+\end{align}
+where $\tilde{\boldsymbol{Z}}_{i}$ is $T \times  2$ vector. \\
+
+\begin{myAssu}
+$\boldsymbol{A}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{A}}_{i,T}$ has full column rank, $\boldsymbol{B}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{B}}_{i,T}$ and $\boldsymbol{\Sigma}_{i}=\plim_{T \to \infty} T^{-1}\boldsymbol{Z}^{'}_{i}\boldsymbol{u}_{i} \boldsymbol{u}_{i}^{'}\boldsymbol{Z}$ has positive definite, uniformly, where $\tilde{\boldsymbol{A}}_{i,T}= \frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{W}}_{i}$ and $\tilde{\boldsymbol{B}}_{i,T}= \frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{Z}}_{i}$ \\
+\end{myAssu}
+
+Then, the IV estimator can be expressed as
+\begin{align}
+\boldsymbol{\hat{\theta}}_{IV,i}=\left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{g}}_{i,T},
+\end{align}
+where
+\begin{align}
+\tilde{\boldsymbol{g}}_{i,T}=\frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{y}}_{i},
+\end{align}
+ and $\tilde{\boldsymbol{W}}_{i}=\left( \tilde{w}^{'}_{i,1},\ldots, \tilde{w}^{'}_{i,T} \right)^{'}$ is $T \times 2$ matrix
+
+From above equation, we have
+\begin{align}
+\sqrt{T}\left(\boldsymbol{\hat{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)=\left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\left(T^{-1/2}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \right)
+\end{align}
+Then, the property of $T^{-1/2}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} $ is given by following proposition.\\
+\begin{myProp}
+Under above assumptions, as $\left(N, T \right)\overset{j}{\to} \infty$ such that $N/T \to c$ with $0 < c<\infty $, for each $i$, we have
+\begin{align}
+\begin{split}
+&N^{-1} \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}\overset{p}{\to} \boldsymbol{0},  \\
+&\,\,\,\,and\,\,\,\,\, \\
+&T^{-1/2}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{i} \right).
+\end{split}
+\end{align}
+\end{myProp}
+
+Thus, IV  estimator, $\boldsymbol{\theta}_{IV, i}$ is $\sqrt{T}$ consistent to $\boldsymbol{\theta}_{i}$ and this estimator does not have Nickell's bias. Then, we have following theorem\\
+$\mathbf{Theorem \,\,1}$ \\
+As $\left(N,T \right)\to \infty $ such that $N/T \to c$ with $0< c< \infty$. for each $i$,
+\begin{align}
+\sqrt{T}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right)\overset{d}{\to} N \left(\boldsymbol{0},\,\left(\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}\boldsymbol{A}_{i} \right)^{-1}\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}   \boldsymbol{\Sigma}_{i}\boldsymbol{B}_{i}^{-1} \boldsymbol{A}_{i}\left(\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}\boldsymbol{A}_{i} \right)\right).
+\end{align}
+
+\subsubsection{Mean group IV estimator }
+Now, we define the mean group estimator of $\boldsymbol{\theta}$:
+\begin{align}
+\hat{\boldsymbol{\theta}}_{IVMG}=\frac{1}{N}\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{IVi}.
+\end{align}
+And we can show that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG}$, as
+\begin{align}
+\hat{\boldsymbol{\theta}}_{IVMG}-\boldsymbol{\theta}=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}\right)=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}_{i}\right)+\frac{1}{N}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i},
+\end{align}
+where
+\begin{align}
+\begin{split}
+\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}_{i}\right)&=\frac{1}{N}\sum^{N}_{i=1} \left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)^{-1}\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\left(T^{-1}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \right) \\
+&= O_{p}\left(\delta^{-2}_{NT} \right),
+\end{split}
+\end{align}
+where $\delta_{NT}=\min \{\sqrt{N},\,\sqrt{T} \}$.
+We note that $\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}=O_{p}\left(N^{-1/2} \right)$, if $\delta_{NT}^{-(2+\varsigma)}\to 0$ for any $\varsigma >0$, we have
+\begin{align}
+\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{IVMG}-\boldsymbol{\theta}  \right)=\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}+o_{p} \left(1 \right).
+\end{align}
+
+And the variance estimator of $\hat{\boldsymbol{\theta}}_{IVMG}$ is given by
+\begin{align}
+\hat{\boldsymbol{\Sigma}}_{IV,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{IV,i}- \hat{\boldsymbol{\theta}}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}_{IV,i}- \hat{\boldsymbol{\theta}}_{IVMG}\right)^{'}.
+\label{44}
+\end{align}
+Follow \citet{Norkute:2019}, we can show that $\hat{\boldsymbol{\Sigma}}_{IV,\lambda}$ is consistent and it does not have small $T$ bias.
+Firstly, we decompose $(\ref{44})$ as
+\begin{align}
+\begin{split}
+&\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}_{IVMG}\right)^{'}= \\
+& \sum^{N}_{i=1} \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)^{'}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) -\\
+&N\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right). \label{45}
+\end{split}
+\end{align}
+Then we can show consistent of $\hat{\boldsymbol{\Sigma}}_{IV,\lambda}$ as
+\begin{align}
+\begin{split}
+&\hat{\boldsymbol{\Sigma}}_{IV,\lambda}-\boldsymbol{\Sigma}_{IV,\lambda}=
+ \frac{1}{N-1}\sum^{N}_{i=1}\left( \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}-\boldsymbol{\Sigma}_{IV,\lambda}\right) +\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)^{'} \\
+&+\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\frac{1}{N-1}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) -\\
+&\frac{N}{N-1}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right)  =o_{p}(1).
+\end{split}
+\end{align}
+
+Then, we can see that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG} $ as,
+\begin{align}
+\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{IVMG}-\boldsymbol{\theta}  \right)\overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{IV,\lambda} \right).
+\end{align}
+
+\section{Estimation method on dynamic heterogeneous panel data model with  multifactor error structure}
+For convenient, we assume the number of regressor is $1$ and we express the model as
+\begin{align}
+y_{i,t}=\phi_{i} y_{i,t-1}+ \sum^{k}_{\ell=1}\beta_{\ell i}x_{\ell i,t}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T, \, \ell=1,\ldots, k. \label{46}
+\end{align}
+Consider the model $(\ref{45})$, we drawn $x_{\ell i,t}$ as
+\begin{align}
+x_{\ell i,t}=\boldsymbol{\gamma}^{0'}_{xi}\boldsymbol{f}^{0}_{xt}+\varepsilon_{xi,t}
+\end{align}
+and the idiosyncratic errors of the process for $y_{i,t}$ as
+\begin{align}
+u_{i,t}=\boldsymbol{\gamma}^{0'}_{yi}\boldsymbol{f}^{0}_{yt}+\varepsilon_{yi,t},
+\end{align}
+where $\boldsymbol{\gamma}^{0}_{yi}$ and $\boldsymbol{\gamma}^{0}_{xi}$ are $m_{y}\times 1$ and $m_{x}\times 1$ true
+ factor loading respectively, $\boldsymbol{f}^{0}_{yt}$  and  $\boldsymbol{f}^{0}_{xt}$ are  $m_{y}\times 1$ and $m_{x}\times 1$ true vector of unobservable factors respectively.
+\subsection{Norkutes' (2019) IVMG estimator}
+ We asymptotically eliminate the common factor in $\boldsymbol{x}_{i}$ by projecting matrix, $\boldsymbol{M}_{F^{0}_{x}}$.
+ \begin{align}
+ \boldsymbol{M}_{F^{0}_{x}}=\boldsymbol{I}_{T}-\boldsymbol{F}^{0}_{x}\left(\boldsymbol{F}^{0'}_{x}\boldsymbol{F}^{0}_{x}  \right)^{-1}\boldsymbol{F}^{0'}_{x} ; \boldsymbol{M}_{F^{0}_{x,-1}}=\boldsymbol{I}_{T}-\boldsymbol{F}^{0}_{x,-1}\left(\boldsymbol{F}^{0'}_{x,-1}\boldsymbol{F}^{0}_{x,-1}  \right)^{-1}\boldsymbol{F}^{0'}_{x,-1}
+ \end{align}
+And using the defactored covariates as instruments, as
+\begin{align}
+\boldsymbol{Z}_{IVi}=\left(\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{x}_{i}, \boldsymbol{M}_{F^{0}_{x,-1}}\boldsymbol{X}_{i,-1}  \right)
+\end{align}
+
+The first step IV estimator can be expressed as
+\begin{align}
+\begin{split}
+\boldsymbol{\hat{\varphi}}_{IVi}&=\left(\left(\frac{\boldsymbol{Z}^{'}_{i}\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{W}_{i}}{T } \right)^{'} \left(\frac{\boldsymbol{Z}^{'}_{i}\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{Z}_{i}}{T}  \right)^{-1}  \left(\frac{\boldsymbol{Z}^{'}_{i}\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{W}_{i}}{T}  \right)\right)^{-1} \\
+&\left(\left( \frac{\boldsymbol{Z}^{'}_{i}\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{W}_{i}}{T}  \right)^{'} \left(\frac{\boldsymbol{Z}^{'}_{i}\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{Z}_{i}}{T}  \right)^{-1}  \left(\frac{\boldsymbol{Z}^{'}_{i}\boldsymbol{M}_{F^{0}_{X}}\boldsymbol{y}_{i}}{T}  \right)\right).
+\end{split}
+\end{align}
+
+\section{Monte Carlo simulation design}
+\subsection{dynamic heterogeneous panels data model without error factor structure}
+The data generating process:
+\begin{align}
+\begin{split}
+y_{i,t}&= \phi_{i} y_{i,t-1}+ \sum^{k}_{\ell=1}\beta_{\ell i}x_{\ell i,t}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=-49,\ldots,T\, , \\ \label{M1}
+x_{\ell i,t}&=\sum^{k}_{\ell=1}\phi_{\ell i}x_{\ell i,t-1}+v_{\ell i,t},
+\end{split}
+\end{align}
+where $u_{i,t}\overset{i.i.d.}{\sim} \mathcal{N}(0,\,1)\,,$ and $v_{\ell i,t}=\rho_{v, \ell}v_{\ell i,t-1}+\left( 1-\rho^{2}_{v, \ell} \right)^{\frac{1}{2}}\varpi_{\ell i,t}, \varpi_{\ell i,t} \overset{i.i.d.}{\sim} U(0.5, 1.5) \, ,\rho_{v, \ell}=0.5.$
+
+The slope coefficients are generated as
+\begin{align}
+\phi_{i}=\phi+\eta_{\phi i},\,\, \beta_{1,i}=\beta_{1}+\eta_{\beta_{1} i}\, and\, \beta_{2,i}=\beta_{2}+\eta_{\beta_{2}i}.
+\end{align}
+Here we consider $\phi \in \left\{0.5 \right\}$, $\beta_{1}=3$ and $\beta_{2}=1$. For the design of heterogenous slopes, $\eta_{\phi i} \overset{i.i.d.}{\sim} U\left( -c, c\right)$, and
+\begin{align}
+\eta_{\beta_{\ell}i}= \left(1-\rho^{2}_{\beta}  \right)^{1/2}\eta_{\phi i}.
+\end{align}
+Here, we set $c=0.2,\, \rho_{\beta}=0.4$ for $\ell=1,2.$
+
+\subsection{Dynamic heterogeneous panels data model with multi-factor error structure}
+This Monte Carlo simulation design same as \citet{Norkute:2019}.
+For convenience, we rewrite the data generating process as bellow
+\begin{align}
+y_{i,t}=\alpha_{i}+\phi_{i} y_{i,t-1}+ \sum^{k}_{\ell=1}\beta_{\ell i}x_{\ell i,t}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=-49,\ldots,T\, . \\ \label{M1}
+\end{align}
+We allow error factor structure in the model as
+\begin{align}
+u_{i,t}=    \sum^{m_{y}}_{s=1}\gamma^{0}_{si}f^{0}_{s,t} +\varepsilon_{i,t},
+\end{align}
+where
+\begin{align}
+f^{0}_{s,t}=\rho^{0}_{s,t} f^{0}_{s,t-1}+\left( 1-\rho^{2}_{fs} \right)^{1/2}\zeta_{s,t},
+\end{align}
+with $\zeta_{s,t} \overset{i.i.d.}{\sim} N(0,1)$ for $s=1,\ldots m_{y}$. We assume $k=2$ and $m_{y}=1+k=3$ and set $\rho^{0}_{s,t}=0.5$ for all $s$. The error term, $\varepsilon_{i,t}$, setting as
+\begin{align}
+\varepsilon_{i,t}=\varsigma_{\varepsilon}\sigma_{it}\left(\epsilon_{it}-1 \right)/\sqrt{2},
+\end{align}
+where $ \epsilon_{it}\overset{i.i.d.}{\sim} \chi^{2}_{1},\, \sigma^{2}_{it}=\eta_{i}\varphi_{t}, \,\eta_{i}\overset{i.i.d.}{\sim}\chi^{2}_{2}/2,$  and  $\varphi_{t}=t/T\, for \,\, t=0,\ldots, T.$ And we set
+\begin{align}
+\varsigma_{\varepsilon}=\frac{\pi_{\mu}}{1-\pi_{\mu}}m_{y}.
+\end{align}
+we set $\pi_{\mu} \in \left\{ 3/4\right\}.$
+
+The process of regressors is
+\begin{align}
+x_{\ell it}=\mu_{\ell i}++\sum^{k}_{\ell=1}\phi_{\ell i}x_{\ell i,t-1}+\sum^{m_{x}}_{s=1}\gamma^{0}_{\ell si}f^{0}_{s,t}+v_{\ell it}, \,\, for\,\,i=1,\ldots N;\,t=-49,\ldots,T\,; \, \ell=1,2.
+\end{align}
+We set number of factor, $m_{x}$, is $2$.
+Therefore, $\boldsymbol{f}^{0}_{y,t}=\left(f^{0}_{1t}, f^{0}_{2t},f^{0}_{3t}  \right)^{'}$ and $\boldsymbol{f}^{0}_{x,t}=\left(f^{0}_{1t}, f^{0}_{2t}  \right)^{'}.$
+We set
+\begin{align}
+v_{\ell i,t}=\rho_{v, \ell}v_{\ell i,t-1}+\left( 1-\rho^{2}_{v, \ell} \right)^{\frac{1}{2}}\varpi_{\ell i,t},  for \, \ell=1,2,
+\end{align}
+  where $\rho_{v, \ell}=0.5$ for all $\ell$.
+The individual effect is
+\begin{align}
+ \alpha^{\ast}_{i}\overset{i.i.d.}{\sim} N\left(0, (1-\rho_{i})^{2} \right), \,\, \mu^{\ast}_{\ell i}=\rho_{\mu,\ell}\alpha^{\ast}_{i}+\left( 1-\rho^{2}_{\mu,\ell} \right)^{1/2}\omega_{\ell i},
+\end{align}
+where $\omega \overset{i.i.d.}{\sim}N\left(0, (1-\rho_{i})^{2} \right)$ and $\rho_{\mu,\ell}=0.5$.
+
+Now, we define the factor loading in $u_{i,t}$ are generated as $\gamma^{0\ast}_{si}\overset{i.i.d.}{\sim}N\left(0, 1 \right)$, for $s=1,\ldots, m_{y}=3$, and the factor loading in $x_{1it}$ and $x_{2it}$ are drawn as
+\begin{align}
+\begin{split}
+\gamma^{0\ast}_{1si}&=\rho_{\gamma,1s} \gamma^{0\ast}_{3i}+\left(1-\rho^{2}_{\gamma,1s}  \right)^{1/2}\xi_{1si};\,\xi_{1si}\overset{i.i.d.}{\sim}N\left(0, 1 \right); \\
+\gamma^{0\ast}_{2si}&=\rho_{\gamma,2s} \gamma^{0\ast}_{si}+\left(1-\rho^{2}_{\gamma,2s}  \right)^{1/2}\xi_{2si};\,\xi_{2si}\overset{i.i.d.}{\sim}N\left(0, 1 \right);
+\end{split}
+\end{align}
+for $s=1,\ldots, m_{x}=2$. We set $\rho_{\gamma, 11}=\rho_{\gamma, 12} \in \left\{ 0.5 \right\}$ and $\rho_{\gamma, 21}=\rho_{\gamma, 22}=0.5.$
+The factor loading are generated as
+\begin{align}
+\boldsymbol{\Gamma}=\boldsymbol{\Gamma}^{0}+\boldsymbol{\Gamma}^{0\ast}_{i}
+\end{align}
+where
+\begin{align}
+\boldsymbol{\Gamma}^{0}_{i}=
+\begin{bmatrix}
+\gamma^{0}_{1i} & \gamma^{0}_{11i} & \gamma^{0}_{21i} \\
+\gamma^{0}_{2i} & \gamma^{0}_{12i} & \gamma^{0}_{22i} \\
+\gamma^{0}_{3i} &  0               &     0
+\end{bmatrix}
+\end{align}
+and
+\begin{align}
+\boldsymbol{\Gamma}^{0\ast}_{i}=
+\begin{bmatrix}
+\gamma^{0\ast}_{1i} & \gamma^{0\ast}_{11i} & \gamma^{0\ast}_{21i} \\
+\gamma^{0\ast}_{2i} & \gamma^{0\ast}_{12i} & \gamma^{0\ast}_{22i} \\
+\gamma^{0\ast}_{3i} &  0               &     0
+\end{bmatrix}.
+\end{align}
+We set
+\begin{align}
+\boldsymbol{\Gamma}^{0}=
+\begin{bmatrix}
+1/4 & 1/4 & -1 \\
+1/2 & -1  & 1/4 \\
+1/2 & 0   & 0
+\end{bmatrix} .
+\end{align}
+And
+\begin{align}
+\alpha_{i}=\alpha+ \alpha^{\ast}_{i}, \, \mu_{\ell i}= \mu_{\ell}+\mu^{\ast}_{\ell i},
+\end{align}
+where $\alpha=1/2$, $\mu_{1}=1$, $\mu_{2}=-1/2$.
+
+The slope coefficients are generated as
+\begin{align}
+\phi_{i}=\phi+\eta_{\phi i},\,\, \beta_{1,i}=\beta_{1}+\eta_{\beta_{1} i}\, and\, \beta_{2,i}=\beta_{2}+\eta_{\beta_{2}i}.
+\end{align}
+Here we consider $\phi \in \left\{0.5\right\}$, $\beta_{1}=3$ and $\beta_{2}=1$. For the design of heterogenous slopes, $\eta_{\phi i} \overset{i.i.d.}{\sim} U\left( -c, c\right)$, and
+\begin{align}
+\eta_{\beta_{\ell}i}=\left[(2c)^{2}/12 \right]\rho_{\beta}\xi_{\beta \ell i}+ \left(1-\rho^{2}_{\beta}  \right)^{1/2}\eta_{\phi i},
+\end{align}
+where
+\begin{align}
+\xi_{\beta \ell i}=\frac{\bar{v^{2}_{\ell i}}- \bar{v^{2}_{\ell}}}{\left[ N^{-1}\sum^{N}_{i=1} \left( \bar{v^{2}_{\ell i}}- \bar{v^{2}_{\ell }}\right)^{2} \right]^{1/2} },
+\end{align}
+with $\bar{v^{2}_{ell i}}=T^{-1}\sum^{T}_{t=1}v^{2}_{\ell i t}$, $\bar{v^{2}_{\ell}}=N^{-1} \sum^{N}_{i=1} \bar{v^{2}_{\ell i}}$, for $\ell=1,2.$
+Here, we set $c=0.2,\, \rho_{\beta}=0.4$ for $\ell=1,2.$ And
+\begin{align}
+\varsigma^{2}_{v}=\varsigma^{2}_{\varepsilon}\left[SNR-\frac{\rho^{2}_{v}}{1-\rho^{2}_{v}}   \right]\left(\frac{\beta^{2}_{1}+\beta^{2}_{2}}{1-\rho^{2}_{v}}  \right)^{-1},
+\end{align}
+
+where $SNR=4$. For the $(T,N)$, we consider $T \in \left\{25, 50, 100, 200  \right\}$ and  $N \in \left\{25, 50, 100, 200  \right\}.$
+
+\section{Monte Carlo simulation results}
+\subsection{Dynamic Heterogeneous Panels without multifactor error structure }
+We consider ARDL(1,0) model. \\
+$\phi \in \left\{0.5 \right\}.$ \\
+ $\beta_{1}=3.$ \\
+  $\beta_{2}=1.$ \\
+$u_{i,t}\overset{i.i.d.}{\sim} \mathcal{N}(0,\,1).$ \\
+$\varpi_{\ell i,t} \overset{i.i.d.}{\sim} U(0.5, 1.5).$ \\
+$\rho_{v, \ell}=0.5.$ \\
+  $c=0.2.$ \\
+  $ \rho_{\beta}=0.4.$ \\
+ $T \in \left\{25, 50, 100, 200  \right\}.$ \\
+ $N \in \left\{25, 50, 100, 200  \right\}.$ \\
+
+LSMG estimator is provided in sheet 1 of MC.xlsx file. \\
+IVMG estimator is provided in sheet 2 of MC.xlsx file. \\
+
+\subsection{Dynamic Heterogeneous Panels with multifactor error structure }
+We consider ARDL(1,0) model. \\
+$\phi \in \left\{0.5 \right\}.$ \\
+ $\beta_{1}=3.$ \\
+  $\beta_{2}=1.$ \\
+  $k=2.$ \\
+  $m_{y}=1+k=3.$\\
+  $m_{x}=k=2.$\\
+$\zeta_{s,t} \overset{i.i.d.}{\sim} N(0,1)$ \\
+$\pi_{\mu} \in \left\{ 3/4\right\}.$ \\
+$\rho^{0}_{s,t}=0.5.$ \\
+$\rho_{v, \ell}=0.5.$\\
+ $\rho_{\mu,\ell}=0.5.$ \\
+  $\gamma^{0\ast}_{si}\overset{i.i.d.}{\sim}N\left(0, 1 \right).$ \\
+ $\xi_{1si}\overset{i.i.d.}{\sim}N\left(0, 1 \right).$ \\
+$\xi_{2si}\overset{i.i.d.}{\sim}N\left(0, 1 \right).$ \\
+$\rho_{\gamma, 11}=\rho_{\gamma, 12} \in \left\{ 0.5 \right\}.$ \\
+$\rho_{\gamma, 21}=\rho_{\gamma, 22}=0.5.$ \\
+$
+\boldsymbol{\Gamma}^{0}=
+\begin{bmatrix}
+1/4 & 1/4 & -1 \\
+1/2 & -1  & 1/4 \\
+1/2 & 0   & 0
+\end{bmatrix} .
+$ \\
+$\alpha=1/2.$ \\
+ $\mu_{1}=1.$\\
+  $\mu_{2}=-1/2.$ \\
+$c=0.2.$ \\
+$\rho_{\beta}=0.4.$ \\
+$SNR=4.$ \\
+$T \in \left\{25, 50, 100, 200  \right\}.$ \\
+ $N \in \left\{25, 50, 100, 200  \right\}.$ \\
+
+IVMG estimator is provided in sheet 3 of MC.xlsx file. \\
+
+\section{Short summary}
+\subsection{Dynamic Heterogeneous Panels without multifactor error structure}
+1. The performance of IVMG estimator is better than LSMG estimator in bias and RMSE.
+
+\subsection{Dynamic Heterogeneous Panels with multifactor error structure}
+1. When $N$ and $T$ increase, the performance of IVMG estimator is good in bias and RMSE. \\
+Related literature to dynamic Heterogeneous Panels with multifactor error structure: \citet{Chudik:2015} and \citet{Norkute:2019}.\\
+Related literature to choosing number of instruments: \citet{Stephen:2001}, \citet{Swanson:2005}, \citet{Marine:2012}, \citet{Bai:2010} and \citet{Kang:2019}.
+
+\newpage
+
+\addcontentsline{toc}{section}{Reference}
+\renewcommand\refname{References}
+\bibliographystyle{chicago}
+\bibliography{1}
+
+\begin{appendices}
+\section{Some Notation}
+
+\section{Some More Notation}
+\end{appendices}
+
+=======
 \documentclass[12pt,a4paper,hyperref]{article}
@@
 
+>>>>>>> 0c15682029aba834c6aa5b77f1e7ce6d65bf5d86
 \end{document}  \href{*}{*}

### 2020-02-28 MC_code/MAIV_MG_lag5_test2.m
up

@@ -1,0 +1,613 @@
+rep = 500;  
+list_T = [ 25 50 100 200]; 
+list_N = [25 50 100 200];  
+list_phi= [0.2 0.5 0.9]; 
+b1=3;
+rho_b=0.4;
+rho_b1=0;
+tao=0.5;
+v_theta=-0.2;
+b=[b1];
+k=1;   % number of regressors
+j=5; % lag of regressor
+Dis_T=50;
+%%%%%%%%%%%%%%%%%%%%%%%%
+ini_bias_mean_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_bias_mean_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
+
+ini_std_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
+ini_std_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
+
+ini_rmse_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_rmse_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+
+ini_mae_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_mae_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+opt_bias_mean_phi_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+opt_bias_mean_beta1_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
+
[…]

### 2020-02-29 MC_code/MAIV_MG_lag5_test2.m
up

@@ -1,7 +1,8 @@
+tic
 rep = 500;  
-list_T = [ 25 50 100 200]; 
-list_N = [25 50 100 200];  
-list_phi= [0.2 0.5 0.9]; 
+list_T = [ 50 ]; 
+list_N = [50 ];  
+list_phi= [0.8]; 
 b1=3;
 rho_b=0.4;
 rho_b1=0;
@@ -24,7 +25,6 @@ ini_rmse_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
 ini_mae_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
 ini_mae_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
 
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@ -33,7 +33,6 @@ opt_bias_mean_beta1_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
 
 opt_std_phi_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
 opt_std_beta1_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-
 
 opt_rmse_phi_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
 opt_rmse_beta1_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
@@ -78,9 +77,6 @@ opt_mae_phi_5=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
 opt_mae_beta1_5=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-
-
-
[…]

### 2020-02-29 Draft_V6.tex
up

\documentclass[12pt,a4paper,hyperref]{article}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
	\definecolor{ultramarine}{rgb}{0.07, 0.04, 0.56}
\usepackage{amsmath, natbib, latexsym, array, amssymb,longtable,float, graphicx, appendix,lscape,diagbox,textcomp,placeins}
\usepackage[colorlinks,
            linkcolor=ultramarine,
            anchorcolor=green,
            citecolor=darkblue
            ]{hyperref}
\usepackage[flushleft]{threeparttable}
\usepackage[top=2.7cm, left=3cm, right=3cm, bottom=2.7cm]{geometry}
\usepackage{hyperref}
\newtheorem{myDef}{Definition}
\newtheorem{myTheo}{Theorem}
\newtheorem{myProp}{proposition}
\newtheorem{myRem}{Remark}
\newtheorem{myAssu}{Assumption}
\newtheorem{myCor}{Corollary}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

\urlstyle{same}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{pgfplotstable}
\sisetup{
  round-mode          = places, % Rounds numbers
  round-precision     = 2, % to 2 places
}

\newenvironment{sequation}{\begin{equation}\tiny}{\end{equation}}
\DeclareMathOperator*{\plim}{plim}
\renewcommand{\floatpagefraction}{0.60}
\renewcommand{\appendixpagename}{\Large Appendix}
\setcounter{secnumdepth}{3}
\begin{document}
\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here

\center % Center everything on the page

\HRule \\[0.4cm]
{ \huge \bfseries Dynamic Heterogeneous Panels with multi-factor error sructure}\\[0.4cm] % Title of your document
\HRule \\[1.5cm]

\vfill % Fill the rest of the page with whitespace

\end{titlepage}

\newpage
\tableofcontents
\newpage
\section{Introduction}
How many instrument variables should we use in estimation $?$ How to balance the trade-off between bias and efficiency $?$   
Is our model slope heterogeneity or slope homogeneous $?$ In practical, we often have these open questions and we need to give the reasonable explanation from theory or data.
Therefore, it might cost time to control all of these to get the reasonable explain in applied research. In this study, we would want to develop the statistical  methods to reduce the model uncertainty.
Our contribution in this study are reducing the uncertainty of number of instrument variables and reducing the model selection problems. Also, this method is useful to largest set of instrument variables in high dimensional.

\section{Model, asymptotic property of IV estimator}
\subsection{The models and Assumptions}
\subsubsection{Fixed effects model, b=1}
Consider the dynamic heterogeneous panels data model with fixed effects:
\begin{align}
\begin{split}
y^{b}_{i,t}&=\phi_{i} y^{b}_{i,t-1}+ \boldsymbol{x}^{'}_{i,t}\boldsymbol{\beta}_{i}+\alpha_{i}+u^{b}_{i,t}  \\
&= \boldsymbol{w}^{b'}_{i,t}\boldsymbol{\theta}_{i}+ \alpha_{i}+u^{b}_{i,t}, \,\,\,\, \,\, \,\, \,\,\,\, \,\,\,\, \,\,\,\, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \label{1}
\end{split}
\end{align}
where $\boldsymbol{x}_{i,t}$ and $\boldsymbol{\beta}_{i}$ are $k \times 1$ vectors, $\boldsymbol{\theta}_{i}=\left(\phi_{i}, \boldsymbol{\beta}^{'}_{i} \right)^{'}$ and $\boldsymbol{w}^{b}_{i,t}=\left(y^{b}_{i,t-1}, \boldsymbol{x}^{'}_{i,t} \right)^{'}$ are $\left(1+k\right) \times 1$ vectors, and $b=1$ corresponds to the fixed effects model.
Stacking the $T$ observations for each $i$, we have
\begin{align}
\boldsymbol{y}^{b}_{i}=\boldsymbol{W}^{b}_{i}\boldsymbol{\theta}_{i}+ \alpha_{i}\boldsymbol{\iota}_{T}+ \boldsymbol{u}^{b}_{i}, \label{2}
\end{align}
where $\boldsymbol{y}_{i}=\left(y_{i,1},\ldots, y_{i,T} \right)^{'}$ is a $T \times 1$ vector, $\boldsymbol{W}^{b}_{i}=\left(\boldsymbol{w}^{b}_{i,1},\ldots, \boldsymbol{w}^{b}_{i,T} \right)^{'}$ is a $T \times (1+k)$ matrix, $\iota_{T}=\left(1,\ldots,1 \right)^{'}$ and $\boldsymbol{u}^{b}_{i}=\left(u^{b}_{i,1}, \ldots, u^{b}_{i,T} \right)^{'}$ are $T \times 1$ vectors.

Due to the incidental parameters problem arise, we use forward filter to the model by \citet{Moon:2000}, \citet{Hayakawa:2009} and \citet{Hayakawa:2019}. We define the $\left(T-1 \right) \times T$ forward demeaning matrix as

\begin{align}
\boldsymbol{F}^{b}=diag(c^{b}_{1}, c^{b}_{2}, \ldots c^{b}_{T-1})
\begin{bmatrix}
1 & \frac{-1}{T-1} & \cdots & \cdots & \frac{-1}{T-1}\\
\vdots & 1 & \frac{-1}{T-2} & \cdots & \frac{-1}{T-2}\\
\vdots & \vdots & \vdots & \ddots & \vdots \\
0 & 0 & 0 & \cdots & -1
\end{bmatrix},
\end{align}
where $c^{b}_{t}=\sqrt{\left( T-t\right)\left( T-t+1\right) }$, and  $b=1$ corresponds to the forward demeaning matrix under the fixed effects model.
Premultiplying the model $(\ref{2})$ by $\boldsymbol{F}^{b}$, the model can be expressed as
\begin{align}
\tilde{\boldsymbol{y}}^{b}_{i}= \tilde{\boldsymbol{W}}^{b}_{i}\boldsymbol{\theta}_{i}+\tilde{\boldsymbol{u}}^{b}_{i}, \label{4}
\end{align}
where $b=1$, $\tilde{\boldsymbol{y}}^{b}_{i}=\boldsymbol{F}^{b}\boldsymbol{y}^{b}_{i}= \left(\tilde{\boldsymbol{y}}^{b}_{i,1}, \ldots, \tilde{\boldsymbol{y}}^{b}_{i,T-1} \right)^{'}$,  $\tilde{\boldsymbol{W}}^{b}_{i}=\boldsymbol{F}^{b}\boldsymbol{W}^{b}_{i}= \left(\tilde{\boldsymbol{w}}^{b}_{i,1}, \ldots, \tilde{\boldsymbol{w}}^{b}_{i,T-1} \right)^{'}$ and $\tilde{\boldsymbol{u}}^{b}_{i}=\boldsymbol{F}^{b}\boldsymbol{u}^{b}_{i}= \left(\tilde{\boldsymbol{u}}^{b}_{i,1}, \ldots, \tilde{\boldsymbol{u}}^{b}_{i,T-1} \right)^{'}$ with $\tilde{\boldsymbol{y}}^{b}_{i,t}=c^{b}_{t}\left[y_{i,t}-\left(y_{i,t+1}+\cdots+y_{i,T} \right)/\left(T-t \right) \right]$, for $t=1, \ldots, T-1.$

\subsubsection{Trend model, b=2}
Consider the dynamic heterogeneous panels data model with fixed effects and heterogeneous time trends:
\begin{align}
\begin{split}
y^{b}_{i,t}&= \phi_{i} y^{b}_{i,t-1}+ \boldsymbol{x}^{'}_{i,t}\boldsymbol{\beta}_{i}+\alpha_{i}+\eta_{i}t+u^{b}_{i,t} \\
&= \boldsymbol{w}^{b'}_{i,t}\boldsymbol{\theta}_{i}+ \alpha_{i}+\eta_{i}t+u^{b}_{i,t}, \,\,\,\, \,\, \,\, \,\,\,\, \,\,\,\, \,\,\,\, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, ,
\end{split}
\end{align}
where $\boldsymbol{x}_{i,t}$ and $\boldsymbol{\beta}_{i}$ are $k \times 1$ vectors,  $\boldsymbol{\theta}_{i}=\left(\phi_{i}, \boldsymbol{\beta}^{'}_{i} \right)^{'}$ and $\boldsymbol{w}^{b}_{i,t}=\left(y^{b}_{i,t-1}, \boldsymbol{x}^{'}_{i,t} \right)^{'}$ are $\left(1+k\right) \times 1$ vectors, and $b=2$ corresponds to the trend model.
Stacking the $T$ observations for each $i$, we have
\begin{align}
\boldsymbol{y}^{b}_{i}=\boldsymbol{W}^{b}_{i}\boldsymbol{\theta}_{i}+ \alpha_{i}\boldsymbol{\iota}_{T}+\eta_{i}\boldsymbol{\tau}_{T} + \boldsymbol{u}^{b}_{i}, \label{6}
\end{align}
where $\boldsymbol{\tau}_{T}=\left(1, 2, \ldots, T \right)^{'}$. Then, we define the forward demeaning matrix to the trend model as

\begin{align}
\boldsymbol{F}^{b}=diag(c^{b}_{1}, c^{\tau}_{2}, \ldots c^{b}_{T-2})
\begin{bmatrix}
1 & \frac{2(-2(T-2))}{(T-1)(T-2)} & \frac{2(-2(T-2)+3)}{(T-1)(T-2)} & \cdots & \frac{2(-2(T-2)+3(T-2))}{(T-1)(T-2)} \\
0 & 1 & \frac{2(-2(T-3))}{(T-2)(T-3)} & \cdots & \frac{2(-2(T-3)+3(T-3))}{(T-3)(T-4)} \\
\vdots &\vdots & \vdots & \ddots  &\vdots \\
0 & \cdots & \cdots & \cdots & \frac{2(-2+3)}{2 \cdot 1}
\end{bmatrix}, \label {7}
\end{align}
where $c^{b}_{t}=\left((T-t)(T-t-1)/(T-t-1)(T-t+2)\right)^{1/2}$, and $b=2$ corresponds to the forward demeaning matrix under the trend model.

Multiply $\boldsymbol{F}^{b}$ to model $(\ref{6})$, the model can expressed as
\begin{align}
\tilde{\boldsymbol{y}}^{b}_{i}= \tilde{\boldsymbol{W}}^{b}_{i}\boldsymbol{\theta}_{i}+\tilde{\boldsymbol{u}}^{b}_{i}, \label{8}
\end{align}
where $\tilde{\boldsymbol{y}}^{b}_{i}=\boldsymbol{F}^{b}\boldsymbol{y}^{b}_{i}= \left(\tilde{\boldsymbol{y}}^{b}_{i,1}, \ldots, \tilde{\boldsymbol{y}}^{b}_{i,T-2} \right)^{'}$,  $\tilde{\boldsymbol{W}}^{b}_{i}=\boldsymbol{F}^{b}\boldsymbol{W}^{b}_{i}$ and $\tilde{\boldsymbol{u}}^{b}_{i}=\boldsymbol{F}^{b}\boldsymbol{u}^{b}_{i},$ and $b=2$.

\begin{myAssu}
$\boldsymbol{x}_{i,t}$ and $u^{b}_{i,t}$ are independently distributed for all $t$, $i$ and $b$ .
\end{myAssu}

\begin{myAssu}
$\boldsymbol{\theta}_{i}=\boldsymbol{\theta}+\boldsymbol{\lambda}_{i}$, \,\,$\boldsymbol{\lambda}_{i} \overset{i.i.d.}{\sim}(\boldsymbol{0},\, \boldsymbol{\Sigma}_{\lambda})$, where $\boldsymbol{\Sigma}_{\lambda}$ is a fixed positive definite matrix.
\end{myAssu}

\subsection{IV estimation method and asymptotic property}
\citet{Norkute:2019} propose an IV estimator in dynamic heterogeneous panel data model.
They use current and lagged values of $\boldsymbol{X}_{i}$ as instruments, as
\begin{align}
\tilde{\boldsymbol{Z}}^{b}_{i}=\left(\boldsymbol{F}^{b} \boldsymbol{X}_{i}, \boldsymbol{F}^{b} \boldsymbol{X}_{i,-1} \right),
\end{align}
where $\tilde{\boldsymbol{Z}}^{b}_{i}$ is a $(T-1) \times  2k$ vector with $\boldsymbol{X}_{i}=\left(\boldsymbol{x}_{i,1}, \ldots, \boldsymbol{x}_{i,T}  \right)^{'}$ and $\boldsymbol{X}_{i,-1}=\left(\boldsymbol{x}_{i,0}, \ldots, \boldsymbol{x}_{i,T-1}  \right)^{'}$. \\

\begin{myAssu}
$\boldsymbol{A}^{b}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{A}}^{b}_{i,T}$ has full column rank, $\boldsymbol{B}^{b}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{B}}^{b}_{i,T}$ and $\boldsymbol{\Sigma}^{b}_{i}=\plim_{T \to \infty} T^{-1}\tilde{\boldsymbol{Z}}^{b'}_{i}\tilde{\boldsymbol{u}}^{b}_{i} \tilde{\boldsymbol{u}}_{i}^{b'}\tilde{\boldsymbol{Z}}^{b}_{i}$ has positive definite, uniformly, where $\tilde{\boldsymbol{A}}^{b}_{i,T}= \frac{1}{T}\tilde{\boldsymbol{Z}}^{b'}_{i}\tilde{\boldsymbol{W}}^{b}_{i}$ and $\tilde{\boldsymbol{B}}^{b}_{i,T}= \frac{1}{T}\tilde{\boldsymbol{Z}}^{b'}_{i}\tilde{\boldsymbol{Z}}^{b}_{i}$
with $b = 1$ corresponds to the fixed effects model while $b = 2$ corresponds to the trend models.
\end{myAssu}

Then, the IV estimator can be expressed as
\begin{align}
\boldsymbol{\hat{\theta}}^{b}_{i}=\left(\tilde{\boldsymbol{A}}_{i,T}^{b'}\tilde{\boldsymbol{B}}_{i,T}^{b -1}\tilde{\boldsymbol{A}}^{b}_{i,T} \right)^{-1}\tilde{\boldsymbol{A}}_{i,T}^{b'}\tilde{\boldsymbol{B}}_{i,T}^{b -1}\tilde{\boldsymbol{g}}^{b}_{i,T},
\end{align}
where
\begin{align}
\tilde{\boldsymbol{g}}^{b}_{i,T}=\frac{1}{T}\tilde{\boldsymbol{Z}}^{b'}_{i}\tilde{\boldsymbol{y}}^{b}_{i}.
\end{align}

From above equation, we have
\begin{align}
\boldsymbol{\hat{\theta}}^{b}_{i}=\boldsymbol{\theta}_{i}+\left(\tilde{\boldsymbol{A}}_{i,T}^{b'}\tilde{\boldsymbol{B}}_{i,T}^{b -1}\tilde{\boldsymbol{A}}^{b}_{i,T} \right)^{-1}\tilde{\boldsymbol{A}}_{i,T}^{b'}\tilde{\boldsymbol{B}}_{i,T}^{b -1}\left(T^{-1}  \tilde{\boldsymbol{Z}}^{b'}_{i}\tilde{\boldsymbol{u}}^{b}_{i} \right) \label{14}
\end{align}

From assumption, we know $\boldsymbol{x}_{i,t}$ is strictly exogenous regressors. Then, we know $ E\left(\boldsymbol{z}_{i,t} \boldsymbol{u}_{it}  \right)=0.$
Therefore, we can show that
\begin{align}
\boldsymbol{\hat{\theta}}^{b}_{i}\overset{p}{\to} \boldsymbol{\theta}_{i}.
\end{align}

From $(\ref{14})$, we know

\begin{align}
\sqrt{T}\left(\boldsymbol{\hat{\theta}}^{b}_{i}-\boldsymbol{\theta}_{i} \right)=\left(\tilde{\boldsymbol{A}}_{i,T}^{b'}\tilde{\boldsymbol{B}}_{i,T}^{b -1}\tilde{\boldsymbol{A}}^{b}_{i,T} \right)^{-1}\tilde{\boldsymbol{A}}_{i,T}^{b'}\tilde{\boldsymbol{B}}_{i,T}^{b -1}\left(T^{-1/2}  \tilde{\boldsymbol{Z}}^{b'}_{i}\tilde{\boldsymbol{u}}^{b}_{i} \right)
\end{align}
Then, the property of $T^{-1/2}  \tilde{\boldsymbol{Z}}^{b'}_{i}\tilde{\boldsymbol{u}}^{b}_{i} $ is given by following proposition.\\
\begin{myProp}
Under above assumptions, as $\left(N, T \right)\overset{j}{\to} \infty$ such that $N/T \to c$ with $0 < c<\infty $, for each $i$, we have
\begin{align}
T^{-1/2}  \tilde{\boldsymbol{Z}}^{b'}_{i}\tilde{\boldsymbol{u}}^{b}_{i} \overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}^{b}_{i} \right).
\end{align}
\end{myProp}

Thus, IV  estimator, $\hat{\boldsymbol{\theta}}^{b}_{ i}$ is $\sqrt{T}$ consistent to $\boldsymbol{\theta}_{i}$ and this estimator does not have Nickell's bias. Then, we have following theorem\\
$\mathbf{Theorem \,\,1}$ \\
As $\left(N,T \right)\overset{j}{\to} \infty $ such that $N/T \to c$ with $0< c< \infty$. for each $i$,
\begin{align}
\sqrt{T}\left(\hat{\boldsymbol{\theta}}^{b}_{i}-\boldsymbol{\theta}_{i}  \right)\overset{d}{\to} N \left(\boldsymbol{0},\,\left(\boldsymbol{A}_{i}^{b'}\tilde{\boldsymbol{B}}_{i}^{b -1}\boldsymbol{A}^{b}_{i} \right)^{-1}\boldsymbol{A}_{i}^{b'}\tilde{\boldsymbol{B}}_{i}^{b -1}   \boldsymbol{\Sigma}^{b}_{i}\tilde{\boldsymbol{B}}_{i}^{b -1} \boldsymbol{A}^{b}_{i}\left(\boldsymbol{A}_{i}^{b'}\tilde{\boldsymbol{B}}_{i}^{b -1}\boldsymbol{A}^{b}_{i} \right)\right).
\end{align}

\section{Construction optimal instruments}
How to select optimal instruments is important issue in empirical studies.
\citet{Stephen:2001}, \citet{Kuersteiner:2010}, \citet{Ryo:2011}, \citet{Kang:2019} and \citet{Seojeong:2019} propose different methods to construct optimal instruments.
Here, we try to apply model average approach by \citet{Kuersteiner:2010} in here.

If we can observed long past periods variables, we have many instruments. In this case we define our instruments, as
\begin{align}
\tilde{\boldsymbol{Z}}^{b(j)}_{i}=\left( \boldsymbol{F}^{b}\boldsymbol{X}_{i}, \boldsymbol{F}^{b} \boldsymbol{X}_{i,-1},\ldots, \boldsymbol{F}^{b} \boldsymbol{X}_{i,-j}  \right),
\end{align}
where $\tilde{\boldsymbol{Z}}^{b(j)}_{i}$ is $(T-1) \times  (j+1)k$ matrix with $1\leq j \leq J $ with $J$ is the maximum lags of variables that we can observe. \\

Then, we can define IV estimator, $\hat{\boldsymbol{\theta}}^{b}_{i}$, as
\begin{align}
\hat{\boldsymbol{\theta}}^{b}_{i}= \left( \tilde{\boldsymbol{W}}^{b'}_{i}\boldsymbol{P}^{b(j)}_{i} \tilde{\boldsymbol{W}}^{b}_{i} \right)^{-1} \tilde{\boldsymbol{W}}^{b'}_{i}\boldsymbol{P}^{b(j)}_{i} \tilde{\boldsymbol{y}}^{b}_{i},
\end{align}
where $\boldsymbol{P}^{b(j)}_{i}=\tilde{\boldsymbol{Z}}^{b(j)}_{i} \left(\tilde{\boldsymbol{Z}}^{b(j)'}_{i}\tilde{\boldsymbol{Z}}^{b(j)}_{i} \right)^{-1}\tilde{\boldsymbol{Z}}^{b(j)'}_{i}$.

If we can observe long lagged length from data, we can use more instruments.
In empirical study, researchers do not use all past variables as instruments because there are trade off between efficiency and bias.
But we have not clearly know that the effect of using long lagged length  IV estimator in heterogeneous dynamic panel data model. And how to select the instruments to balance the bias and efficiency.

\citet{Kuersteiner:2010} provided model averaging two stage least squares estimator to balance the bias and efficiency. We try to follow this method to construct the optimal instruments. We define a weighting vector
\begin{align}
\boldsymbol{\omega}^{(i)}=\left(\omega^{(i)}_{1}, \ldots,\omega^{(i)}_{J}  \right)^{'},
\end{align}
where $\boldsymbol{\omega}^{(i)}$ is a $J \times 1$ vector and $\sum^{J}_{j=1} \omega^{(i)}_{j}=1.$
Then, we can weight $\boldsymbol{P}^{(j)}_{i}$ as
\begin{align}
\boldsymbol{P}^{b}_{i}= \sum^{J}_{j=1} \omega^{(i)}_{j} \boldsymbol{P}^{b(j)}_{i},
\end{align}
where $J$ is maximum number of lagged variables that we can observed.
Our goal is to select $\boldsymbol{\omega}^{(i)}$ to minimize the approximate mean square error, $S^{b}_{\eta^{(i)}}\left(\boldsymbol{\omega^{(i)}} \right)$, where $\boldsymbol{\eta}^{(i)}$ is a $(1+k) \times 1$ fixed parameters vector.
 In beginning, we consider positive weights, such that $\omega^{(i)}_{j} \in [0,1].$ And we define $\boldsymbol{D}^{b}_{i}=\left( \tilde{\boldsymbol{w}}^{b}_{i,1},\ldots,  \tilde{\boldsymbol{w}}^{b}_{i,T-1} \right)^{'}$ is a $(T-1) \times (1+k)$ matrix. Let $\hat{\boldsymbol{H}}_{i}$ is some estimator of $\boldsymbol{H}_{i}=\frac{\boldsymbol{D}^{b'}_{i}\boldsymbol{D}^{b}_{i}}{T-1}$. Let $\hat{\boldsymbol{\theta}}^{b}_{i}$ is some preliminary estimator, and define the residuals $\hat{\tilde{\boldsymbol{u}}}^{b}_{i}=\tilde{\boldsymbol{y}}^{b}_{i}-\tilde{\boldsymbol{W}}^{b}_{i}\hat{\boldsymbol{\theta}}^{b}_{i}$ that does not depend on the weighting vector.  Let $(T-1) \times (1+k)$ matrix, $\tilde{\boldsymbol{V}}^{b}_{i}$, be some preliminary residual from first stage regression, and $\tilde{\boldsymbol{v}}^{b}_{\eta, i}=\tilde{\boldsymbol{V}}^{b}_{i} \hat{\boldsymbol{H}}_{i}^{-1}\boldsymbol{\eta}^{(i)}$.

 Define
 \begin{align}
 \hat{\sigma}^{b 2}_{u, i}=\frac{\hat{\tilde{\boldsymbol{u}}}^{b'}_{i} \hat{\tilde{\boldsymbol{u}}}^{b}_{i}}{T-1}, \,\, \hat{\sigma}^{b2}_{\eta, i}=\frac{\tilde{\boldsymbol{v}}^{b '}_{\eta, i} \tilde{\boldsymbol{v}}^{b}_{\eta, i}}{T-1}, \,\, \hat{\boldsymbol{\sigma}}^{b}_{\eta u, i}=\frac{\tilde{\boldsymbol{v}}^{b'}_{\eta, i} \hat{\tilde{\boldsymbol{u}}}^{b}_{i}}{T-1}.
 \end{align}
 Let $\hat{\boldsymbol{v}}^{(j)}_{\eta, i}=\left(\boldsymbol{P}_{i}^{(J)}- \boldsymbol{P}_{i}^{(j)}\right)\tilde{\boldsymbol{W}}^{b}_{i}  \hat{\boldsymbol{H}}^{-1}\boldsymbol{\eta}^{(i)}$ is a $(T-1) \times 1$ vector, and $\hat{\boldsymbol{U}}_{i}=\left(\hat{\boldsymbol{v}}^{(1)}_{\eta, i}, \ldots, \hat{\boldsymbol{v}}^{(J)}_{\eta, i} \right)^{'}\left(\hat{\boldsymbol{v}}^{(1)}_{\eta, i}, \ldots, \hat{\boldsymbol{v}}^{(J)}_{\eta, i} \right)$ is $J \times J$ matrix. Define $\boldsymbol{\Gamma}^{(i)}$ be the $J \times J$ matrix whose $(j^{'}, j)$ element is $min(j^{'}, j)$ and let $K=(1, \ldots, J)^{'}$. The criterion $\hat{S}^{b}_{\eta^{(i)}}\left(\boldsymbol{\omega^{(i)}} \right)$ is
 \begin{align}
 \hat{S}^{b}_{\eta^{(i)}}\left(\boldsymbol{\omega^{(i)}} \right)=\hat{\sigma}^{b 2}_{\eta u, i} \frac{(K^{'}\boldsymbol{\omega}^{(i)})^{2}}{T-1}+\hat{\sigma}^{b2}_{u,i}\frac{\boldsymbol{\omega}^{(i)'}\hat{\boldsymbol{U}}_{i}\boldsymbol{\omega}^{(i)}-\hat{\sigma}^{b 2}_{\eta, i}(J-2K^{'}\boldsymbol{\omega}^{(i)}+\boldsymbol{\omega}^{(i)'}\Gamma_{i} \boldsymbol{\omega}^{(i)})}{T-1}.
 \end{align}
 Then, we can find the optimal weight,$\boldsymbol{\omega}^{(i)\ast}$ ,by minimize $\hat{S}^{b}_{\eta^{(i)}}(\boldsymbol{\omega}^{(i)})$.

Therefore, we have mean average 2SLS estimator, $\hat{\boldsymbol{\theta}}^{b}_{i}$ ,as
\begin{align}
\hat{\boldsymbol{\theta}}^{\ast b}_{i}= \left( \tilde{\boldsymbol{W}}^{b'}_{i}\boldsymbol{P}^{b}_{i}\left(\boldsymbol{\omega^{(i)\ast}} \right)\tilde{\boldsymbol{W}}^{b}_{i} \right)^{-1} \tilde{\boldsymbol{W}}^{b'}_{i}\boldsymbol{P}^{b}_{i}\left(\boldsymbol{\omega^{(i)\ast}} \right) \tilde{\boldsymbol{y}}^{b}_{i}.
\end{align}
\citet{Xiaohong:2016} also provide an alternative weighting scheme based on weighting individual estimators. This method can be also applied in heterogeneous dynamic panel data model. Also this method could be seen as an alternative method for mean group estimator. It would be interested to compare the performance of these two weighting scheme.

\subsection{Mean group IV estimator }
Now, we define the mean group estimator of $\boldsymbol{\theta}$:
\begin{align}
\hat{\boldsymbol{\theta}}^{b}_{IVMG}=\frac{1}{N}\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}^{\ast b}_{i}.
\end{align}
From Assumption $(2)$, we can show that the asymptotic property of $\hat{\boldsymbol{\theta}}^{b}_{IVMG}$, as
\begin{align}
\hat{\boldsymbol{\theta}}^{\ast b}_{IVMG}-\boldsymbol{\theta}=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{\ast b}_{i}- \boldsymbol{\theta}\right)=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{\ast b}_{i}- \boldsymbol{\theta}_{i}\right)+\frac{1}{N}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i},
\end{align}
where the first of right hand side
\begin{align}
\begin{split}
\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{\ast b}_{i}- \boldsymbol{\theta}_{i}\right)&=\frac{1}{N}\sum^{N}_{i=1} \left(\tilde{\boldsymbol{A}}_{i,T}^{b'}\tilde{\boldsymbol{B}}_{i,T}^{b -1}\tilde{\boldsymbol{A}}^{b}_{i,T} \right)^{-1}\tilde{\boldsymbol{A}}_{i,T}^{b'}\tilde{\boldsymbol{B}}_{i,T}^{b -1}\left(T^{-1}  \tilde{\boldsymbol{Z}}^{b'}_{i}\tilde{\boldsymbol{u}}^{b}_{i} \right) \\
&= o_{p}\left(1 \right).
\end{split}
\end{align}
Then, we can see
\begin{align}
\sqrt{N}\left(\hat{\boldsymbol{\theta}}^{b}_{IVMG}-\boldsymbol{\theta}  \right)=\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}+o_{p} \left(1 \right).
\end{align}
As $N \to \infty$, we can see
\begin{align}
\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \overset{d}{\to}  N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{\lambda} \right).
\end{align}
Therefore, we know that $\hat{\boldsymbol{\theta}}^{b}_{IVMG}$ is $\sqrt{N}$ consistent.

And the variance estimator of $\hat{\boldsymbol{\theta}}_{IVMG}$ is given by
\begin{align}
\hat{\boldsymbol{\Sigma}}^{b}_{\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}^{\ast b}_{i}- \hat{\boldsymbol{\theta}}^{b}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}^{\ast b}_{i}- \hat{\boldsymbol{\theta}}^{b}_{IVMG}\right)^{'}. \label{44}
\end{align}
Follow \citet{Norkute:2019}, we can show that $\hat{\boldsymbol{\Sigma}}^{b}_{\lambda}$ is consistent and it does not have small $T$ bias.
Firstly, we decompose $(\ref{44})$ as
\begin{align}
\begin{split}
&\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}^{\ast b}_{i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}^{b}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}^{\ast b}_{i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}^{b}_{IVMG}\right)^{'}= \\
& \sum^{N}_{i=1} \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{\ast b}_{i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}^{\ast b}_{i}-\boldsymbol{\theta}_{i} \right)^{'}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{\ast b}_{i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}^{\ast b}_{i}-\boldsymbol{\theta}_{i}  \right) -\\
&N\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}^{b}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}^{b}_{IVMG} \right). \label{45}
\end{split}
\end{align}
Then we can show consistent of $\hat{\boldsymbol{\Sigma}}^{b}_{\lambda}$ as
\begin{align}
\begin{split}
&\hat{\boldsymbol{\Sigma}}^{b}_{\lambda}-\boldsymbol{\Sigma}^{b}_{\lambda}=
 \frac{1}{N-1}\sum^{N}_{i=1}\left( \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}-\boldsymbol{\Sigma}^{b}_{\lambda}\right) +\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{\ast b}_{i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}^{\ast b}_{i}-\boldsymbol{\theta}_{i} \right)^{'} \\
&+\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{\ast b}_{i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\frac{1}{N-1}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}^{\ast b}_{i}-\boldsymbol{\theta}_{i}  \right) -\\
&\frac{N}{N-1}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}^{b}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}^{b}_{IVMG} \right)  =o_{p}(1).
\end{split}
\end{align}

Then, we can see that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG} $ as,
\begin{align}
\begin{split}
\sqrt{N}\left(\hat{\boldsymbol{\theta}}^{b}_{IVMG}-\boldsymbol{\theta}  \right)&\overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}^{b}_{\lambda} \right); \\
 \hat{\boldsymbol{\Sigma}}^{b}_{\lambda} & \overset{p}{\to}   \boldsymbol{\Sigma}^{b}_{\lambda}.
\end{split}
\end{align}

\section{Dynamic heterogeneous panel data model with multifactor error structure}
Reconsider model $(\ref{1})$ here,
\begin{align}
\begin{split}
y^{b}_{i,t}&=\phi_{i} y^{b}_{i,t-1}+ \boldsymbol{x}^{'}_{i,t}\boldsymbol{\beta}_{i}+u^{b}_{i,t}  \\
&= \boldsymbol{w}^{b'}_{i,t}\boldsymbol{\theta}_{i}+u^{b}_{i,t}, \,\,\,\, \,\, \,\, \,\,\,\, \,\,\,\, \,\,\,\, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \label{m1}
\end{split}
\end{align}
with
\begin{align}
u^{b}_{i,t}=\boldsymbol{\gamma}^{'}_{y,i}\boldsymbol{f}_{y,t}+\varepsilon_{i,t}, 
\end{align}
where $\boldsymbol{\gamma}_{y,i}$ is a $m_{y} \times 1$ vector of unobservable factors and $\boldsymbol{f}_{y,t}$ is a $m_{x} \times 1$ vector of factor loading and $\varepsilon_{i,t}$ is an idiosyncratic error. 
Regressor $\boldsymbol{x}_{i,t}$ follow the process as 
\begin{align}
 \boldsymbol{x}_{i,t}=\boldsymbol{\Gamma}^{'}_{x,i}\boldsymbol{f}_{x,t}+ \boldsymbol{v}_{i,t}.
\end{align}
Again, we stack the $T$ observations for each $i$ as
\begin{align}
\boldsymbol{y}_{i}= \phi_{i} \boldsymbol{y}_{i}+\boldsymbol{W}_{i}\boldsymbol{\theta}_{i}+\boldsymbol{u}_{i}\,\,\,\, with\,\,\boldsymbol{u}_{i}=\boldsymbol{F}_{y}\boldsymbol{\gamma}_{y,i}+\boldsymbol{\varepsilon}_{i},
\end{align}
where $\boldsymbol{F}_{y}=\left( \boldsymbol{f}_{y,1}, \boldsymbol{f}_{y,2},\ldots,\boldsymbol{f}_{y,T}  \right)^{'}$ and $\boldsymbol{\varepsilon}_{i}=\left( \varepsilon_{i,1}, \varepsilon_{i,2},\ldots,\varepsilon_{i,T} \right)^{'}$. And the regressor $\boldsymbol{X}_{i}$ as
\begin{align}
\boldsymbol{X}_{i}=\boldsymbol{F}_{x}\boldsymbol{\Gamma}_{x,i}+\boldsymbol{V}_{i},
\end{align}
where $\boldsymbol{F}_{x}=\left( \boldsymbol{f}_{x,1}, \boldsymbol{f}_{x,1},\ldots,\boldsymbol{f}_{x,T} \right)^{'}$ and $\boldsymbol{V}_{i}=\left( \boldsymbol{v}_{i,1}, \boldsymbol{v}_{i,2},\ldots,\boldsymbol{v}_{i,T}.  \right)$
Follow \citet{bai:2003} and \citet{bai:2009}, we can use principal components approach to estimate $\boldsymbol{F}_{x}$ and $\boldsymbol{F}_{x,-1}$. Then, we can build the projection matrices as
\begin{align}
\boldsymbol{M}_{\hat{F}_{x}}=\boldsymbol{I}_{T}-\hat{\boldsymbol{F}}_{x}\left(\hat{\boldsymbol{F}}^{'}_{x} \hat{\boldsymbol{F}}_{x}   \right)^{-1}\hat{\boldsymbol{F}}^{'}_{x}; \,\, \boldsymbol{M}_{\hat{F}_{x,-1}}=\boldsymbol{I}_{T}-\hat{\boldsymbol{F}}_{x,-1}\left(\hat{\boldsymbol{F}}^{'}_{x,-1} \hat{\boldsymbol{F}}_{x,-1}   \right)^{-1}\hat{\boldsymbol{F}}^{'}_{x,-1}.
\end{align}
Then, we can project out factor structure in $\boldsymbol{X}_{i}$.  Premultiplying $\boldsymbol{X}_{i}$ by $\boldsymbol{M}_{\hat{F}_{x}}$, we have $\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{X}_{i}=\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{V}_{i}.$ And we assume $\boldsymbol{V}_{i}$ is independent of $\boldsymbol{\varepsilon}$, $\boldsymbol{F}_{x}$, $\boldsymbol{F}_{y}$ and $\boldsymbol{\gamma}_{y,i}$. Then, we can see that $E\left(\boldsymbol{X}^{'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{u}_{i} \right)=E\left(  \boldsymbol{V}_{i}^{'}\boldsymbol{M}_{F_{x}}\boldsymbol{u}_{i} \right).$
Therefore, using the similar approach in section $1$, we can collect the set of instrumental variables:
\begin{align}
\boldsymbol{Z}_{i}=\left( \boldsymbol{M}_{F_{x}}\boldsymbol{X}_{i}, \boldsymbol{M}_{F_{x,-1}}\boldsymbol{X}_{i,-1},\ldots  ,\boldsymbol{M}_{F_{x,-j}}\boldsymbol{X}_{i,-j}, \right)
\end{align}
Define $\boldsymbol{P}^{(j)}_{i}$ as
\begin{align}
\boldsymbol{P}^{(j)}_{i}=\boldsymbol{Z}^{(j)}_{i} \left(\boldsymbol{Z}^{(j)'}_{i}\boldsymbol{Z}^{(j)}_{i} \right)^{-1}\boldsymbol{Z}^{(j)'}_{i}
\end{align}
where $\boldsymbol{Z}^{(j)}_{i}$ is $T \times  (j+1)k$ matrix with $1\leq j \leq J$ with $J$ is the maximum lags of variables that we can observe.

Then, we can show 2SLS estimator of $\boldsymbol{\theta}_{i}$ :
\begin{align}
\hat{\boldsymbol{\theta}}_{i}= \left( \boldsymbol{W}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \boldsymbol{W}^{b}_{i} \right)^{-1} \boldsymbol{W}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \boldsymbol{y}_{i},
\end{align}

\subsection{Optimal number of instrument variables}
Again, to select the number of instrument variables, we can follow the approach by \citet{Kuersteiner:2010}

\citet{Kuersteiner:2010} provided model averaging two stage least squares estimator to balance the bias and efficiency. We try to follow this method to construct the optimal instruments. We define a weighting vector
\begin{align}
\boldsymbol{\omega}^{(i)}=\left(\omega^{(i)}_{1}, \ldots,\omega^{(i)}_{J}  \right)^{'},
\end{align}
where $\boldsymbol{\omega}^{(i)}$ is a $J \times 1$ vector and $\sum^{J}_{j=1} \omega^{(i)}_{j}=1.$
Then, we can weight $\boldsymbol{P}^{(j)}_{i}$ as
\begin{align}
\boldsymbol{P}_{i}= \sum^{J}_{j=1} \omega^{(i)}_{j} \boldsymbol{P}^{(j)}_{i},
\end{align}
where $J$ is maximum number of lagged variables that we can observed.
Our goal is to select $\boldsymbol{\omega}^{(i)}$ to minimize the approximate mean square error, $S_{\eta^{(i)}}\left(\boldsymbol{\omega^{(i)}} \right)$, where $\boldsymbol{\eta}^{(i)}$ is a $(1+k) \times 1$ fixed parameters vector.
 In beginning, we consider positive weights, such that $\omega^{(i)}_{j} \in [0,1].$ And we define $\boldsymbol{D}_{i}=\left( \tilde{\boldsymbol{w}}_{i,1},\ldots,  \tilde{\boldsymbol{w}}_{i,T-1} \right)^{'}$ is a $T \times (1+k)$ matrix. Let $\hat{\boldsymbol{H}}_{i}$ is some estimator of $\boldsymbol{H}_{i}=\frac{\boldsymbol{D}^{'}_{i}\boldsymbol{D}_{i}}{T}$. Let $\hat{\boldsymbol{\theta}}_{i}$ is some preliminary estimator, and define the residuals $\hat{\tilde{\boldsymbol{u}}}_{i}=\boldsymbol{y}_{i}-\boldsymbol{W}_{i}\hat{\boldsymbol{\theta}}_{i}$ that does not depend on the weighting vector.  Let $T \times (1+k)$ matrix, $\boldsymbol{V}_{i}$, be some preliminary residual from first stage regression, and $\boldsymbol{v}_{\eta, i}=\boldsymbol{V}_{i} \hat{\boldsymbol{H}}_{i}^{-1}\boldsymbol{\eta}^{(i)}$.

 Define
 \begin{align}
 \hat{\sigma}^{ 2}_{u, i}=\frac{\hat{\boldsymbol{u}}^{'}_{i} \hat{\boldsymbol{u}}_{i}}{T}, \,\, \hat{\sigma}^{2}_{\eta, i}=\frac{\boldsymbol{v}^{ '}_{\eta, i} \boldsymbol{v}_{\eta, i}}{T}, \,\, \hat{\boldsymbol{\sigma}}_{\eta u, i}=\frac{\boldsymbol{v}^{'}_{\eta, i} \hat{\boldsymbol{u}}_{i}}{T}.
 \end{align}
 Let $\hat{\boldsymbol{v}}^{(j)}_{\eta, i}=\left(\boldsymbol{P}_{i}^{(J)}- \boldsymbol{P}_{i}^{(j)}\right)\boldsymbol{W}_{i}  \hat{\boldsymbol{H}}^{-1}\boldsymbol{\eta}^{(i)}$ is a $(T) \times 1$ vector, and $\hat{\boldsymbol{U}}_{i}=\left(\hat{\boldsymbol{v}}^{(1)}_{\eta, i}, \ldots, \hat{\boldsymbol{v}}^{(J)}_{\eta, i} \right)^{'}\left(\hat{\boldsymbol{v}}^{(1)}_{\eta, i}, \ldots, \hat{\boldsymbol{v}}^{(J)}_{\eta, i} \right)$ is $J \times J$ matrix. Define $\boldsymbol{\Gamma}^{(i)}$ be the $J \times J$ matrix whose $(j^{'}, j)$ element is $min(j^{'}, j)$ and let $K=(1, \ldots, J)^{'}$. The criterion $\hat{S}_{\eta^{(i)}}\left(\boldsymbol{\omega^{(i)}} \right)$ is
 \begin{align}
 \hat{S}_{\eta^{(i)}}\left(\boldsymbol{\omega^{(i)}} \right)=\hat{\sigma}^{2}_{\eta u, i} \frac{(K^{'}\boldsymbol{\omega}^{(i)})^{2}}{T}+\hat{\sigma}^{2}_{u,i}\frac{\boldsymbol{\omega}^{(i)'}\hat{\boldsymbol{U}}_{i}\boldsymbol{\omega}^{(i)}-\hat{\sigma}^{ 2}_{\eta, i}(J-2K^{'}\boldsymbol{\omega}^{(i)}+\boldsymbol{\omega}^{(i)'}\Gamma_{i} \boldsymbol{\omega}^{(i)})}{T}.
 \end{align}
 Then, we can find the optimal weight,$\boldsymbol{\omega}^{(i)\ast}$ ,by minimize $\hat{S}_{\eta^{(i)}}(\boldsymbol{\omega}^{(i)})$.

Therefore, we have mean average 2SLS estimator, $\hat{\boldsymbol{\theta}}^{b}_{i}$ ,as
\begin{align}
\hat{\boldsymbol{\theta}}^{\ast b}_{i}= \left( \tilde{\boldsymbol{W}}^{b'}_{i}\boldsymbol{P}^{b}_{i}\left(\boldsymbol{\omega^{(i)\ast}} \right)\tilde{\boldsymbol{W}}^{b}_{i} \right)^{-1} \tilde{\boldsymbol{W}}^{b'}_{i}\boldsymbol{P}^{b}_{i}\left(\boldsymbol{\omega^{(i)\ast}} \right) \tilde{\boldsymbol{y}}^{b}_{i}.
\end{align}

\section{Monte Carlo simulation design}
It has been found that the IV estimator exhibit systematic bias in the model with heterogeneous slops by \citet{Norkute:2019}. And $IVMG^{c}$ is outperform $CCEMG$ in terms of bias, RMSE, size and power.
Therefore, we would like to see the behaviour of $IV^{a}, IV^{c}, IVMG^{a}, IVMG^{c}, IV^{opt},$ and $IVMG^{opt} $ estimators in this simple simulation, where $a$ corresponds to two instruments are used and $c$  corresponds to three instruments are used while $opt$ corresponds MA2SLS estimator.

\subsection{dynamic heterogeneous panels data model without multi-factor error structure}
The data generating process:
\begin{align}
\begin{split}
y_{i,t}&= \phi_{i} y_{i,t-1}+\beta_{1 i}x_{1 i,t}+\alpha_{i}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=-49-(J+1),\ldots,T\, , \\ \label{M1}
x_{1 i,t}&=\rho x_{1 i,t-1}+\tau_{\alpha} \alpha_{i} +v_{i,t},
\end{split}
\end{align}
where $u_{i,t}\overset{i.i.d.}{\sim} \mathcal{N}(0,\,1)\,,$ and $v_{ i,t}\overset{i.i.d.}{\sim} \mathcal{N}(0,\,1), \alpha_{i}\overset{i.i.d.}{\sim} \mathcal{N}(0,\,1) \, ,\rho \in \left\{0, 0.5  \right\}  \, \, ,\tau_{\alpha}=0.5, J=3,4,5,6.$

The slope coefficients are generated as
\begin{align}
\phi_{i}=\phi+\eta_{\phi i};\,\, \beta_{1,i}=\beta_{1}+\eta_{\beta_{1} i}.
\end{align}
Here we consider $\phi \in \left\{0.2, 0.5, 0.8 \right\}$, $\beta_{1}=3$. For the design of heterogenous slopes, $\eta_{\phi i} \overset{i.i.d.}{\sim} U\left( -c, c\right)$, and
\begin{align}
\eta_{\beta_{1} i}= \left(1-\rho^{2}_{\beta}  \right)^{1/2}\eta_{\phi i}.
\end{align}
Here, we set $c=0.2,\, \rho_{\beta}=0.4.$

 The first $50$ observations are discarded. For the $(T,N)$, we consider $T \in \left\{25, 50, 100, 200  \right\}$ and  $N \in \left\{25, 50, 100, 200  \right\}.$

\subsection{Dynamic heterogeneous panels data model with multi-factor error structure}
This Monte Carlo simulation design same as \citet{Norkute:2019}.
For convenience, we rewrite the data generating process as bellow
\begin{align}
y_{i,t}=\alpha_{i}+\phi_{i} y_{i,t-1}+ \sum^{k}_{\ell=1}\beta_{\ell i}x_{\ell i,t}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=-49,\ldots,T\, . \\ \label{M1}
\end{align}
We allow error factor structure in the model as
\begin{align}
u_{i,t}=    \sum^{m_{y}}_{s=1}\gamma^{0}_{si}f^{0}_{s,t} +\varepsilon_{i,t},
\end{align}
where
\begin{align}
f^{0}_{s,t}=\rho^{0}_{s,t} f^{0}_{s,t-1}+\left( 1-\rho^{2}_{fs} \right)^{1/2}\zeta_{s,t},
\end{align}
with $\zeta_{s,t} \overset{i.i.d.}{\sim} N(0,1)$ for $s=1,\ldots m_{y}$. We assume $k=2$ and $m_{y}=1+k=3$ and set $\rho^{0}_{s,t}=0.5$ for all $s$. The error term, $\varepsilon_{i,t}$, setting as
\begin{align}
\varepsilon_{i,t}=\varsigma_{\varepsilon}\sigma_{it}\left(\epsilon_{it}-1 \right)/\sqrt{2},
\end{align}
where $ \epsilon_{it}\overset{i.i.d.}{\sim} \chi^{2}_{1},\, \sigma^{2}_{it}=\eta_{i}\varphi_{t}, \,\eta_{i}\overset{i.i.d.}{\sim}\chi^{2}_{2}/2,$  and  $\varphi_{t}=t/T\, for \,\, t=0,\ldots, T.$ And we set
\begin{align}
\varsigma_{\varepsilon}=\frac{\pi_{\mu}}{1-\pi_{\mu}}m_{y}.
\end{align}
we set $\pi_{\mu} \in \left\{ 3/4\right\}.$

The process of regressors is
\begin{align}
x_{\ell it}=\mu_{\ell i}++\sum^{k}_{\ell=1}\phi_{\ell i}x_{\ell i,t-1}+\sum^{m_{x}}_{s=1}\gamma^{0}_{\ell si}f^{0}_{s,t}+v_{\ell it}, \,\, for\,\,i=1,\ldots N;\,t=-49,\ldots,T\,; \, \ell=1,2.
\end{align}
We set number of factor, $m_{x}$, is $2$. Therefore, $\boldsymbol{f}^{0}_{y,t}=\left(f^{0}_{1t}, f^{0}_{2t},f^{0}_{3t}  \right)^{'}$ and $\boldsymbol{f}^{0}_{x,t}=\left(f^{0}_{1t}, f^{0}_{2t}  \right)^{'}.$
We set
\begin{align}
v_{\ell i,t}=\rho_{v, \ell}v_{\ell i,t-1}+\left( 1-\rho^{2}_{v, \ell} \right)^{\frac{1}{2}}\varpi_{\ell i,t},  for \, \ell=1,2,
\end{align}
  where $\rho_{v, \ell}=0.5$ for all $\ell$.
The individual effect is
\begin{align}
 \alpha^{\ast}_{i}\overset{i.i.d.}{\sim} N\left(0, (1-\rho_{i})^{2} \right), \,\, \mu^{\ast}_{\ell i}=\rho_{\mu,\ell}\alpha^{\ast}_{i}+\left( 1-\rho^{2}_{\mu,\ell} \right)^{1/2}\omega_{\ell i},
\end{align}
where $\omega \overset{i.i.d.}{\sim}N\left(0, (1-\rho_{i})^{2} \right)$ and $\rho_{\mu,\ell}=0.5$.

Now, we define the factor loading in $u_{i,t}$ are generated as $\gamma^{0\ast}_{si}\overset{i.i.d.}{\sim}N\left(0, 1 \right)$, for $s=1,\ldots, m_{y}=3$, and the factor loading in $x_{1it}$ and $x_{2it}$ are drawn as
\begin{align}
\begin{split}
\gamma^{0\ast}_{1si}&=\rho_{\gamma,1s} \gamma^{0\ast}_{3i}+\left(1-\rho^{2}_{\gamma,1s}  \right)^{1/2}\xi_{1si};\,\xi_{1si}\overset{i.i.d.}{\sim}N\left(0, 1 \right); \\
\gamma^{0\ast}_{2si}&=\rho_{\gamma,2s} \gamma^{0\ast}_{si}+\left(1-\rho^{2}_{\gamma,2s}  \right)^{1/2}\xi_{2si};\,\xi_{2si}\overset{i.i.d.}{\sim}N\left(0, 1 \right);
\end{split}
\end{align}
for $s=1,\ldots, m_{x}=2$. We set $\rho_{\gamma, 11}=\rho_{\gamma, 12} \in \left\{ 0.5 \right\}$ and $\rho_{\gamma, 21}=\rho_{\gamma, 22}=0.5.$
The factor loading are generated as
\begin{align}
\boldsymbol{\Gamma}=\boldsymbol{\Gamma}^{0}+\boldsymbol{\Gamma}^{0\ast}_{i}
\end{align}
where
\begin{align}
\boldsymbol{\Gamma}^{0}_{i}=
\begin{bmatrix}
\gamma^{0}_{1i} & \gamma^{0}_{11i} & \gamma^{0}_{21i} \\
\gamma^{0}_{2i} & \gamma^{0}_{12i} & \gamma^{0}_{22i} \\
\gamma^{0}_{3i} &  0               &     0
\end{bmatrix}
\end{align}
and
\begin{align}
\boldsymbol{\Gamma}^{0\ast}_{i}=
\begin{bmatrix}
\gamma^{0\ast}_{1i} & \gamma^{0\ast}_{11i} & \gamma^{0\ast}_{21i} \\
\gamma^{0\ast}_{2i} & \gamma^{0\ast}_{12i} & \gamma^{0\ast}_{22i} \\
\gamma^{0\ast}_{3i} &  0               &     0
\end{bmatrix}.
\end{align}
We set
\begin{align}
\boldsymbol{\Gamma}^{0}=
\begin{bmatrix}
1/4 & 1/4 & -1 \\
1/2 & -1  & 1/4 \\
1/2 & 0   & 0
\end{bmatrix} .
\end{align}
And
\begin{align}
\alpha_{i}=\alpha+ \alpha^{\ast}_{i}, \, \mu_{\ell i}= \mu_{\ell}+\mu^{\ast}_{\ell i},
\end{align}
where $\alpha=1/2$, $\mu_{1}=1$, $\mu_{2}=-1/2$.

The slope coefficients are generated as
\begin{align}
\phi_{i}=\phi+\eta_{\phi i},\,\, \beta_{1,i}=\beta_{1}+\eta_{\beta_{1} i}\, and\, \beta_{2,i}=\beta_{2}+\eta_{\beta_{2}i}.
\end{align}
Here we consider $\phi \in \left\{0.5\right\}$, $\beta_{1}=3$ and $\beta_{2}=1$. For the design of heterogenous slopes, $\eta_{\phi i} \overset{i.i.d.}{\sim} U\left( -c, c\right)$, and
\begin{align}
\eta_{\beta_{\ell}i}=\left[(2c)^{2}/12 \right]\rho_{\beta}\xi_{\beta \ell i}+ \left(1-\rho^{2}_{\beta}  \right)^{1/2}\eta_{\phi i},
\end{align}
where
\begin{align}
\xi_{\beta \ell i}=\frac{\bar{v^{2}_{\ell i}}- \bar{v^{2}_{\ell}}}{\left[ N^{-1}\sum^{N}_{i=1} \left( \bar{v^{2}_{\ell i}}- \bar{v^{2}_{\ell }}\right)^{2} \right]^{1/2} },
\end{align}
with $\bar{v^{2}_{ell i}}=T^{-1}\sum^{T}_{t=1}v^{2}_{\ell i t}$, $\bar{v^{2}_{\ell}}=N^{-1} \sum^{N}_{i=1} \bar{v^{2}_{\ell i}}$, for $\ell=1,2.$
Here, we set $c=0.2,\, \rho_{\beta}=0.4$ for $\ell=1,2.$ And
\begin{align}
\varsigma^{2}_{v}=\varsigma^{2}_{\varepsilon}\left[SNR-\frac{\rho^{2}_{v}}{1-\rho^{2}_{v}}   \right]\left(\frac{\beta^{2}_{1}+\beta^{2}_{2}}{1-\rho^{2}_{v}}  \right)^{-1},
\end{align}

where $SNR=4$. For the $(T,N)$, we consider $T \in \left\{25, 50, 100, 200  \right\}$ and  $N \in \left\{25, 50, 100, 200  \right\}.$

\newpage
\appendix
\appendixpage
\section{Asymptotic property of LS estimator}

Based on heterogenous dynamic panel data model $(\ref{1})$, we can obtain fixed effect estimator as
\begin{align}
\hat{\boldsymbol{\theta}}_{LS,i}=
\begin{pmatrix}
\hat{\phi}_{i} \\
\hat{\beta}_{i}
\end{pmatrix}=
\begin{pmatrix}
\frac{\sum^{T}_{t=1}\tilde{y}^{2}_{i,t-1}}{T} & \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{x}_{i,t}}{T} \\
\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t-1}}{T} &  \frac{\sum^{T}_{t=1}\tilde{x}_{i,t}^{2}}{T}
\end{pmatrix}^{-1}
\begin{pmatrix}
\frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{y}_{i,t}}{T} \\
\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t}}{T}
\end{pmatrix},
\end{align}

where $\tilde{y}_{i,t}=y_{i,t}-\bar{y}_{i}$, $\tilde{y}_{i,t-1}=y_{i,t-1}-\bar{y}_{i,-1}\iota_{T}$ and $\tilde{x}_{i,t}=x_{i,t}-\bar{x}_{i}$ with $\bar{y}_{i}=\frac{1}{T}\sum^{T}_{t=1}y_{i,t}$, $\bar{y}_{i,-1}=\frac{1}{T}\sum^{T}_{t=1}y_{i,t-1}$,  $\bar{x}_{i}=\frac{1}{T}\sum^{T}_{t=1}x_{i,t}$.  Under equation $(\ref{1})$, we have
\begin{align}
\begin{pmatrix}
\hat{\phi}_{i}-\phi_{i} \\
\hat{\beta}_{i}-\beta_{i}
\end{pmatrix}=
\begin{pmatrix}
\frac{\sum^{T}_{t=1}\tilde{y}^{2}_{i,t-1}}{T} & \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{x}_{i,t}}{T} \\
\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{y}_{i,t-1}}{T} &  \frac{\sum^{T}_{t=1}\tilde{x}_{i,t}^{2}}{T}
\end{pmatrix}^{-1}
\begin{pmatrix}
\frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{u}_{i,t}}{T} \\
\frac{\sum^{T}_{t=1}\tilde{x}_{i,t}\tilde{u}_{i,t}}{T}
\end{pmatrix},
\end{align}
where $\tilde{u}_{i,t}$ is $u_{i,t}-\bar{u}_{i}$ with $\bar{u}_{i}=\frac{1}{T}\sum^{T}_{t=1}u_{i,t}.$

Now, we can investigate asymptotic bias by taking the probability limit as
\begin{align}
A^{(1)}_{\phi i}=\plim_{T  \rightarrow \infty}\left( \frac{\sum^{T}_{t=1}\tilde{y}_{i,t-1}\tilde{u}_{i,t}}{T} \right). \label{11}
\end{align}
Then $A^{(1)}_{i}$ can be taken expectations as
\begin{align}
\begin{split}
A^{(1)}_{\phi i}&=E\left(y_{i,t-1}-\bar{y}_{i,-1} \right) \left(u_{i,t}-\bar{u}_{i} \right) \\
&= E\left( y_{i,t-1}u_{i,t}\right) - E\left( y_{i,t-1} \bar{u}_{i}  \right)-E\left(\bar{y}_{i,-1}   u_{i,t}\right)+E\left(\bar{y}_{i,-1}  \bar{u}_{i}\right),
\end{split}
\end{align}
where $E\left( y_{i,t-1}u_{i,t}\right)=0$.

And we assume $y_{i,t}$ has started from a long time period in the past, so we have
\begin{align}
y_{i,t}=\frac{\alpha_{i}}{\left(1-\phi_{i} \right)}+\sum^{\infty}_{s=0}\beta_{i}\phi^{s}_{i}x_{i,t -s}+\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s},
\end{align}

Then, we have
\begin{align}
\begin{split}
A^{(1)}_{\phi i}&=-E\left( \left(\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right) \left(\frac{1}{T}\sum^{T}_{t=1}u_{i,t} \right)  \right)-E\left(\frac{u_{i,t}}{T}\sum^{T}_{t=1}\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right)+ \\
&\left(\frac{1}{T}\sum^{T}_{t=1}\sum^{\infty}_{s=0}\phi^{s}_{i}u_{i,t-s-1} \right)\left( \frac{1}{T}\sum^{T}_{t=1}u_{i,t} \right). \label{12}
\end{split}
\end{align}
 Hence, from above equation, we have
 \begin{equation}
\begin{split}
A^{(1)}_{\phi i}=&-\dfrac{1}{T} E\left\{  \left( u_{i,t-1}+u_{i,t-2}\phi_{i}^{1}+u_{i,t-3}\phi_{i}^{2}+\ldots\right)\left(u_{i,1}+\ldots+u_{i,t-1}+u_{i,t}+\ldots+u_{i,T}\right) \right\} -\\
 &\dfrac{1}{T} E \left\{  u_{i,t}\sum^{T}_{s=1}\left( u_{i,s-1}\phi_{i}^{0}+u_{i,s-2}\phi_{i}^{1}+\ldots+u_{i,s-t-1}\phi_{i}^{t}+\ldots+u_{i,s-T-1}\phi_{i}^{T}+\ldots \right)  \right\}  + \\
 +& \dfrac{1}{T} E\{ \left( \sum^{T}_{t=1}u_{i,t-1}\phi_{i}^{0}+\sum^{T}_{t=1}u_{i,t-2}\phi_{i}^{1}+\ldots+\sum^{T}_{t=1}u_{i,-1}\phi_{i}^{t}+\ldots
+\sum^{T}_{t=1}u_{it-T-1}\phi_{i}^{T}+\ldots \right)\\
 &\left(\dfrac{1}{T}\sum^{T}_{t=1}u_{i,t}\right) \} \\
 =&-\dfrac{\sigma_{u}^{2}}{T}\dfrac{(1-\phi_{i}^{t-1})}{1-\phi_{i}}-\dfrac{\sigma^{2}_{u}}{T}\dfrac{(1-\phi_{i}^{T-t})}{(1-\phi_{i})}+\dfrac{\sigma^{2}_{u}}{T} \left( \dfrac{1}{1-\phi_{i}}-\dfrac{1}{T}\dfrac{(1-\phi_{i}^{T})}{(1-\phi_{i})^{2}}\right) \\
 =&-\dfrac{\sigma_{u}^{2}}{T(1-\phi_{i})}\left( 1-\phi_{i}^{t-1}-\phi_{i}^{T-t}+\dfrac{1}{T}\dfrac{(1-\phi_{i}^{T})}{(1-\phi_{i})}  \right).
 \end{split}
\end{equation}

Therefore, we can see the bias of $\hat{\phi}_{i}$ is $O\left(T^{-1}\right)$.

To be more compact ,we can rewrite the model as,
\begin{align}
\tilde{\boldsymbol{y}}_{i}=\tilde{\boldsymbol{W}}_{i}\boldsymbol{\theta}_{i}+\tilde{\boldsymbol{u}}_{i},
\end{align}
where $\tilde{\boldsymbol{y}}_{i}=\left(\tilde{\boldsymbol{y}}_{i,1},\ldots, \tilde{\boldsymbol{y}}_{i,T}  \right)^{'}$ is $T \times 1$ vector,  $\tilde{\boldsymbol{W}}_{i}=\left( \tilde{\boldsymbol{w}}_{i,1},\ldots, \tilde{\boldsymbol{w}}_{i,T} \right)^{'}$ is $T \times 2$ matrix and $\tilde{\boldsymbol{u}}_{i}=\left(\tilde{\boldsymbol{u}}_{i,1}, \ldots, \tilde{\boldsymbol{u}}_{i,T} \right)$ is $T \times 1$ vector with $\tilde{\boldsymbol{w}}_{i,t}=\left(y_{i,t-1}-\bar{y}_{i,-1}, x_{i,t}-\bar{x}_{i}  \right)^{'}$, for $t=1,\ldots, T$ and $i=1,\ldots, N.$

Also, we define our interested parameter as
\begin{align}
\left(\phi_{i},\beta_{i}  \right)^{'}=\boldsymbol{\theta}_{i}=\boldsymbol{\theta}+\boldsymbol{\lambda}_{i},
\end{align}
where $\boldsymbol{\lambda}_{i}\overset{i.i.d.}{\sim} \left(\boldsymbol{0}, \boldsymbol{\Sigma}_{\lambda} \right).$
The lest square estimator, $\hat{\boldsymbol{\theta}}_{LS,i}$, can be expressed as
\begin{align}
\hat{\boldsymbol{\theta}}_{LS,i}=\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{y}}_{i}}{T}. \label{13}
\end{align}

From above discussion and assumptions, we have following theorem \\
\begin{myTheo}
\begin{align}
\sqrt{T}\left(\hat{\boldsymbol{\theta}}_{LS,i}-\boldsymbol{\theta}_{i}\right) \overset{d}{\to} N \left(\boldsymbol{0}, \boldsymbol{Q}_{i}^{-1}\boldsymbol{\Sigma}_{LS,i}\boldsymbol{Q}_{i}^{-1}  \right),
\end{align}
where $\boldsymbol{\Sigma}_{LS,i}=\plim_{T \to \infty} T^{-1}\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{u}}_{i} \tilde{\boldsymbol{u}}^{'}_{i}  \tilde{\boldsymbol{W}}_{i} $ and $\boldsymbol{Q}_{i}=\plim_{T \to \infty} T^{-1}\tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{W}}_{i}$
\end{myTheo}

\subsection{Asymptotic property of Mean group LS estimator }
Now, we define the mean group estimator of $\boldsymbol{\theta}$:
\begin{align}
\hat{\boldsymbol{\theta}}_{LSMG}=\frac{1}{N}\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{LSi}.
\end{align}
And we can show that the asymptotic property of $\hat{\boldsymbol{\theta}}_{LSMG}$, as
\begin{align}
\begin{split}
\hat{\boldsymbol{\theta}}_{LSMG}&=N^{-1}\sum^{N}_{i=1}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{y}}_{i}}{T} \\
&=\bar{\boldsymbol{\theta}}+N^{-1}\sum^{N}_{i=1}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1} \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T},
\end{split}
\end{align}
where $\bar{\boldsymbol{\theta}}=N^{-1}\sum^{N}_{i=1}\boldsymbol{\theta}_{i}.$
For fixed $N$ and large $T$, we have
\begin{align}
\plim_{T \to \infty}\hat{\boldsymbol{\theta}}_{LSMG} =  \bar{\boldsymbol{\theta}}+ N^{-1}\sum^{N}_{i=1}\plim_{T \to \infty}\left(\frac{\tilde{\boldsymbol{W}}^{'}_{i} \tilde{\boldsymbol{W}}_{i}}{T}  \right)^{-1}\plim_{T \to \infty}\left( \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T}\right)
\end{align}
 Then, from section $1.1$, we know that $\plim_{T \to \infty}\left( \frac{ \tilde{\boldsymbol{W}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}}{T}\right)=O_{p}(1)$. Thus,  we can obtain
\begin{align}
\plim_{T \to \infty}\hat{\boldsymbol{\theta}}_{LSMG} =  \bar{\boldsymbol{\theta}}.
\end{align}
When $N \to \infty$ and $T \to \infty$ and by the law of large numbers, we can see that
\begin{align}
\plim_{T \to \infty, N \to \infty}\hat{\boldsymbol{\theta}}_{LSMG}=\boldsymbol{\theta}.
\end{align}

And the variance estimator of $\hat{\boldsymbol{\theta}}_{LSMG}$ is given by
\begin{align}
\hat{\boldsymbol{\Sigma}}_{LS,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \hat{\boldsymbol{\theta}}_{LSMG}\right)^{'}. \label{V1}
\end{align}

Firstly, we decompose $(\ref{V1})$ as
\begin{align}
\begin{split}
&\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{LS,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}_{LSMG}\right)\left( \hat{\boldsymbol{\theta}}_{LS,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}_{lSMG}\right)^{'}= \\
& \sum^{N}_{i=1} \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{LS,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}_{LS,i}-\boldsymbol{\theta}_{i} \right)^{'}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{LS,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}_{LS,i}-\boldsymbol{\theta}_{i}  \right) -\\
&N\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{LSMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{LSMG} \right). \label{V2}
\end{split}
\end{align}
Then we can show consistent of $\hat{\boldsymbol{\Sigma}}_{LS,\lambda}$ as
\begin{align}
\begin{split}
&\hat{\boldsymbol{\Sigma}}_{LS,\lambda}-\boldsymbol{\Sigma}_{LS,\lambda}=
 \frac{1}{N-1}\sum^{N}_{i=1}\left( \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}-\boldsymbol{\Sigma}_{LS,\lambda}\right) +\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{LS,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}_{LS,i}-\boldsymbol{\theta}_{i} \right)^{'} \\
&+\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{LS,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\frac{1}{N-1}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}_{LS,i}-\boldsymbol{\theta}_{i}  \right) -\\
&\frac{N}{N-1}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{LSMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{LSMG} \right)  =o_{p}(1).
\end{split}
\end{align}

Then, we can see that the asymptotic property of $\hat{\boldsymbol{\theta}}_{LSMG} $ as,
\begin{align}
\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{LSMG}-\boldsymbol{\theta}  \right)\overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{LS,\lambda} \right).
\end{align}

\section{Asymptotic property of IV estimator}

From the section $1$, we know the IV estimator is
\begin{align}
\begin{split}
\boldsymbol{\hat{\theta}}^{b}_{i}=\left(\tilde{\boldsymbol{A}}_{i,T}^{b'}\tilde{\boldsymbol{B}}_{i,T}^{b -1}\tilde{\boldsymbol{A}}^{b}_{i,T} \right)^{-1}\tilde{\boldsymbol{A}}_{i,T}^{b'}\tilde{\boldsymbol{B}}_{i,T}^{b -1}\tilde{\boldsymbol{g}}^{b}_{i,T}, \\
\boldsymbol{\hat{\theta}}^{b}_{i}=\boldsymbol{\theta}^{b}_{i}+\left(\tilde{\boldsymbol{A}}_{i,T}^{b'}\tilde{\boldsymbol{B}}_{i,T}^{b -1}\tilde{\boldsymbol{A}}^{b}_{i,T} \right)^{-1}\tilde{\boldsymbol{A}}_{i,T}^{b'}\tilde{\boldsymbol{B}}_{i,T}^{b -1}\left(T^{-1/2}  \tilde{\boldsymbol{Z}}^{b'}_{i}\tilde{\boldsymbol{u}}^{b}_{i} \right)
\end{split}
\end{align}

From assumption, we know $\boldsymbol{x}_{i,t}$ is strictly exogenous regressors. Then, we know $ E\left(\boldsymbol{z}_{i,t} \boldsymbol{u}_{it}  \right)=0.$
Therefore, we can show that
\begin{align}
\boldsymbol{\hat{\theta}}^{b}_{i}\overset{p}{\to} \boldsymbol{\theta}^{b}_{i}.
\end{align}

\addcontentsline{toc}{section}{Reference}
\renewcommand\refname{References}
\bibliographystyle{chicago}
\bibliography{1}

\end{document}  \href{*}{*}

### 2020-03-02 MC_code/opt_IV_factor.m
up

@@ -1,0 +1,727 @@
+tic
+rep = 500;  
+list_T = [ 25 50 100 ]; 
+list_N = [25 50 100];  
+list_phi= [0.5 0.8]; 
+b1=3;
+b2=1;
+b=[b1,b2];
+rho=[0];
+pi_u=0.75;
+SNR=4;
+Mu1=1;
+Mu2=-0.5;
+A=0.5;
+rho_gamma_1s=0.5;
+k=2;   % number of regressors
+m_x=2; % number of factors of regressor
+my=1;
+m_y=m_x+my; % number of factors of y
+xi_es=sqrt((pi_u/(1-pi_u))*m_y);
+
+rho_mu=0.5;
+rho_v=0.5;
+rho_b=0.4;
+xi_ev=xi_es^(2)*(SNR-(rho_v^(2)/(1-rho_v^(2))))*((b1^(2)+b2^(2))/(1-rho_v^(2)))^(-1);
+
+
+
+j=5; % lag of regressor
+Dis_T=50;
+%%%%%%%%%%%%%%%%%%%%%%%%
+ini_bias_mean_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_bias_mean_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
+
+ini_std_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
+ini_std_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
+
+ini_rmse_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_rmse_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+
+ini_mae_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_mae_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
[…]

### 2020-03-03 MC_code/MAIV_MG_lag5_test2.m
up

@@ -1,8 +1,8 @@
 tic
 rep = 500;  
-list_T = [ 50 ]; 
-list_N = [50 ];  
-list_phi= [0.8]; 
+list_T = [ 25 ]; 
+list_N = [25];  
+list_phi= [0.5]; 
 b1=3;
 rho_b=0.4;
 rho_b1=0;
@@ -213,7 +213,7 @@ Z_it_M(:,:,6)=(F*x_NT1_5')';  % N by T1     ; lag 4
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 D=zeros(T1,1+k,N);    
-Z_1=zeros(T1,2*k,N);   % lag 1
+Z_1=zeros(T1,1+k,N);   % lag 1
 Z_2=zeros(T1,1*k,N);  % lag 2
 Z_3=zeros(T1,1*k,N);  % lag 3
 Z_4=zeros(T1,1*k,N);  % lag 4
@@ -261,7 +261,7 @@ end
 
 H=zeros(1+k,1+k,N);
 for hi=1:N
-H(:,:,hi)= Z_1(:,:,hi)'* Z_1(:,:,hi); % 1+k by 1+k
+H(:,:,hi)= Z_1(:,:,hi)'* Z_1(:,:,hi)/T1; % 1+k by 1+k
 end 
 
 ini_theta_IV_1=zeros(1+k,N); 
@@ -277,7 +277,7 @@ end
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 V_2=zeros(T1,1+k,N);
 for V_i_2=1:N
-   V_2(:,:,V_i_2)= D(:,:,V_i_2)- Z_2(:,:,V_i_2)*pinv(Z_2(:,:,V_i_2)'*Z_2(:,:,V_i_2))*Z_2(:,:,V_i_2)'*D(:,:,V_i_2);  %T1 by 1+k ; first stage residual
[…]

### 2020-03-03 MC_code/opt_IV_factor.m

@@ -1,18 +1,18 @@
 tic
 rep = 500;  
-list_T = [ 25 50 100 ]; 
-list_N = [25 50 100];  
-list_phi= [0.5 0.8]; 
+list_T = [ 25 ]; 
+list_N = [25 ];  
+list_phi= [0.8]; 
 b1=3;
 b2=1;
-b=[b1,b2];
-rho=[0];
-pi_u=0.75;
+b=[b1,b2]; % 1 by k 
+rho=0; % lag of x ARDL(0,1) 
+pi_u=0.25; % 0.25 or 0.75
 SNR=4;
 Mu1=1;
 Mu2=-0.5;
 A=0.5;
-rho_gamma_1s=0.5;
+rho_gamma_1s=0; %  0 independent factor loading; 0.5 correlated loading
 k=2;   % number of regressors
 m_x=2; % number of factors of regressor
 my=1;
@@ -140,21 +140,22 @@ x=zeros(k,N,TT);
 eta_rho_i=-0.25+(0.5)*rand([1,N]); % 1 by N heterogeneous_y
 eta_rho_bi=-sqrt(3)+2*sqrt(3)*rand([1,N]);
 phi_i= phi+  eta_rho_i;
+sig_bar_w=0.5+rand;
 v_x=zeros(k,N,TT);
 v_x(:,:,1)=zeros(k,N,1);  
 for ttt=2:TT
     for iiii=1:N
-v_x(:,iiii,ttt)=0.5*v_x(:,iiii,ttt-1)+sqrt((1-0.5^(2)))*normrnd(0,xi_ev,[k,1]); % k by N by TT
+v_x(:,iiii,ttt)=0.5*v_x(:,iiii,ttt-1)+sqrt((1-0.5^(2)))*normrnd(0,sqrt(xi_ev*sig_bar_w),[k,1]); % k by N by TT
     end 
 end
 bar_v_i=zeros(k,N);
 for tttt=1:TT
-bar_v_i=bar_v_i+v_x(:,:,tttt);
+bar_v_i=bar_v_i+(v_x(:,:,tttt).^2);
 end
-bar_v_i=bar_v_i*(TT)^(-1); % k by N
[…]

### 2020-03-03 MC_code/opt_IV_factor.m
up

@@ -7,7 +7,7 @@ b1=3;
 b2=1;
 b=[b1,b2]; % 1 by k 
 rho=0; % lag of x ARDL(0,1) 
-pi_u=0.25; % 0.25 or 0.75
+pi_u=0.75; % 0.25 or 0.75
 SNR=4;
 Mu1=1;
 Mu2=-0.5;
@@ -593,7 +593,7 @@ end
 
 opt_theta_IV_i_5=zeros(1+k,N);
 for ome__5=1:N
-opt_theta_IV_i_5(:,ome__5)= pinv(D(:,:,ome__5)'*MF_x1*P_5(:,:,ome__5)*D(:,:,ome__5))*D(:,:,ome__5)'*MF_x1*P_5(:,:,ome__5)*MF_x1*y_NT2(:,ome__5) ;
+opt_theta_IV_i_5(:,ome__5)= pinv(D(:,:,ome__5)'*MF_x1*P_5(:,:,ome__5)*MF_x1*D(:,:,ome__5))*D(:,:,ome__5)'*MF_x1*P_5(:,:,ome__5)*MF_x1*y_NT2(:,ome__5) ;
 end
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-03-05 MC_code/IV_Norkute2.m
up

@@ -1,0 +1,329 @@
+tic
+rep = 2000;  
+list_T = [ 25 50  100]; 
+list_N = [25  50 100];  
+list_phi= [0.5 ]; 
+b1=3;
+b2=1;
+b=[b1,b2]; % 1 by k 
+rho=0; % lag of x ARDL(0,1) 
+pi_u=0.75; % 0.25 or 0.75
+SNR=4;
+Mu1=1;
+Mu2=-0.5;
+A=0.5;
+rho_gamma_1s=0; %  0 independent factor loading; 0.5 correlated loading
+k=2;   % number of regressors
+m_x=2; % number of factors of regressor
+my=1;
+m_y=m_x+my; % number of factors of y
+xi_es=(pi_u/(1-pi_u))*m_y;
+
+rho_mu=0.5;
+rho_v=0.5;
+rho_b=0.4;
+xi_ev=xi_es*(SNR-(rho_v^(2)/(1-rho_v^(2))))*((b1^(2)+b2^(2))/(1-rho_v^(2)))^(-1);
+
+
+
+j=1; % lag of regressor
+Dis_T=50;
+%%%%%%%%%%%%%%%%%%%%%%%%
+ini_bias_mean_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_bias_mean_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
+
+ini_std_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
+ini_std_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
+
+ini_rmse_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_rmse_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+
+ini_mae_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_mae_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+
[…]

### 2020-03-05 MC_code/opt_IV_factor.m

@@ -1,8 +1,8 @@
 tic
 rep = 500;  
-list_T = [ 25 ]; 
-list_N = [25 ];  
-list_phi= [0.8]; 
+list_T = [ 25  ]; 
+list_N = [50  ];  
+list_phi= [0.5 ]; 
 b1=3;
 b2=1;
 b=[b1,b2]; % 1 by k 
@@ -17,16 +17,16 @@ k=2;   % number of regressors
 m_x=2; % number of factors of regressor
 my=1;
 m_y=m_x+my; % number of factors of y
-xi_es=sqrt((pi_u/(1-pi_u))*m_y);
+xi_es=(pi_u/(1-pi_u))*m_y;
 
 rho_mu=0.5;
 rho_v=0.5;
 rho_b=0.4;
-xi_ev=xi_es^(2)*(SNR-(rho_v^(2)/(1-rho_v^(2))))*((b1^(2)+b2^(2))/(1-rho_v^(2)))^(-1);
+xi_ev=xi_es*(SNR-(rho_v^(2)/(1-rho_v^(2))))*((b1^(2)+b2^(2))/(1-rho_v^(2)))^(-1);
 
 
 
-j=5; % lag of regressor
+j=7; % lag of regressor
 Dis_T=50;
 %%%%%%%%%%%%%%%%%%%%%%%%
 ini_bias_mean_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
@@ -94,14 +94,36 @@ opt_rmse_beta1_5=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
 opt_mae_phi_5=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
 opt_mae_beta1_5=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+opt_bias_mean_phi_6=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+opt_bias_mean_beta1_6=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
 
[…]

### 2020-03-06 MC_code/MAIV_opt_nores_2.m
up

@@ -1,0 +1,26 @@
+function [omega_2, fval_2, exitflag_2, output_2, lambda_2, hessian_2]=MAIV_opt_nores_2(T1,K_2,sigma_etau_i,Sigma_u_i_i,Sigma_eta_i_i, hat_U_i_2,Gamma_2, Sigmau_2,sigmaue_2,A1,A2, H2,etai2,d,j2,omega0,lq_2,uq_2)
+ 
+% maximum likelihood routine. see the program transformed_ml.m
+ 
+
+[omega_2, fval_2, exitflag_2, output_2, lambda_2,~,hessian_2] = fmincon(@likelihood,omega0,[],[],[ones(1,j2)],1,lq_2,uq_2,[]); 
+ 
+    function [likelihood]=likelihood(omega)
+ dim_omega = size(omega0,1);
+    omega  = omega(1:dim_omega,1);
+ 
+    
+ 
+ B_N=2*(Sigma_u_i_i*Sigmau_2+d*real(sigmaue_2*sigmaue_2')+A1/T1+A2/T1);
+    
+ sigma_mse=(sigma_etau_i^2)*((K_2'*omega)^2)/T1+(Sigma_u_i_i*Sigma_u_i_i+sigma_etau_i^2)*(omega'*Gamma_2*omega/T1)-(K_2'*omega/T1)*etai2'* pinv(H2)*B_N*pinv(H2)*etai2+Sigma_u_i_i*((omega'*hat_U_i_2*omega- Sigma_eta_i_i*(j2-2*K_2'*omega+omega'*Gamma_2*omega))/T1);
+  
+    
+    
+ likelihood = sigma_mse;
+    
+    
+    
+  
+end
+end

### 2020-03-06 MC_code/MAIV_opt_nores_3.m

@@ -1,0 +1,26 @@
+function [omega_3, fval_3, exitflag_3, output_3, lambda_3, hessian_3]=MAIV_opt_nores_3(T1,K_3,sigma_etau_i,Sigma_u_i_i,Sigma_eta_i_i, hat_U_i_3,Gamma_3, Sigmau_3,sigmaue_3,A1,A2, H2,etai3,d,j3,omega0,lq_3,uq_3)
+ 
+% maximum likelihood routine. see the program transformed_ml.m
+ 
+
+[omega_3, fval_3, exitflag_3, output_3, lambda_3,~,hessian_3] = fmincon(@likelihood,omega0,[],[],[ones(1,j3)],1,lq_3,uq_3,[]); 
+ 
+    function [likelihood]=likelihood(omega)
+ dim_omega = size(omega0,1);
+    omega  = omega(1:dim_omega,1);
+ 
+    
+ 
+ B_N=2*(Sigma_u_i_i*Sigmau_3+d*real(sigmaue_3*sigmaue_3')+A1/T1+A2/T1);
+    
+ sigma_mse=(sigma_etau_i^2)*((K_3'*omega)^2)/T1+(Sigma_u_i_i*Sigma_u_i_i+sigma_etau_i^2)*(omega'*Gamma_3*omega/T1)-(K_3'*omega/T1)*etai3'* pinv(H2)*B_N*pinv(H2)*etai3+Sigma_u_i_i*((omega'*hat_U_i_3*omega- Sigma_eta_i_i*(j3-2*K_3'*omega+omega'*Gamma_3*omega))/T1);
+  
+    
+    
+ likelihood = sigma_mse;
+    
+    
+    
+  
+end
+end

### 2020-03-06 MC_code/MAIV_opt_nores_4.m

@@ -1,0 +1,26 @@
+function [omega_4, fval_4, exitflag_4, output_4, lambda_4, hessian_4]=MAIV_opt_nores_4(T1,K_4,sigma_etau_i,Sigma_u_i_i,Sigma_eta_i_i, hat_U_i_4,Gamma_4, Sigmau_4,sigmaue_4,A1,A2, H2,etai4,d,j4,omega0,lq_4,uq_4)
+ 
+% maximum likelihood routine. see the program transformed_ml.m
+ 
+
+[omega_4, fval_4, exitflag_4, output_4, lambda_4,~,hessian_4] = fmincon(@likelihood,omega0,[],[],[ones(1,j4)],1,lq_4,uq_4,[]); 
+ 
+    function [likelihood]=likelihood(omega)
+ dim_omega = size(omega0,1);
+    omega  = omega(1:dim_omega,1);
+ 
+    
+ 
+ B_N=2*(Sigma_u_i_i*Sigmau_4+d*real(sigmaue_4*sigmaue_4')+A1/T1+A2/T1);
+    
+ sigma_mse=(sigma_etau_i^2)*((K_4'*omega)^2)/T1+(Sigma_u_i_i*Sigma_u_i_i+sigma_etau_i^2)*(omega'*Gamma_4*omega/T1)-(K_4'*omega/T1)*etai4'* pinv(H2)*B_N*pinv(H2)*etai4+Sigma_u_i_i*((omega'*hat_U_i_4*omega- Sigma_eta_i_i*(j4-2*K_4'*omega+omega'*Gamma_4*omega))/T1);
+  
+    
+    
+ likelihood = sigma_mse;
+    
+    
+    
+  
+end
+end

### 2020-03-06 MC_code/MAIV_opt_nores_5.m

@@ -1,0 +1,26 @@
+function [omega_5, fval_5, exitflag_5, output_5, lambda_5, hessian_5]=MAIV_opt_nores_5(T1,K_5,sigma_etau_i,Sigma_u_i_i,Sigma_eta_i_i, hat_U_i_5,Gamma_5, Sigmau_5,sigmaue_5,A1,A2, H2,etai5,d,j5,omega0,lq_5,uq_5)
+ 
+% maximum likelihood routine. see the program transformed_ml.m
+ 
+
+[omega_5, fval_5, exitflag_5, output_5, lambda_5,~,hessian_5] = fmincon(@likelihood,omega0,[],[],[ones(1,j5)],1,lq_5,uq_5,[]); 
+ 
+    function [likelihood]=likelihood(omega)
+ dim_omega = size(omega0,1);
+    omega  = omega(1:dim_omega,1);
+ 
+    
+ 
+ B_N=2*(Sigma_u_i_i*Sigmau_5+d*real(sigmaue_5*sigmaue_5')+A1/T1+A2/T1);
+    
+ sigma_mse=(sigma_etau_i^2)*((K_5'*omega)^2)/T1+(Sigma_u_i_i*Sigma_u_i_i+sigma_etau_i^2)*(omega'*Gamma_5*omega/T1)-(K_5'*omega/T1)*etai5'* pinv(H2)*B_N*pinv(H2)*etai5+Sigma_u_i_i*((omega'*hat_U_i_5*omega- Sigma_eta_i_i*(j5-2*K_5'*omega+omega'*Gamma_5*omega))/T1);
+  
+    
+    
+ likelihood = sigma_mse;
+    
+    
+    
+  
+end
+end

### 2020-03-06 MC_code/MAIV_opt_nores_6.m

@@ -1,0 +1,26 @@
+function [omega_6, fval_6, exitflag_6, output_6, lambda_6, hessian_6]=MAIV_opt_nores_6(T1,K_6,sigma_etau_i,Sigma_u_i_i,Sigma_eta_i_i, hat_U_i_6,Gamma_6, Sigmau_6,sigmaue_6,A1,A2, H2,etai6,d,j6,omega0,lq_6,uq_6)
+ 
+% maximum likelihood routine. see the program transformed_ml.m
+ 
+
+[omega_6, fval_6, exitflag_6, output_6, lambda_6,~,hessian_6] = fmincon(@likelihood,omega0,[],[],[ones(1,j6)],1,lq_6,uq_6,[]); 
+ 
+    function [likelihood]=likelihood(omega)
+ dim_omega = size(omega0,1);
+    omega  = omega(1:dim_omega,1);
+ 
+    
+ 
+ B_N=2*(Sigma_u_i_i*Sigmau_6+d*real(sigmaue_6*sigmaue_6')+A1/T1+A2/T1);
+    
+ sigma_mse=(sigma_etau_i^2)*((K_6'*omega)^2)/T1+(Sigma_u_i_i*Sigma_u_i_i+sigma_etau_i^2)*(omega'*Gamma_6*omega/T1)-(K_6'*omega/T1)*etai6'* pinv(H2)*B_N*pinv(H2)*etai6+Sigma_u_i_i*((omega'*hat_U_i_6*omega- Sigma_eta_i_i*(j6-2*K_6'*omega+omega'*Gamma_6*omega))/T1);
+  
+    
+    
+ likelihood = sigma_mse;
+    
+    
+    
+  
+end
+end

### 2020-03-06 MC_code/MAIV_opt_nores_7.m

@@ -1,0 +1,26 @@
+function [omega_7, fval_7, exitflag_7, output_7, lambda_7, hessian_7]=MAIV_opt_nores_7(T1,K_7,sigma_etau_i,Sigma_u_i_i,Sigma_eta_i_i, hat_U_i_7,Gamma_7, Sigmau_7,sigmaue_7,A1,A2, H2,etai7,d,j7,omega0,lq_7,uq_7)
+ 
+% maximum likelihood routine. see the program transformed_ml.m
+ 
+
+[omega_7, fval_7, exitflag_7, output_7, lambda_7,~,hessian_7] = fmincon(@likelihood,omega0,[],[],[ones(1,j7)],1,lq_7,uq_7,[]); 
+ 
+    function [likelihood]=likelihood(omega)
+ dim_omega = size(omega0,1);
+    omega  = omega(1:dim_omega,1);
+ 
+    
+ 
+ B_N=2*(Sigma_u_i_i*Sigmau_7+d*real(sigmaue_7*sigmaue_7')+A1/T1+A2/T1);
+    
+ sigma_mse=(sigma_etau_i^2)*((K_7'*omega)^2)/T1+(Sigma_u_i_i*Sigma_u_i_i+sigma_etau_i^2)*(omega'*Gamma_7*omega/T1)-(K_7'*omega/T1)*etai7'* pinv(H2)*B_N*pinv(H2)*etai7+Sigma_u_i_i*((omega'*hat_U_i_7*omega- Sigma_eta_i_i*(j7-2*K_7'*omega+omega'*Gamma_7*omega))/T1);
+  
+    
+    
+ likelihood = sigma_mse;
+    
+    
+    
+  
+end
+end

### 2020-03-06 MC_code/opt_IV_factor_norestrition.m

@@ -1,0 +1,1008 @@
+tic
+rep = 500;  
+list_T = [ 25 ]; 
+list_N = [25 ];  
+list_phi= [0.5 ]; 
+b1=3;
+b2=1;
+b=[b1,b2]; % 1 by k 
+rho=0; % lag of x ARDL(0,1) 
+pi_u=0.75; % 0.25 or 0.75
+SNR=4;
+Mu1=1;
+Mu2=-0.5;
+A=0.5;
+rho_gamma_1s=0; %  0 independent factor loading; 0.5 correlated loading
+k=2;   % number of regressors
+m_x=2; % number of factors of regressor
+my=1;
+m_y=m_x+my; % number of factors of y
+xi_es=(pi_u/(1-pi_u))*m_y;
+
+rho_mu=0.5;
+rho_v=0.5;
+rho_b=0.4;
+xi_ev=xi_es*(SNR-(rho_v^(2)/(1-rho_v^(2))))*((b1^(2)+b2^(2))/(1-rho_v^(2)))^(-1);
+
+
+
+j=7; % lag of regressor
+Dis_T=50;
+%%%%%%%%%%%%%%%%%%%%%%%%
+ini_bias_mean_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_bias_mean_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
+
+ini_std_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
+ini_std_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
+
+ini_rmse_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_rmse_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+
+ini_mae_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_mae_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
[…]

### 2020-03-06 Draft_V6.tex

@@
 	\definecolor{ultramarine}{rgb}{0.07, 0.04, 0.56}
-\usepackage{amsmath, natbib, latexsym, array, amssymb,longtable,float, graphicx, appendix,lscape,diagbox,textcomp,placeins}
+\usepackage{amsmath, natbib, latexsym, array, amssymb,longtable,float, graphicx, appendix,lscape,diagbox,textcomp,placeins,mathtools}
 \usepackage[colorlinks,
@@
 \setcounter{secnumdepth}{3}
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
+\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
+\makeatletter
+\let\oldabs\abs
 \begin{document}
@@
 \HRule \\[0.4cm]
-{ \huge \bfseries Dynamic Heterogeneous Panels with multi-factor error sructure}\\[0.4cm] % Title of your document
+{ \huge \bfseries Model Average of Dynamic Heterogeneous Panels with multi-factor error sructure}\\[0.4cm] % Title of your document
 \HRule \\[1.5cm]
@@
 \begin{align}
-\boldsymbol{Z}_{i}=\left( \boldsymbol{M}_{F_{x}}\boldsymbol{X}_{i}, \boldsymbol{M}_{F_{x,-1}}\boldsymbol{X}_{i,-1},\ldots  ,\boldsymbol{M}_{F_{x,-j}}\boldsymbol{X}_{i,-j}, \right)
+\hat{\boldsymbol{Z}}^{j}_{i}=\left( \boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{X}_{i}, \boldsymbol{M}_{\hat{F}_{x,-1}}\boldsymbol{X}_{i,-1},\ldots  ,\boldsymbol{M}_{\hat{F}_{x,-j}}\boldsymbol{X}_{i,-j}, \right)
 \end{align}
@@
 \begin{align}
-\boldsymbol{P}^{(j)}_{i}=\boldsymbol{Z}^{(j)}_{i} \left(\boldsymbol{Z}^{(j)'}_{i}\boldsymbol{Z}^{(j)}_{i} \right)^{-1}\boldsymbol{Z}^{(j)'}_{i}
+\boldsymbol{P}^{(j)}_{i}=\hat{\boldsymbol{Z}}^{(j)}_{i} \left(\hat{\boldsymbol{Z}}^{(j)'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\hat{\boldsymbol{Z}}^{(j)}_{i} \right)^{-1}\hat{\boldsymbol{Z}}^{(j)'}_{i}
 \end{align}
@@
 \begin{align}
-\hat{\boldsymbol{\theta}}_{i}= \left( \boldsymbol{W}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \boldsymbol{W}^{b}_{i} \right)^{-1} \boldsymbol{W}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \boldsymbol{y}_{i},
+\hat{\boldsymbol{\theta}}_{i}= \left( \boldsymbol{W}^{'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{P}^{(j)}_{i}\boldsymbol{M}_{\hat{F}_{x}} \boldsymbol{W}_{i} \right)^{-1} \boldsymbol{W}^{'}_{i}\boldsymbol{P}^{(j)}_{i}\boldsymbol{M}_{\hat{F}_{x}} \boldsymbol{y}_{i},
 \end{align}
@@
 \begin{align}
-\hat{\boldsymbol{\theta}}^{\ast b}_{i}= \left( \tilde{\boldsymbol{W}}^{b'}_{i}\boldsymbol{P}^{b}_{i}\left(\boldsymbol{\omega^{(i)\ast}} \right)\tilde{\boldsymbol{W}}^{b}_{i} \right)^{-1} \tilde{\boldsymbol{W}}^{b'}_{i}\boldsymbol{P}^{b}_{i}\left(\boldsymbol{\omega^{(i)\ast}} \right) \tilde{\boldsymbol{y}}^{b}_{i}.
+\hat{\boldsymbol{\theta}}^{\ast }_{i}= \left( \tilde{\boldsymbol{W}}^{'}_{i}\boldsymbol{P}_{i}\left(\boldsymbol{\omega^{(i)\ast}} \right)\tilde{\boldsymbol{W}}_{i} \right)^{-1} \tilde{\boldsymbol{W}}^{'}_{i}\boldsymbol{P}_{i}\left(\boldsymbol{\omega^{(i)\ast}} \right) \tilde{\boldsymbol{y}}_{i}.
 \end{align}
@@
 \appendixpage
+\section{Consistency of model average IV estimator}
+First we consider IV estimator without model average. From previous section, IV estimator can be written as 
+\begin{align}
+\begin{split}
+\sqrt{T}\left(\hat{\boldsymbol{\theta}}_{i}-\boldsymbol{\theta}_{i}\right)&= \left( \boldsymbol{W}^{'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\hat{\boldsymbol{Z}}^{(j)}_{i} \left(\hat{\boldsymbol{Z}}^{(j)'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\hat{\boldsymbol{Z}}^{(j)}_{i} \right)^{-1}\hat{\boldsymbol{Z}}^{(j)'}_{i}\boldsymbol{M}_{\hat{F}_{x}} \boldsymbol{W}_{i} \right)^{-1} \times \\ &\boldsymbol{W}^{'}_{i}\hat{\boldsymbol{Z}}^{(j)}_{i} \left(\hat{\boldsymbol{Z}}^{(j)'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\hat{\boldsymbol{Z}}^{(j)}_{i} \right)^{-1}\left( T^{-1/2} \hat{\boldsymbol{Z}}^{(j)'}_{i}\boldsymbol{M}_{\hat{F}_{x}} \boldsymbol{u}_{i}\right),
+\end{split}
+\end{align}
+When $N,T \to \infty$, we can show $T^{-1/2} \hat{\boldsymbol{Z}}^{(j)'}_{i}\boldsymbol{M}_{\hat{F}_{x}} \boldsymbol{u}_{i}$ is $O_{p}\left(1 \right)$ as following.
+Consider the first element of $\hat{\boldsymbol{Z}}^{(j)}_{i}=\left( \boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{X}_{i}, \boldsymbol{M}_{\hat{F}_{x,-1}}\boldsymbol{X}_{i,-1},\ldots  ,\boldsymbol{M}_{\hat{F}_{x,-j}}\boldsymbol{X}_{i,-j} \right).$ Then we have
+\begin{align}
+T^{-1/2} \hat{\boldsymbol{X}}^{'}_{i}\boldsymbol{M}_{\hat{F}_{x}} \boldsymbol{u}_{i}= T^{-1/2} \hat{\boldsymbol{X}}^{'}_{i}\boldsymbol{M}_{\hat{F}^{0}_{x}} \boldsymbol{u}_{i}+T^{-1/2} \hat{\boldsymbol{X}}^{'}_{i} \left(\boldsymbol{M}_{\hat{F}_{x}} -\boldsymbol{M}_{\hat{F}^{0}_{x}} \right) \boldsymbol{u}_{i}.
+\end{align}
+
+\begin{align}
+\begin{split}
+&T^{-1/2} \hat{\boldsymbol{X}}^{'}_{i} \left(\boldsymbol{M}_{\hat{F}_{x}}-\boldsymbol{M}_{\hat{F}^{0}_{x}} \right) \boldsymbol{u}_{i}= -T^{-1/2} \hat{\boldsymbol{X}}^{'}_{i} \left( \frac{\hat{\boldsymbol{F}}^{'}_{x}\hat{\boldsymbol{F}}_{x}  }{T} -\boldsymbol{P}_{F^{0}_{x}}  \right) \boldsymbol{u}_{i}= \\
+&  -T^{-1/2} \frac{\boldsymbol{X}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}  \right)}{T}\boldsymbol{G}^{'}_{x}\boldsymbol{F}^{0'}_{x}\boldsymbol{u}_{i}-T^{-1/2} \frac{\boldsymbol{X}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x} \boldsymbol{G}_{x}  \right)}{T}\left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}   \right)^{'}\boldsymbol{u}_{i} \\
+& -T^{-1/2} \frac{\boldsymbol{X}^{'}_{i}\boldsymbol{F}^{0}_{x} }{T}\boldsymbol{G}_{x} \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}   \right)^{'}\boldsymbol{u}_{i}-T^{-1/2} \frac{\boldsymbol{X}^{'}_{i} \boldsymbol{F}^{0}_{x}}{T} \left( \boldsymbol{G}_{x}\boldsymbol{G}^{'}_{x}-\left( \frac{\boldsymbol{F}^{0'}_{x} \boldsymbol{F}^{0}_{x} }{T} \right)^{-1}      \right)\boldsymbol{F}^{0'}_{x}\boldsymbol{u}_{i} \\
+&= -\left( b_{1}+ b_{2}+b_{3}+b_{4} \right).
+\end{split}
+\end{align}
+By Cauchy–Schwarz inequality we know
+
+\begin{align}
+\begin{split}
+&\abs{b_{1}}\leq T^{1/2} \norm{\frac{ \boldsymbol{X}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right) }{T}} \norm{\boldsymbol{G}_{x}}\norm{\frac{\boldsymbol{F}^{0'}_{x}\boldsymbol{u}_{i}}{T}}\leq T^{1/2} \norm{\boldsymbol{\Gamma}_{x,i}}\norm{\frac{\boldsymbol{F}^{'}_{x}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right)}{T}}\norm{\boldsymbol{G}_{x}} \norm{\frac{\boldsymbol{F}^{0}_{x}}{\sqrt{T}}}\norm{\frac{\boldsymbol{u}_{i}}{\sqrt{T}}}\\
+&+T^{1/2} \norm{\frac{\boldsymbol{V}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G} \right)}{T} } \norm{\boldsymbol{G}_{x}}\norm{\frac{\boldsymbol{F}^{0}_{x}}{\sqrt{T}}} \norm{\frac{\boldsymbol{u}_{i}}{\sqrt{T}}}=\sqrt{T}O_{p}\left(c^{-2}_{NT} \right),
+\end{split}
+\end{align}
+where $\norm{\frac{\boldsymbol{F}^{0'}_{x}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right) }{T}}= O_{p}\left(c^{-2}_{NT}\right)$, $\norm{\frac{\boldsymbol{V}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G} \right)}{T} }=  O_{p}\left(c^{-2}_{NT}\right)$, $ \norm{\boldsymbol{G}_{x}}=  O_{p}\left(c^{-2}_{NT}\right)$, $\norm{\boldsymbol{\Gamma}_{x,i}}=  O_{p}\left(c^{-2}_{NT}\right)$, $\frac{ \norm{\boldsymbol{F}^{0}_{x}}}{\sqrt{T}}=  O_{p}\left(c^{-2}_{NT}\right)$, $ \norm{\frac{\boldsymbol{u}_{i}}{\sqrt{T}}}\leq \norm{\boldsymbol{\gamma^{0}_{i}}} \frac{\norm{\boldsymbol{F}^{0}_{y}}}{\sqrt{T}}+\norm{\boldsymbol{\lambda}^{0}_{i}} \frac{ \norm{\boldsymbol{F}^{0}_{y}} }{\sqrt{T}}+ \frac{\norm{\varepsilon_{i} } }{\sqrt{T}}=O_{p}\left(c^{-2}_{NT}\right).$
+
+\begin{align}
+\begin{split}
+\abs{b_{2}}&\leq \sqrt{T} \norm{\frac{\boldsymbol{X}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right)}{T}} \norm{\frac{ \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}   \right)^{'}\boldsymbol{u}_{i}}{T} } \\
+& \leq \sqrt{T} \norm{\Gamma_{x,i}} \norm{\frac{\boldsymbol{F}^{'}_{x}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right)}{T}} \norm{\frac{ \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}  \right)^{'}\boldsymbol{u}_{i}}{T}}+ \\
+&\sqrt{T}  \norm{\Gamma_{x,i}} \norm{\frac{\boldsymbol{V}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right)}{T}} \norm{\frac{ \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}  \right)^{'}\boldsymbol{u}_{i}}{T}}= \sqrt{T}O_{p}\left( c^{-2}_{NT} \right),
+\end{split}
+\end{align}
+where $\norm{\frac{\boldsymbol{u}^{'}_{i} \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}  \right)^{'}}{T}} \leq \norm{\boldsymbol{\gamma}^{0}_{i}} \norm{\frac{\boldsymbol{V}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right)}{T}} + \norm{\boldsymbol{\lambda}^{0}_{i}} \norm{\frac{\boldsymbol{F}^{0'}_{y} \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}  \right)}{T}}+ \norm{\frac{\boldsymbol{\varepsilon}^{'}_{i} \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}  \right)}{T}} $
+
+\begin{align}
+\begin{split}
+\abs{b_{3}}&\leq  \sqrt{T} \norm{\frac{\boldsymbol{X}^{'}_{i}\boldsymbol{F}^{0}_{x} }{T}} \norm{\boldsymbol{G}_{x} } \norm{ \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}   \right)^{'}\boldsymbol{u}_{i} } \\
+&\leq \sqrt{T} \norm{\boldsymbol{\Gamma}_{x,i}} \norm{\frac{\boldsymbol{F}^{'}_{x}\boldsymbol{F}_{x}}{T}} \norm{\boldsymbol{G}_{x}} \norm{ \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}   \right)^{'}\boldsymbol{u}_{i}} +\\
+&\sqrt{T} \norm{ \frac{\boldsymbol{V}_{i}}{\sqrt{T}} } \norm{\frac{\boldsymbol{F}^{0}_{x}}{\sqrt{T}} } \norm{\boldsymbol{G}_{x}} \norm{ \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}   \right)^{'}\boldsymbol{u}_{i}}=\sqrt{T}O_{p}\left( c^{-2}_{NT} \right).
+\end{split}
+\end{align}
+
+\begin{align}
+\begin{split}
+\abs{b_{4}}&\leq   \sqrt{T}\norm{\frac{\boldsymbol{X}^{'}_{i}\boldsymbol{F}^{0}_{x} }{T}}  \norm{\boldsymbol{G}_{x}\boldsymbol{G}^{'}_{x}-\left(\frac{\boldsymbol{F}^{0'}_{x}\boldsymbol{F}^{0}_{x}}{T}  \right)^{-1} }\norm{\frac{\boldsymbol{F}^{0'}_{x}\boldsymbol{u}_{i}}{T}} \\
+& \sqrt{T} \norm{\boldsymbol{G}_{x} } \norm{\frac{\boldsymbol{F}^{'}_{x}\boldsymbol{F}_{x}}{T}}  \norm{\boldsymbol{G}_{x}\boldsymbol{G}^{'}_{x}-\left(\frac{\boldsymbol{F}^{0'}_{x}\boldsymbol{F}^{0}_{x}}{T}  \right)^{-1} } \norm{\frac{\boldsymbol{F}^{0'}_{x}\boldsymbol{u}_{i}}{T} }=\sqrt{T}O_{p}\left( c^{-2}_{NT} \right).
+\end{split}
+\end{align}
+
+Then, we can see
+\begin{align}
+\norm{T^{-1/2} \hat{\boldsymbol{X}}^{'}_{i} \left(\boldsymbol{M}_{\hat{F}_{x}}-\boldsymbol{M}_{\hat{F}^{0}_{x}} \right) \boldsymbol{u}_{i}}= \sqrt{T}O_{p}\left( c^{-2}_{NT} \right)
+\end{align}
+and
+\begin{align}
+T^{-1/2} \boldsymbol{X}^{'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{u}_{i}=T^{-1/2} \boldsymbol{X}^{'}_{i}\boldsymbol{M}_{F^{0}_{x}}\boldsymbol{u}_{i}+\sqrt{T}O_{p}\left( c^{-2}_{NT} \right)
+\end{align}
+Thus, we know when $N,T \to \infty$, $T^{-1/2} \boldsymbol{X}^{'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{u}_{i}$ is $O_{p}\left( 1 \right)$
+Next, we consider the second element of $\hat{\boldsymbol{Z}}^{(j)}_{i}=\left( \boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{X}_{i}, \boldsymbol{M}_{\hat{F}_{x,-1}}\boldsymbol{X}_{i,-1},\ldots  ,\boldsymbol{M}_{\hat{F}_{x,-j}}\boldsymbol{X}_{i,-j} \right).$ Then we have
+\begin{align}
+\begin{split}
+&T^{-1/2} \boldsymbol{X}^{'}_{i,-1} \boldsymbol{M}_{\hat{F}_{x,-1}}\boldsymbol{M}_{F^{0}_{x}} \boldsymbol{u}_{i}= T^{-1/2} \boldsymbol{X}^{'}_{i,-1} \boldsymbol{M}_{F^{0}_{x,-1}}\boldsymbol{M}_{F^{0}_{x}} \boldsymbol{u}_{i}+\\
+&   T^{-1/2} \boldsymbol{X}^{'}_{i,-1} \left(\boldsymbol{M}_{\hat{F}_{x,-1}}- \boldsymbol{M}_{F^{0}_{x,-1}}  \right)\boldsymbol{M}_{F^{0}_{x}} \boldsymbol{u}_{i}+ T^{-1/2} \boldsymbol{X}^{'}_{i,-1} \boldsymbol{M}_{\hat{F}_{x,-1}} \left(\boldsymbol{M}_{\hat{F}_{x}}  \boldsymbol{M}_{F^{0}_{x}} \right) \boldsymbol{u}_{i}
+\end{split}
+\end{align}
+ For the right hand side of above equation, we have 
+\begin{align}
+\begin{split}
+& T^{-1/2} \boldsymbol{X}^{'}_{i,-1} \boldsymbol{M}_{\hat{F}_{x,-1}} \left(\boldsymbol{M}_{\hat{F}_{x}} - \boldsymbol{M}_{F^{0}_{x}} \right) \boldsymbol{u}_{i}= \\
+ &T^{-1/2} \boldsymbol{X}^{'}_{i,-1} \boldsymbol{M}_{\hat{F}_{x,-1}} \left(\boldsymbol{M}_{\hat{F}_{x}}-  \boldsymbol{M}_{F^{0}_{x}} \right) \boldsymbol{u}_{i}+ T^{-1/2} \boldsymbol{X}^{'}_{i,-1} \boldsymbol{P}_{\hat{F}_{x,-1}} \left(\boldsymbol{M}_{\hat{F}_{x}}  -\boldsymbol{M}_{F^{0}_{x}} \right) \boldsymbol{u}_{i} \\
+ &= \sqrt{T}O_{p}\left( c^{-2}_{NT} \right)
+\end{split}
+\end{align}
+and
+\begin{align}
+\begin{split}
+& T^{-1/2} \boldsymbol{X}^{'}_{i,-1}  \left(\boldsymbol{M}_{\hat{F}_{x,-1}} - \boldsymbol{M}_{F^{0}_{x,-1}} \right) \boldsymbol{M}_{F^{0}_{x}}\boldsymbol{u}_{i}= \\
+ &T^{-1/2} \boldsymbol{X}^{'}_{i,-1} \left(\boldsymbol{M}_{\hat{F}_{x}}-  \boldsymbol{M}_{F^{0}_{x}} \right) \boldsymbol{u}_{i}- T^{-1/2} \boldsymbol{X}^{'}_{i,-1} \left(\boldsymbol{M}_{\hat{F}_{x,-1}}  -\boldsymbol{M}_{F^{0}_{x,-1}} \right)  \boldsymbol{P}_{\hat{F}^{0}_{x}} \boldsymbol{u}_{i} \\
+ &= \sqrt{T}O_{p}\left( c^{-2}_{NT} \right)
+\end{split}
+\end{align}
+
 \section{Asymptotic property of LS estimator}

### 2020-03-06 MC_code/opt_IV_factor_norestrition.m
up

@@ -1,8 +1,8 @@
 tic
 rep = 500;  
-list_T = [ 25 ]; 
-list_N = [25 ];  
-list_phi= [0.5 ]; 
+list_T = [ 50 ]; 
+list_N = [50 ];  
+list_phi= [0.8 ]; 
 b1=3;
 b2=1;
 b=[b1,b2]; % 1 by k 

### 2020-03-06 MC_code/IV_Norkute2.m
up

@@ -1,8 +1,8 @@
 tic
-rep = 2000;  
-list_T = [ 25 50  100]; 
-list_N = [25  50 100];  
-list_phi= [0.5 ]; 
+rep = 500;  
+list_T = [ 25 50 100  ]; 
+list_N = [25   ];  
+list_phi= [0.5]; 
 b1=3;
 b2=1;
 b=[b1,b2]; % 1 by k 
@@ -23,8 +23,6 @@ rho_mu=0.5;
 rho_v=0.5;
 rho_b=0.4;
 xi_ev=xi_es*(SNR-(rho_v^(2)/(1-rho_v^(2))))*((b1^(2)+b2^(2))/(1-rho_v^(2)))^(-1);
-
-
 
 j=1; % lag of regressor
 Dis_T=50;
@@ -82,7 +80,7 @@ while sml<=rep
 
 
 eta_rho_i=-0.2+(0.4)*rand([1,N]); % 1 by N heterogeneous_y U(-0.2,0.2)
-eta_rho_bi=-sqrt(3)+2*sqrt(3)*rand([k,N]);
+eta_rho_bi=-sqrt(3)+2*sqrt(3)*rand([1,N]);
 
 
 phi_i= phi+  eta_rho_i;
@@ -93,14 +91,13 @@ for ttt=2:TT
     for iiii=1:N
 %v_x(:,iiii,ttt)=0.5*v_x(:,iiii,ttt-1)+sqrt((1-0.5^(2)))*normrnd(0,sqrt(xi_ev*sig_bar_w(iiii,1)),[k,1]); % k by N by TT
 v_x(:,iiii,ttt)=0.5*v_x(:,iiii,ttt-1)+sqrt((1-0.5^(2)))*normrnd(0,sqrt(xi_ev),[k,1]); % k by N by TT
-
     end 
 end
 bar_v_i=zeros(k,N);
-for tttt=1:TT
+for tttt=TT-T0+1:TT
 bar_v_i=bar_v_i+(v_x(:,:,tttt).^2);
 end
-bar_v_i=bar_v_i/TT; % k by N
+bar_v_i=bar_v_i/T0; % k by N
 bar_v=sum(bar_v_i,2)/N; % k by 1
 diff_bar_v=bar_v_i-bar_v*ones(1,N); % k by N
[…]

### 2020-03-07 MC_code/IV_Norkute2.m
up

@@ -1,7 +1,7 @@
 tic
 rep = 500;  
-list_T = [ 25 50 100  ]; 
-list_N = [25   ];  
+list_T = [ 35 50 100 ]; 
+list_N = [25 50 100  ];  
 list_phi= [0.5]; 
 b1=3;
 b2=1;
@@ -76,12 +76,8 @@ rand('state', 1234567) ;
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 sml=1;         
 while sml<=rep
-%parfor sml=1:rep
-
-
 eta_rho_i=-0.2+(0.4)*rand([1,N]); % 1 by N heterogeneous_y U(-0.2,0.2)
 eta_rho_bi=-sqrt(3)+2*sqrt(3)*rand([1,N]);
-
 
 phi_i= phi+  eta_rho_i;
 sig_bar_w=0.5+rand(N,1);
@@ -89,8 +85,8 @@ v_x=zeros(k,N,TT);
 v_x(:,:,1)=zeros(k,N,1);  
 for ttt=2:TT
     for iiii=1:N
-%v_x(:,iiii,ttt)=0.5*v_x(:,iiii,ttt-1)+sqrt((1-0.5^(2)))*normrnd(0,sqrt(xi_ev*sig_bar_w(iiii,1)),[k,1]); % k by N by TT
-v_x(:,iiii,ttt)=0.5*v_x(:,iiii,ttt-1)+sqrt((1-0.5^(2)))*normrnd(0,sqrt(xi_ev),[k,1]); % k by N by TT
+v_x(:,iiii,ttt)=0.5*v_x(:,iiii,ttt-1)+sqrt((1-0.5^(2)))*normrnd(0,sqrt(xi_ev*sig_bar_w(iiii,1)),[k,1]); % k by N by TT
+%v_x(:,iiii,ttt)=0.5*v_x(:,iiii,ttt-1)+sqrt((1-0.5^(2)))*normrnd(0,sqrt(xi_ev),[k,1]); % k by N by TT
     end 
 end
 bar_v_i=zeros(k,N);
[…]

### 2020-03-08 MC_code/IV_MG.m
up

@@ -1,139 +1,0 @@
-rep = 2000;  
-list_T = [25 50 100 200]; 
-list_N = [25 50 100 200];  
-list_phi= [0.5]; 
-rho=0;
-b1=3;
-b2=1;
-rho_b=0.4;
-b=[b1,b2];
-k=2;   % number of regressors
-bias_mean_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); bias_mean_beta1=zeros(size(list_T,2), size(list_N,2)); 
-bias_mean_beta2=zeros(size(list_T,2), size(list_N,2)); 
-std_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-std_beta1=zeros(size(list_T,2), size(list_N,2));  
-std_beta2=zeros(size(list_T,2), size(list_N,2));  
-rmse_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-rmse_beta1=zeros(size(list_T,2), size(list_N,2));
-rmse_beta2=zeros(size(list_T,2), size(list_N,2));
-
-
-for idx_phi=1:size(list_phi,2)     
-phi= list_phi(idx_phi);  
-  b1=3;
-  b2=1;
-for idx_T=1:size(list_T,2)    
-T0 = list_T(idx_T);             
- 
-for idx_N=1:size(list_N,2)   
-N = list_N(idx_N);
-Dis_T=50;
-
-TT= (T0+1)+Dis_T;    
-
-IVMG=zeros(1+k,rep);   % 1+k by rep
-
-sml=1;         
-while sml<=rep
-%parfor sml=1:rep
-y=zeros(N,TT);
-x=zeros(k,N,TT);
-
-eta_rho_i=-0.25+(0.5)*rand([1,N]); % 1 by N
-phi_i= phi+  eta_rho_i;
-
-beta_i=b'*ones(1,N)+sqrt(1-rho_b^(2))*ones(k,1)*eta_rho_i; % k by N
-
-theta_i=[phi_i;beta_i];   % 1+k by N
-v_x=zeros(k,N,TT);
-v_x(:,:,1)=zeros(k,N,1);  
-for ttt=2:TT
[…]

### 2020-03-08 MC_code/IV_Norkute.m

@@ -1,6 +1,6 @@
-rep = 2000;  
-list_T = [25 50 100 200]; 
-list_N = [25 50 100 200];  
+rep = 250;  
+list_T = [25 ]; 
+list_N = [25 ];  
 list_phi= [0.5]; 
 b1=3;
 b2=1;
@@ -59,7 +59,7 @@ while sml<=rep
 y=zeros(N,TT);
 x=zeros(k,N,TT);
 
-eta_rho_i=-0.25+(0.5)*rand([1,N]); % 1 by N
+eta_rho_i=-0.25+(0.5)*rand([1,N]); % 1 by N heterogeneous_y
 eta_rho_bi=-sqrt(3)+2*sqrt(3)*rand([1,N]);
 phi_i= phi+eta_rho_i;  % phi heterogeneous; 1 by N
 v_x=zeros(k,N,TT);

### 2020-03-08 MC_code/IV_Norkute2.m

@@ -1,7 +1,7 @@
 tic
 rep = 500;  
-list_T = [ 35 50 100 ]; 
-list_N = [25 50 100  ];  
+list_T = [ 25 50]; 
+list_N = [25  50];  
 list_phi= [0.5]; 
 b1=3;
 b2=1;
@@ -104,8 +104,8 @@ Xi_b(kk,iiiii)= (diff_bar_v(kk,iiiii))/(mean_sqr_diff_bar_v(kk));  % k by N
     end
 end
 
-% beta_i=b'*ones(1,N)+(sqrt((0.4^2)/12)*rho_b*Xi_b+ones(k,1)*sqrt(1-rho_b^(2))*eta_rho_bi); % k by N
-beta_i=b'*ones(1,N);
+ beta_i=b'*ones(1,N)+(sqrt((0.4^2)/12)*rho_b*Xi_b+ones(k,1)*sqrt(1-rho_b^(2))*eta_rho_bi); % k by N
+%beta_i=b'*ones(1,N);
 
 
 
@@ -164,36 +164,86 @@ for tt=2:TT
     for ii=1:N
         
    eta_x(:,:,ii)= [Gamma_i(1,2,ii),Gamma_i(1,3,ii);Gamma_i(2,2,ii),Gamma_i(2,3,ii)];     
- % mu_i(ii,:)'+
- x(:,ii,tt)=eta_x(:,:,ii)'*fy(1:m_x,tt)+v_x(:,ii,tt);     % k by N by TT
+ %
+ x(:,ii,tt)= mu_i(ii,:)'+eta_x(:,:,ii)'*fy(1:m_x,tt)+v_x(:,ii,tt);     % k by N by TT
  
    eta_y(:,:,ii)=[Gamma_i(1,1,ii),Gamma_i(2,1,ii),Gamma_i(3,1,ii)]; % 1 by m_y
-%  a_i(ii,:)+
-  y(ii,tt)=y(ii,tt-1)*phi_i(:,ii)+x(:,ii,tt)'*beta_i(:,ii)+eta_y(:,:,ii)*fy(:,tt)+(sqrt(xi_es)*sqrt((chi2rnd(2)/2)*(tt/TT))*(chi2rnd(1)-1))/sqrt(2);    % N by TT    
+% 
[…]

### 2020-03-08 MC_code/LS.m

@@ -1,129 +1,0 @@
-rep = 2000;  
-list_T = [25 50 100 200]; 
-list_N = [25 50 100 200];  
-list_phi= [0.5]; 
-rho=[0];
-b1=3;
-b2=1;
-rho_b=0.4;
-b=[b1,b2];
-k=2;   % number of regressors
-bias_mean_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
-bias_mean_beta1=zeros(size(list_T,2), size(list_N,2)); 
-bias_mean_beta2=zeros(size(list_T,2), size(list_N,2)); 
-std_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-std_beta1=zeros(size(list_T,2), size(list_N,2));  
-std_beta2=zeros(size(list_T,2), size(list_N,2));  
-rmse_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-rmse_beta1=zeros(size(list_T,2), size(list_N,2));
-rmse_beta2=zeros(size(list_T,2), size(list_N,2));
-
-
-for idx_phi=1:size(list_phi,2)     
-phi= list_phi(idx_phi);  
-  b1=3;
-  b2=1;
-for idx_T=1:size(list_T,2)    
-T0 = list_T(idx_T);             
- 
-for idx_N=1:size(list_N,2)   
-N = list_N(idx_N);
-Dis_T=50;
-
-TT= (T0+1)+Dis_T;    
-
-LS_MG=zeros(1+k,rep);   % 1+k by rep
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-randn('state', 12345678) ;
-rand('state', 1234567) ;
-   RandStream.setGlobalStream (RandStream('mcg16807','seed',34));
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-sml=1;         
-while sml<=rep
-%parfor sml=1:rep
-y=zeros(N,TT);
[…]

### 2020-03-08 MC_code/MAIV_MG_lag5_test.m

@@ -1,742 +1,0 @@
-rep = 500;  
-list_T = [ 25 ]; 
-list_N = [25];  
-list_phi= [ 0.5 ]; 
-b1=3;
-rho_b=0.4;
-rho_b1=0;
-tao=0.5;
-v_theta=-0.2;
-b=[b1];
-k=1;   % number of regressors
-j=5; % lag of regressor
-Dis_T=50;
-%%%%%%%%%%%%%%%%%%%%%%%%
-ini_bias_mean_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-ini_bias_mean_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
-
-ini_std_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-ini_std_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-
-ini_rmse_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-ini_rmse_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-
-ini_mae_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-ini_mae_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-ini_bias_mean_phi_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-ini_bias_mean_beta1_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
-
-ini_std_phi_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-ini_std_beta1_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-
-ini_rmse_phi_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-ini_rmse_beta1_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-
[…]

### 2020-03-08 MC_code/MAIV_MG_test_one_regressor_lag5_DGP2.m

@@ -1,659 +1,0 @@
-rep = 350;  
-list_T = [25 50 100 200]; 
-list_N = [25 50 100 200];  
-list_phi= [0.5]; 
-b1=3;
-rho_b=0.4;
-rho_b1=0.5;
-tao=0.5;
-v_theta=-0.2;
-b=[b1];
-k=1;   % number of regressors
-j=10; % lag of regressor
-Dis_T=50;
-ini_bias_mean_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-ini_bias_mean_beta1=zeros(size(list_T,2), size(list_N,2)); 
-
-ini_std_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-ini_std_beta1=zeros(size(list_T,2), size(list_N,2));  
-
-ini_rmse_phi=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-ini_rmse_beta1=zeros(size(list_T,2), size(list_N,2));
-%%%%%%%%%%%%%%%%%%%%%%%%
-ini_bias_mean_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-ini_bias_mean_beta1_1=zeros(size(list_T,2), size(list_N,2)); 
-
-ini_std_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
-ini_std_beta1_1=zeros(size(list_T,2), size(list_N,2));  
-
-ini_rmse_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-ini_rmse_beta1_1=zeros(size(list_T,2), size(list_N,2));
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-ini_bias_mean_phi_2=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
-ini_bias_mean_beta1_2=zeros(size(list_T,2), size(list_N,2)); 
-
[…]

### 2020-03-08 MC_code/MAIV_opt_5.m

@@ -1,19 +1,16 @@
-function [omega_5, fval_5, exitflag_5, output_5, lambda_5, hessian_5]=MAIV_opt_5(T1,K_5,sigma_etau_i,Sigma_u_i_i,Sigma_eta_i_i, hat_U_i_5,Gamma,j,omega0,lq_5,uq_5)
+function [omega_5, fval_5, exitflag_5, output_5, lambda_5, hessian_5]=MAIV_opt_5(T1,K_5,sigma_etau_i,Sigma_u_i_i,Sigma_eta_i_i, hat_U_i_5,Gamma,j5,omega0,lq_5,uq_5)
  
 % maximum likelihood routine. see the program transformed_ml.m
  
 
-[omega_5, fval_5, exitflag_5, output_5, lambda_5,~,hessian_5] = fmincon(@likelihood,omega0,[],[],[ones(1,j)],1,lq_5,uq_5,[]); 
+[omega_5, fval_5, exitflag_5, output_5, lambda_5,~,hessian_5] = fmincon(@likelihood,omega0,[],[],[ones(1,j5)],1,lq_5,uq_5,[]); 
  
     function [likelihood]=likelihood(omega)
  dim_omega = size(omega0,1);
     omega  = omega(1:dim_omega,1);
- 
-    
-    
- sigma_mse=(sigma_etau_i^2)*((K_5'*omega)^2)/T1+Sigma_u_i_i*((omega'*hat_U_i_5*omega- Sigma_eta_i_i*(j-2*K_5'*omega+omega'*Gamma*omega))/T1);
+     
+ sigma_mse=(sigma_etau_i^2)*((K_5'*omega)^2)/T1+Sigma_u_i_i*((omega'*hat_U_i_5*omega- Sigma_eta_i_i*(j5-2*K_5'*omega+omega'*Gamma*omega))/T1);
   
-    
     
  likelihood = sigma_mse;
     

### 2020-03-08 MC_code/MAIV_opt_6.m

@@ -1,0 +1,24 @@
+function [omega_6, fval_6, exitflag_6, output_6, lambda_6, hessian_6]=MAIV_opt_6(T1,K_6,sigma_etau_i,Sigma_u_i_i,Sigma_eta_i_i, hat_U_i_6,Gamma,j6,omega0,lq_6,uq_6)
+ 
+% maximum likelihood routine. see the program transformed_ml.m
+ 
+
+[omega_6, fval_6, exitflag_6, output_6, lambda_6,~,hessian_6] = fmincon(@likelihood,omega0,[],[],[ones(1,j6)],1,lq_6,uq_6,[]); 
+ 
+    function [likelihood]=likelihood(omega)
+ dim_omega = size(omega0,1);
+    omega  = omega(1:dim_omega,1);
+ 
+    
+    
+ sigma_mse=(sigma_etau_i^2)*((K_6'*omega)^2)/T1+Sigma_u_i_i*((omega'*hat_U_i_6*omega- Sigma_eta_i_i*(j6-2*K_6'*omega+omega'*Gamma*omega))/T1);
+  
+    
+    
+ likelihood = sigma_mse;
+    
+    
+    
+  
+end
+end

### 2020-03-08 MC_code/MAIV_opt_7.m

@@ -1,0 +1,18 @@
+function [omega_7, fval_7, exitflag_7, output_7, lambda_7, hessian_7]=MAIV_opt_7(T1,K_7,sigma_etau_i,Sigma_u_i_i,Sigma_eta_i_i, hat_U_i_7,Gamma,j7,omega0,lq_7,uq_7)
+ 
+% maximum likelihood routine. see the program transformed_ml.m
+[omega_7, fval_7, exitflag_7, output_7, lambda_7,~,hessian_7] = fmincon(@likelihood,omega0,[],[],[ones(1,j7)],1,lq_7,uq_7,[]); 
+ 
+    function [likelihood]=likelihood(omega)
+ dim_omega = size(omega0,1);
+    omega  = omega(1:dim_omega,1);
+  
+ sigma_mse=(sigma_etau_i^2)*((K_7'*omega)^2)/T1+Sigma_u_i_i*((omega'*hat_U_i_7*omega- Sigma_eta_i_i*(j7-2*K_7'*omega+omega'*Gamma*omega))/T1);
+  
+    
+    
+ likelihood = sigma_mse;
+    
+  
+end
+end

### 2020-03-08 MC_code/opt_IV_factor.m

@@ -1,7 +1,7 @@
 tic
 rep = 500;  
-list_T = [ 25  ]; 
-list_N = [50  ];  
+list_T = [ 25 ]; 
+list_N = [50 ];  
 list_phi= [0.5 ]; 
 b1=3;
 b2=1;
@@ -256,12 +256,12 @@ for tt=2:TT
     for ii=1:N
         
    eta_x(:,:,ii)= [Gamma_i(1,2,ii),Gamma_i(1,3,ii);Gamma_i(2,2,ii),Gamma_i(2,3,ii)];     
-   
- x(:,ii,tt)=mu_i(ii,:)'+rho*(x(:,ii,tt-1))+eta_x(:,:,ii)'*fx(:,tt)+v_x(:,ii,tt);     % k by N by TT
+   % mu_i(ii,:)'+
+ x(:,ii,tt)=rho*(x(:,ii,tt-1))+eta_x(:,:,ii)'*fx(:,tt)+v_x(:,ii,tt);     % k by N by TT
  
    eta_y(:,:,ii)=[Gamma_i(1,1,ii),Gamma_i(2,1,ii),Gamma_i(3,1,ii)];
- 
-  y(ii,tt)= a_i(ii,:)+y(ii,tt-1)*phi_i(:,ii)+x(:,ii,tt)'*beta_i(:,ii)+eta_y(:,:,ii)*fy(:,tt)+(sqrt(xi_es)*sqrt((chi2rnd(2)/2)*(tt/TT))*(chi2rnd(1)-1))/sqrt(2);    % N by TT    
+ % a_i(ii,:)+
+  y(ii,tt)= y(ii,tt-1)*phi_i(:,ii)+x(:,ii,tt)'*beta_i(:,ii)+eta_y(:,:,ii)*fy(:,tt)+(sqrt(xi_es)*sqrt((chi2rnd(2)/2)*(tt/TT))*(chi2rnd(1)-1))/sqrt(2);    % N by TT    
     end
 end
 

### 2020-03-08 MC_code/opt_IV_factor_forwardfilter.m

@@ -1,0 +1,984 @@
+tic
+rep = 500;  
+list_T = [ 50]; 
+list_N = [50 ];  
+list_phi= [0.5 ]; 
+b1=3;
+b2=1;
+b=[b1,b2]; % 1 by k 
+rho=0; % lag of x ARDL(0,1) 
+pi_u=0.75; % 0.25 or 0.75
+SNR=4;
+Mu1=1;
+Mu2=-0.5;
+A=0.5;
+rho_gamma_1s=0; %  0 independent factor loading; 0.5 correlated loading
+k=2;   % number of regressors
+m_x=2; % number of factors of regressor
+my=1;
+m_y=m_x+my; % number of factors of y
+xi_es=(pi_u/(1-pi_u))*m_y;
+
+rho_mu=0.5;
+rho_v=0.5;
+rho_b=0.4;
+xi_ev=xi_es*(SNR-(rho_v^(2)/(1-rho_v^(2))))*((b1^(2)+b2^(2))/(1-rho_v^(2)))^(-1);
+
+
+
+j=7; % lag of regressor
+Dis_T=50;
+%%%%%%%%%%%%%%%%%%%%%%%%
+ini_bias_mean_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_bias_mean_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
+
+ini_std_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
+ini_std_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
+
+ini_rmse_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_rmse_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+
+ini_mae_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_mae_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
[…]

### 2020-03-08 MC_code/opt_IV_factor_forwardfilter_nonrestrition.m

@@ -1,0 +1,1029 @@
+tic
+rep = 500;  
+list_T = [50 ]; 
+list_N = [50 ];  
+list_phi= [0.8 ]; 
+b1=3;
+b2=1;
+b=[b1,b2]; % 1 by k 
+rho=0; % lag of x ARDL(0,1) 
+pi_u=0.75; % 0.25 or 0.75
+SNR=4;
+Mu1=1;
+Mu2=-0.5;
+A=0.5;
+rho_gamma_1s=0; %  0 independent factor loading; 0.5 correlated loading
+k=2;   % number of regressors
+m_x=2; % number of factors of regressor
+my=1;
+m_y=m_x+my; % number of factors of y
+xi_es=(pi_u/(1-pi_u))*m_y;
+
+rho_mu=0.5;
+rho_v=0.5;
+rho_b=0.4;
+xi_ev=xi_es*(SNR-(rho_v^(2)/(1-rho_v^(2))))*((b1^(2)+b2^(2))/(1-rho_v^(2)))^(-1);
+
+
+
+j=7; % lag of regressor
+Dis_T=50;
+%%%%%%%%%%%%%%%%%%%%%%%%
+ini_bias_mean_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_bias_mean_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2)); 
+
+ini_std_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
+ini_std_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));  
+
+ini_rmse_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_rmse_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+
+ini_mae_phi_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+ini_mae_beta1_1=zeros(size(list_T,2), size(list_N,2), size(list_phi,2));
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
[…]
